\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times,amsmath,epsfig}
\usepackage{booktabs}
\usepackage{color}
\usepackage[table]{xcolor}
\usepackage{listings}
\usepackage{url}
\usepackage{graphicx}
\newcommand{\tab}{\hspace*{2ex}}
\usepackage{multirow}

\newcommand{\ie}{{\em i.e.\ }}
\newcommand{\eg}{{\em e.g.\ }}
\newcommand{\et}{{\em  et al. }}

\newcommand{\eqn}[1]{Equation (\ref{eqn:#1})}
\newcommand{\fig}[1]{Figure \ref{fig:#1}}
\newcommand{\tabl}[1]{Table \ref{tab:#1}}
\newcommand{\secref}[1]{Section \ref{#1}}
\newcommand{\KZ}[1]{\textcolor{blue}{[KZ: #1]}}
\newcommand{\GR}[1]{\textcolor{red}{[grao: #1]}}

\begin{document}

\title{Auditory Scene Recognition Using Textual Knowledge}
\author{
%% author names are typeset in 11pt, which is the default size in the author block
%Guoteng Rao$^*$ \tab Biman Tang$^*$ \tab Kenny Q. Zhu$^{+}$
%\vspace{1.6mm}\\
%\fontsize{10}{10}\selectfont\itshape
%Department of Computer Science \& Engineering,\\
%\fontsize{10}{10}\selectfont\itshape
%Shanghai Jiao Tong University\\
%\fontsize{10}{10}\selectfont\itshape
%Shanghai, China\\
%\fontsize{10}{10}\selectfont\ttfamily\upshape
%$~^{*}$\{rgt0820, bimantang\}@gmail.com\\
%\fontsize{10}{10}\selectfont\ttfamily\upshape
%$~^{+}$kzhu@cs.sjtu.edu.cn
}

\maketitle

\begin{abstract}
Auditory scene recognition is the process of recognizing 
the context of audio clips from a set of predefined class labels. 
In this paper, we introduce a new event based scene recognition framework.
Different from traditional approaches which train statistical models from
samples of the same set of scenes, our framework doesn't require any such
labeled training data. Instead, using a comprehensive concept knowledge base,
we are able to develop a vocabulary of audible event terms and use them to
query for shorter audio samples of such primitive events from the web.
The framework then automatically mines the event-scene distribution from 
large amount of online TV or movie transcripts. Combined with the Gaussian
mixture model learned from the event samples, this event-scene 
probability model allows us to automatically infer the most likely 
scene of any input audio. Despite that no training samples of the original
scenes are used, the framework achieves 10-scene classification accuracy 
closely 
on par with the best-performing machine learning technique reported 
by the latest IEEE AASP scene recognition challenge in 2013.
\end{abstract}

%\begin{keywords}
%Gaussian Mixture Model, Audio Scene Recognition, Knowledge Base, Clustering
%\end{keywords}

\input{intro}
%\input{problem}
\input{approach}
%\input{implement}
\input{eval}
\input{related}
\input{conclude}

\bibliographystyle{aaai}
\bibliography{context}
\end{document}
