\section*{Limitations}

Some limitations of the proposed methods remain to be addressed 
in future research.
% \KZ{We gotta be careful here not to let reviewers to use these limitations
% as weapons against us.} 

First, our experiment settings assume that the desired attributes are available for generation, which would require a separate dialogue policy to decide the 
attribute label provided to the model. Therefore, our model cannot be 
directly applied to end-to-end dialogue models, and may also be affected by 
the potential error propagation from the dialogue policy model. Since the intended use of DASC is to serve as a component of pipeline-style dialogue systems, these common issues in such systems are out of the scope of this work. 
% \KZ{This is only useful in the scenario that the attribute actually changes
% its value dynamically. We can argue that this is out of the scope of
% this work, and that our work can server as a component in this kinda of
% systems.}

Moreover, we require annotated datasets with multiple attributes for evaluation, which are rare. Therefore, we evaluate the capability of multi-attribute control mostly on one dataset. Experiments on more datasets, especially those with additional attributes may be required to further validated the efficacy of the proposed methods.
% \MY{A few points listed here are quite sharp, e.g. the requirement of annotation, we probably can say that we require datasets providing multiple attributes while these are very rare, hence the validation is mostly done on one dataset.}

Last but not least, DASC is not directly applicable for controllable generation with free text as control signal, such as persona descriptions \cite{zhang2018personalizing}, which might limit its application range, though we may simply combine DASC with other techniques like concatenating the descriptions to achieve this goal, which will require further explorations. 
