%
% File acl2018.tex
%
%% Based on the style files for ACL-2017, with some changes, which were, in turn,
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2018}
\usepackage{times}
\usepackage{latexsym}

\usepackage{url}
%\usepackage{breakurl}
\aclfinalcopy % Uncomment this line for the final submission
\def\aclpaperid{638} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\BibTeX{B{\sc ib}\TeX}


\usepackage{CJKutf8}
\usepackage{amsmath,amsfonts,amsthm}
\usepackage{color}
\usepackage{array}
\usepackage{epsfig}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{array}
\usepackage{ragged2e}
\usepackage{pbox}
\usepackage{enumitem}

\usepackage{lipsum}
\usepackage{paralist}
%\setlist[enumerate]{itemsep=0mm}
\renewenvironment{itemize}[1]{\begin{compactitem}#1}{\end{compactitem}}
\renewenvironment{enumerate}[1]{\begin{compactenum}#1}{\end{compactenum}}
\renewenvironment{description}[0]{\begin{compactdesc}}{\end{compactdesc}}
\usepackage[ruled,vlined,boxed,linesnumbered]{algorithm2e}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\usepackage{float}
\restylefloat{table}
\newcolumntype{P}[1]{>{\RaggedRight\hspace{0pt}}p{#1}}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}


\newcommand{\secref}[1]{Section \ref{#1}}
\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\eqnref}[1]{Eq. (\ref{#1})}
\newcommand{\tabref}[1]{Table \ref{#1}}
\newcommand{\exref}[1]{Example \ref{#1}}
\newcommand{\algref}[1]{Algorithm \ref{#1}}
\newcommand{\socvec}{SocVec}
\newcommand{\argmin}{\operatornamewithlimits{argmin}}
\newcommand{\argmax}{\operatornamewithlimits{argmax}}
\newtheorem{example}{Example}
\newtheorem{lemma}{Lemma}
\newtheorem{definition}{Definition}
\newcommand{\cut}[1]{}

\newcommand{\li}{\uline{\hspace{0.5em}}}
\newcommand{\BL}[1]{\textcolor{blue}{Bill: #1}} 
\newcommand{\KZ}[1]{\textcolor{green}{Kenny: #1}}
\newcommand{\SH}[1]{\textcolor{green}{Seung: #1}}
\newcommand{\FX}[1]{\textcolor{blue}{Frank: #1}}

\pdfinfo{
	/Title (Mining Cross-Cultural Differences and Similarities in Social Media)
	/Author (Bill Yuchen Lin, Frank F. Xu, Kenny Q. Zhu, Seung-won Hwang)}

\title{Mining Cross-Cultural Differences and Similarities in Social Media}
\author{
	Bill Yuchen Lin{\small $^{1}$}\thanks{\scriptsize~~Both authors contributed equally.}~~~~~Frank F. Xu{\small $^{1}$}\footnotemark[1]~~~~~Kenny Q. Zhu{\small $^{1}$}~~~~~Seung-won Hwang{\small $^{2}$}\\ 
	{\small $^{1}$}Shanghai Jiao Tong University, Shanghai, China\\
	\{yuchenlin, frankxu\}@sjtu.edu.cn, kzhu@cs.sjtu.edu.cn\\
	{\small $^{2}$}Yonsei University, Seoul, Republic of Korea\\
	seungwonh@yonsei.ac.kr\\
}

%\author{First Author \\
%  Affiliation / Address line 1 \\
%  Affiliation / Address line 2 \\
%  Affiliation / Address line 3 \\
%  {\tt email@domain} \\\And
%  Second Author \\
%  Affiliation / Address line 1 \\
%  Affiliation / Address line 2 \\
%  Affiliation / Address line 3 \\
%  {\tt email@domain} \\}

\date{}
%\hypersetup{draft} 
\begin{document}
\maketitle
\begin{abstract}
Cross-cultural differences and similarities are common in cross-lingual natural language understanding, especially for research in social media.
For instance, people of distinct cultures often hold different opinions on a single named entity.
Also, understanding slang terms across languages requires knowledge of cross-cultural similarities. 
In this paper, we study the problem of computing such cross-cultural differences and similarities.
We present a lightweight yet effective approach, and evaluate it on two novel tasks: 1) mining cross-cultural differences of named entities and 2) finding similar terms for slang across languages. 
Experimental results show that our framework substantially outperforms a number of baseline methods on both tasks.
The framework could be useful for machine translation applications and research in computational social science.
\end{abstract}

\begin{CJK}{UTF8}{gkai}
	\input{intro}
	\input{SocVec}
	\input{eval}
	\input{MCDNE}
	\input{BLEIS}
	\input{related}
	\input{conclude} 
	\section*{Acknowledgment}
Kenny Zhu is the contact author and was supported by NSFC grants 91646205 and 61373031. Seung-won Hwang was supported by Microsoft Research Asia. Thanks to the anonymous reviewers and Hanyuan Shi for their valuable feedback. 
\end{CJK}

% include your own bib file like this:
%\bibliographystyle{acl}
%\bibliography{naaclhlt2018}
\bibliography{acl}
\bibliographystyle{acl_natbib}

\end{document}
