\begin{abstract}
\noindent
Audio scene recognition is the process of the recording context of audio clips. In previous work, many researchers focus on this problem, and proposed a lot of great ideas. In this thesis, we are going to introduce a event based method to recognize scene from audio. In our work, we not only train our model from audio data, but also use information in drama scripts. We train a probabilistic model from text data, to describe the relation between audible events and scenes. For each event, we use Gaussian Mixture Model to train the audio models. Combining these model together, our system can achieve $37\%$ accuracy on average for classifying 10 common scenes. If we take the top 3 results into consideration, our system can an accuracy higher than $70\%$.
\end{abstract}

\keywords{Gaussian Mixture Model, Audio Scene Recognition, Knowledge base}

\newpage
\renewcommand{\abstractname}{摘要}
\renewcommand{\abstractnamefont}{\fontsize{14pt}{14pt}\selectfont\bf}
\renewcommand{\abstracttextfont}{\fontsize{12pt}{16pt}\selectfont}
\setlength{\absleftindent}{0pt}
\setlength{\absrightindent}{0pt}

\renewcommand{\keywords}[1]{\noindent\textbf{关键词:} #1}
\begin{center}
 
\end{center}
\vspace{3cm}
\begin{abstract}
音频场景识别是指根据一段音频推断出其录制场景的过程。在之前的工作中，许多研究人员致力于这个问题并提出了许多非常好的想法。本文将要提出一种基于事件的方法来进行音频场景识别。我们的工作不仅仅从音频数据中训练出我们的模型，同时还用到了剧本相关的信息――从文本信息中训练出一个关于可听事件和场景的关系的概率模型。对于每个事件，我们用高斯混合模型建模来训练音频模型。结合这两种模型，我们的系统对10个场景进行分类的时候可以达到平均$37\%$的准确率。如果考虑可能性最高的3个场景，我们的系统将能达到超过$70\%$的准确率。
\end{abstract}

\keywords{高斯混合模型，音频场景识别，知识库}
