\documentclass[10pt,conference,letterpaper]{IEEEtran}
%\documentclass{vldb}
%\documentclass{acm_proc_article-sp}%sig-alternate
\usepackage{times,amsmath,amsfonts}
\usepackage{float}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{subfigure}
\usepackage{url}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{algcompatible}
\usepackage{eqparbox}
\usepackage{epsfig}
\usepackage{epstopdf}
\usepackage{mathrsfs}
\usepackage{amsmath}
\usepackage{balance}

\renewcommand\algorithmiccomment[1]{%
  \hfill\#\ \eqparbox{COMMENT}{#1}%
}
\newcommand\LONGCOMMENT[1]{%
  \hfill\#\ \begin{minipage}[t]{\eqboxwidth{COMMENT}}#1\strut\end{minipage}%
}

\clubpenalty=10000
\widowpenalty=10000
\makeatletter
\newif\if@restonecol
\makeatother
\let\algorithm\relax
\let\endalgorithm\relax
%\usepackage[vlined,boxed]{algorithm2e}
\usepackage[linesnumbered,vlined,ruled]{algorithm2e}

\usepackage{xspace}
\newcommand{\qid}{\emph{qid}\xspace}
\newcommand{\qids}{\emph{qid}s\xspace}

\newcommand{\SA}{\mathcal{SA}}

\newcommand{\argmax}{\mathop{\mathrm{argmax}}}
\newcommand{\pss}{\sigma^2_{\eta_c^i}}
\newcommand{\qss}{\sigma^2_{\eta_c^j}}
\newcommand{\pww}{w^2_i}
\newcommand{\qww}{w^2_j}
\newcommand{\container}{\mathcal{C}}
\newcommand{\csize}{\kappa}
\newcommand{\linked}{\mathcal{L}}
\newcommand{\enum}{\mathcal{E}}
\newcommand{\safe}{\mathcal{S}}
\newcommand{\policy}{\mathcal{P}}
\newcommand{\natnum}{\mathbb{N}}
\newcommand{\breach}{P_\text{breach}}
\newcommand{\wrt}{w.r.t.}
\newcommand{\TRUE}{\textbf{true} }
\newcommand{\FALSE}{\textbf{false} }
\newcommand{\AND}{\textbf{and} }
\newcommand{\NOT}{\textbf{not} }
\newcommand{\RETURN}{\textbf{return} }
\newcommand{\reference}{\textbf{ref}~}
\newcommand{\shrink}{\vspace*{-3pt}}

\newcommand{\PartialSuppressor}{\textsc{PartialSuppressor} }
\newcommand{\SplitData}{\textsc{DNCSplitData} }
\newcommand{\SanitizeBuffer}{\textsc{SanitizeBuffer} }
\newcommand{\HandleLongRecord}{\textsc{HandleLong} }
\newcommand{\HandleShortRecords}{\textsc{HandleShort} }
\newcommand{\MakeRed}{\textcolor{red}}

\newcommand{\Enum}{\textsc{EnumQids} }
\newcommand{\EnumLong}{\textsc{EnumerateLong} }
\newcommand{\ClearBuffer}{\textsc{ClearBuffer} }
\newcommand{\UpdateBuffer}{\textsc{UpdateBuffer} }
\newcommand{\FindAffected}{\textsc{FindAffected} }
\newcommand{\SuppressionPolicy}{\textsc{SuppressionPolicy} }

\newcommand{\bmax}{b_\text{max}}
\newcommand{\lmin}{l_\text{min}}
\newcommand{\tmax}{t_\text{max}}
\newcommand{\dnum}{\sigma}

\newcommand{\PartialR}{\textsc{Partial(r)} }
\newcommand{\PartialL}{\textsc{Partial(l)} }
\newcommand{\PartialALL}{\textsc{Partial(all)} }

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\newtheorem{property}{Property}
\newtheorem{axiom}{Axiom}
\newtheorem{example}{Example}
\newcommand{\etal}{{\em et al.}\xspace}

\usepackage[usenames]{color}
\newcommand{\XJ}[1]{\textcolor{magenta}{[XJ: #1]}}
\newcommand{\XH}[1]{\textcolor{blue}{[Xinhui: #1]}}
\newcommand{\KZ}[1]{\textcolor{Green}{[KZ: #1]}}
\newcommand{\PC}[1]{\textcolor{red}{[PC: #1]}}

\begin{document}

\title{Anonymization of Set-Valued Data by Partial Suppression}
%\numberofauthors{1}
%\author{
%\alignauthor
%Xinhui Xu$^+$ \hspace*{5mm} Xiao Jia$^+$ \hspace*{5mm}
%Chao Pan$^*$ \hspace*{5mm} Kenny Q. Zhu$^+$\\
%\affaddr{Shanghai Jiao Tong University}\\
%\affaddr{Shanghai, China}\\
%\email{$^+$\{xuxinhui,xjia,kzhu\}@cs.sjtu.edu.cn \hspace*{5mm}
%$^*$pc660@sjtu.edu.cn}
%}
\author{
% author names are typeset in 11pt, which is the default size in the author block
{Xinhui Xu{\small $^{*}$}, Xiao Jia{\small $^{*}$},
Chao Pan{\small $^{+}$}, Kenny Q. Zhu{\small $^{*}$}}%
% add some space between author names and affils
\vspace{1.6mm}\\
\fontsize{10}{10}\selectfont\itshape
$~^{*+}$Shanghai Jiao Tong University\\
Shanghai, China\\
\fontsize{9}{9}\selectfont\ttfamily\upshape
$^*$\{xuxinhui,xjia,kzhu\}@cs.sjtu.edu.cn \hspace{5mm} $^+$pc660@sjtu.edu.cn
}


\maketitle

%\setlength{\parskip}{10pt}
\begin{abstract}
Privacy-preserving set-valued data publishing is an important yet challenging
problem.
In this paper, we present a novel framework for set-valued
data anonymization by partial suppression which ensures no strong
inference of sensitive information is possible regardless of the amount of
background knowledge the attacker possesses, and can be adapted
to both space-time and quality-time trade-offs as a ``pay-as-you-go'' approach.
%
While minimizing the number of item deletions, the framework attempts to
either preserve the original data distribution or retain
mineable useful association rules with limited spurious rules invented in the
anonymized data, without particular assumptions of the downstream utility of the
data.
%
We also devise two novel heuristics to drive
the partial suppression process in two different directions.
The first heuristic seeks to preserve the original data distribution by
minimizing the {\em Kullback-Leibler divergence}
between the original and anonymized data sets.
The second heuristic seeks to reduce the number of spurious rules when
the anonymized data is used for rule mining.
Our extensive experiments show
that partial suppression significantly outperforms generalization and global
suppression, two of the existing popular anonymization techniques, in
maximizing the data utility with reasonable cost in time.
%space and time.
\end{abstract}

\input{intro}
%original
%\input{problem-2934}
%\input{problem}
%original
%\input{algo}
%now
\input{problem2}
\input{algo2}

\input{eval}

\input{related}

%\input{attack}

\input{conclusion}

%\input{analysis}
\balance

{\renewcommand{\baselinestretch}{0.95}
\normalsize
\bibliographystyle{abbrv}
\bibliography{../bibs/privacy}
}
%\input{appendix}

\end{document}
