\section{Conclusion}
\label{sec:conclude}
% \KZ{Conclusion can mention what are our main results.
% Need to be a bit more detailed. Too short right now.}
We have proposed a new declarative 
data description language for describing and extracting 
information from various medical images. 
Our new language makes use of both data information and 
spatial information to automatically 
generate parsers for information extraction from 
images. Although there are errors in the OCR results, 
scoring strategies in the parsers make them capable of 
tolerating errors. 
% enabling one to extract the correct information. 
% With the proposed incremental correction framework, 
We further improve the accuracy of the 
extracted information with the proposed incremental correction framework. 
Our evaluation results validated 
that our proposed methods outperform the other three 
existing solutions on our real life dataset. 
% By designing fuzzy matching strategies, our system 
% finds the optimal results within the OCR results which 
% may be full of errors and noises. 
Furthermore, our evaluation of the manual correction framework indicates that 
by using a suitable error correction recommendation system, 
we can make efficient use of the manual correction and 
correct more errors with limited manual correction 
information. In sum, our system can be used to extract 
information from a large quantity of medical images with simple 
descriptions and to find an efficient way to make use of 
human power. Though the data used in this paper are exclusively
medical images, which is the starting point of our research, 
this framework will conceivably benefit 
information extraction tasks targetting other types of
semi-structured images.

% We propose to design a declarative data description 
% language for descripting and extracting information from 
% medical images. Our new language make use of the spatial 
% and data constraints in medical images, which can be 
% used to automatically generate parsers for 
% information extraction from these images. 
% We also propose an incremental correction framework 
% to make use of user corrections. 
% Our evaluation results validated that our 
% proposed methods outperform other solutions on 
% our real life dataset. 
