%%%% ijcai16.tex

\typeout{IJCAI-16 Instructions for Authors}

% These are the instructions for authors for IJCAI-16.
% They are the same as the ones for IJCAI-11 with superficical wording
%   changes only.

\documentclass{article}
% The file ijcai16.sty is the style file for IJCAI-16 (same as ijcai07.sty).
\usepackage{ijcai16}

% Use the postscript times font!
\usepackage{times}

% the following package is optional:
%\usepackage{latexsym} 

% Following comment is from ijcai97-submit.tex:
% The preparation of these files was supported by Schlumberger Palo Alto
% Research, AT\&T Bell Laboratories, and Morgan Kaufmann Publishers.
% Shirley Jowell, of Morgan Kaufmann Publishers, and Peter F.
% Patel-Schneider, of AT\&T Bell Laboratories collaborated on their
% preparation.

% These instructions can be modified and used in other conferences as long
% as credit to the authors and supporting agencies is retained, this notice
% is not changed, and further modification or reuse is not restricted.
% Neither Shirley Jowell nor Peter F. Patel-Schneider can be listed as
% contacts for providing assistance without their prior permission.

% To use for other conferences, change references to files and the
% conference appropriate and use other authors, contacts, publishers, and
% organizations.
% Also change the deadline and address for returning papers and the length and
% page charge instructions.
% Put where the files are available in the appropriate places.
\usepackage{helvet}
\usepackage{courier}
\usepackage{url}
\usepackage{color}
\usepackage{latexsym}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{diagbox}
\usepackage{array}
\usepackage{multicol}
\usepackage{threeparttable}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

\newtheorem{definition}{Definition}

\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\tabref}[1]{Table \ref{#1}}
\newcommand{\secref}[1]{Section \ref{#1}}
\newcommand{\eqnref}[1]{Eq. (\ref{#1})}
\newcommand{\defref}[1]{Def. \ref{#1}}

\newcommand{\KZ}[1]{\textcolor{blue}{Kenny: #1}}
\newcommand{\KQ}[1]{\textcolor{red}{Kangqi: #1}}
\newcommand{\XS}[1]{\textcolor{blue}{Xusheng: #1}}

\title{Paraphrasing Natural Language Relations to Knowledge Base Schemas}
% \author{Subbarao Kambhampati \\ 
% Arizona State University, Tempe Arizona  \\
% ijcai16programchair@gmail.com}

\begin{document}

\maketitle

\begin{abstract}
% 5 sentences
%1. gap between NL and KB
The task of paraphrasing is to translate a natural language relation into structured knowledge.
Due to the incompleteness of a knowledge base (KB), paraphrasing is important for
bridging semantic gaps between NL representations and canonical forms in KB.
%2. presents
We present a framework to model the semantic representation of a binary relations based on
a small set of relation instances, and to infer a set of relation schemas.
%3. what's the schema look like (no mentioning "template" here)
A relation schema links different predicates from KB into a tree structure, which is a compact representation and is human readable.
%4. data driven  + MDL principle (measuring quality)
Our model is distant supervised, followed by the \textit{minimum description length} principle, 
we are able to learn high-quality schemas by optimizing the cost of transmitting both relation instances and schemas.
%5. apply to  &  competitive
The experiments shows the expressiveness of a schema inferred by our model, and those schemas can be
used in downstream tasks like Knowledge Base Completeion (KBC). 
Compared with state-of-the-art paraphrasing systems on a KBC task using Freebase, 
our schema-based approach outperforms feature-based models by 3\% on F1 score.
\end{abstract}

\input{intro}

\input{problem}

\input{approach}

\input{experiment}

\input{related}

%% The file named.bst is a bibliography style file for BibTeX 0.99c
\bibliographystyle{named}
\bibliography{reference}

\end{document}

