% !Mode:: "TeX:UTF-8"
\documentclass[UTF8]{csoarticle}
\usepackage{url,color}
\usepackage{subfigure}
\usepackage{alltt}
\usepackage{epsfig}
\usepackage{epstopdf}
\usepackage{enumerate}
\usepackage{multirow}
\usepackage{fancyvrb}
%\usepackage{slashbox}
%\renewcommand{\rmdefault}{ptm}
%\usepackage{mathptmx}
\newcommand\Hlight[1]{\textcolor[rgb]{0,0,1}{\textbf{#1}}}
\newcommand\Vlight[1]{\textcolor[rgb]{1,0,1}{\textbf{#1}}}
%\newcommand{\KZ}[1]{\textcolor{blue}{[KZ:#1]}}
\begin{document}
\numberwithin{equation}{section}
\setcounter{section}{0}
% first the title is needed
\titleCHN{IP核设计交互式优化的Verilog预编译器}
\titleENG{A Verilog Precompiler for Interactive Optimization of IP Core Design}
%%%%
\authorCHN{王冬华\affil{1}, 范益波\affil{2}, 朱其立\affil{1}, 方文静\affil{1}}
\authorENG{Donghua Wang\affil{1}, Yibo Fan\affil{2}, Kenny Q. Zhu\affil{1}, Wenjing Fang\affil{1}}
\affiliationCHN{
    \affil{1} 上海交通大学电子信息与电气工程学院，上海，邮编200240 \\
    \affil{2} 复旦大学微电子学院，上海，邮编200433
}
\affiliationENG{
    \affil{1} School of Electronic Information and Electrical Engineering, Shanghai Jiao Tong University, Shanghai, 200240 \\
    \affil{2} School of Microelectronics, Fudan University, Shanghai, 332211
}
\abstractCHN{SV+是一个交互式编译器，它能使电路设计者在不改写源代码的情况下，进行
资源消耗和时间花费之间权衡。本篇文章提出了一套简介的SV+语法，它能被用在Verilog语
言中，用以描述电路的可重组部分。用户可以在编译过程中选择优化选项，编译器根据这些
选项生成Verilog RTL代码。对于不同的优化选择，电路的除开时间和资源的不同外，在结构
上也存在不同。SV+句法可以从数学或方法的层面描述可重组电路结构，因此电路设计者从
繁琐的模块时序安排和线路连接中解放出来。不同于以往的电路编译器，例如DFT，这类编译
器只适用于一种算法，SV+句法能被用在一系列Verilog程序，只要设计中有可重组的组成部分。}
\abstractENG{
SV+ is an interactive compiler that makes circuit designer do trade-offs
between resource consuming and time cost easily, without rewriting the
source code. A set of succinct SV+ syntaxes are proposed in this work.
They can be used to embed with Verilog to describe the
re-configurable parts of a circuit. Users have opportunity to select
optimization options during the compiling process. The compiler
generates Verilog RTL codes, depends on these choices. And for different
 optimization choices, the circuits vary in architectures besides
in time and resource. SV+ syntaxes can describe reconfigurable circuit
 structures in mathematical or functional level, so designers are
liberated from putting much effort on concerning about module scheduling
 and wire connection. Unlike other circuit compilers, for example DFT
compiler\cite{GNordin:FFT}, which work on single kind of algorithm,
 SV+ syntaxes can be used in a range of Verilog programs as long as
there are any reconfigurable components available in the design.
}
\authorIntroduction{Donghua Wang，male，master candidate，major research direction：programming language.Yibo Fan，male，master candidate，major research direction：programming language.  Correspondence author：Kenny Q. Zhu，male，associate professor，major research direction：programming language and natural language processing. Wenjing Fang，female，master candidate，major research direction：natural language processing. }
\keywordCHN{SV+句法，Verilog， 编译器， 电路}
\keywordENG{SV+ syntax, Verilog, compiler, circuit}
\fund{高等学校博士学科点专项科研基金资助课题}
\maketitle

\input{intro}
\input{syntax}
\input{compiler}
\input{examples}
\input{experiments}
\input{relatedwork}
\input{conclusion}
\bibliographystyle{abbrv}
\bibliography{richip}
\newpage
\appendix
\input{appendix}
\end{document}
