\documentclass[preprint, 10pt]{elsarticle}

\usepackage{lineno,hyperref}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[small]{caption}
\usepackage{subcaption}
\usepackage{array}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{diagbox}
\usepackage{mathrsfs}
\usepackage{color}
\usepackage{booktabs}
\usepackage{soul}
\usepackage[ruled, linesnumbered, vlined]{algorithm2e}

\modulolinenumbers[10]

\journal{Journal of Information Processing and Management}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\secref}[1]{Section \ref{#1}}
\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\eqnref}[1]{Eq. (\ref{#1})}
\newcommand{\exref}[1]{Example \ref{#1}}
\newcommand{\algoref}[1]{Algorithm \ref{#1}}
\newcommand{\tabref}[1]{Table \ref{#1}}
\newcommand{\socvec}{SocVec}
\newcommand{\argmin}{\operatornamewithlimits{argmin}}
\newcommand{\argmax}{\operatornamewithlimits{argmax}}
\newtheorem{example}{Example}
\newtheorem{lemma}{Lemma}
\newtheorem{definition}{Definition}
\newcommand{\cut}[1]{}
\newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\definecolor{mygray}{gray}{0.5}
\newcommand{\ZY}[1]{\textcolor{blue}{Zhiyi: #1}}
\newcommand{\KZ}[1]{\textcolor{red}{Kenny: #1}}


\begin{document}

\begin{frontmatter}

\title{Knowledge empowered prominent aspect extraction from
	product reviews}

%% Group authors per affiliation:
\author{Zhiyi Luo}
\ead{jessherlock@sjtu.edu.cn}
\author{Shanshan Huang} 
\ead{huangss\_33@sjtu.edu.cn}
\author{Kenny Q. Zhu\corref{mycorrespondingauthor}}
\ead{kzhu@cs.sjtu.edu.cn}
\cortext[mycorrespondingauthor]{Corresponding author}
\address[mymainaddress]{Department of Computer Science and Engineering, Shanghai Jiao Tong University}
\address[mysecondaryaddress]{ 800 Dongchuan Road, Shanghai, China 200240}

\begin{abstract}
	Many existing systems for analyzing and summarizing customer reviews about 
	products or service are based on a number of prominent review aspects. 
	Conventionally, the {\em prominent review aspects} of a product type 
	are determined manually. This costly approach cannot scale to large and 
	cross-domain services such as Amazon.com, Taobao.com or Yelp.com where 
	there are a large number of product types and
	new products emerge almost everyday. 
	In this paper, we propose a novel method empowered by
	knowledge sources such as
	Probase and WordNet, 
	for extracting the 
	most prominent aspects of a given product type  from textual reviews. 
	The proposed method, 
	ExtRA (Extraction of Prominent Review Aspects), 
	(i) extracts the aspect candidates from text reviews based on a
	data-driven approach,
	(ii) builds an aspect graph utilizing the Probase to narrow the aspect space, 
	(iii) separates the space into reasonable aspect clusters by employing a set of	proposed algorithms and finally
	(iv) generates \emph{K} most prominent aspect terms 
	or phrases which do not overlap semantically automatically without supervision from those aspect clusters.
	ExtRA extracts high-quality prominent aspects as well as aspect clusters with little semantic overlap by exploring knowledge sources.
	ExtRA can extract not only words but also phrases as prominent aspects.
	Furthermore, it is general-purpose and can be applied to 
	almost any type of product and service. 
	Extensive experiments show that ExtRA is effective and achieves 
	the state-of-the-art performance on a dataset consisting of 
	different product types.
\end{abstract}

\begin{keyword}Prominent aspect extraction; Unsupervised learning; Topic modeling; Word embedding
\end{keyword}

\end{frontmatter}

\linenumbers

\input{intro}

\input{related}

\input{method}

\input{experiments}

\input{conclusion}

\section*{Acknowledgements}
This work was supported by NSFC grant 61373031
and NSFC-NRF Joint Research Program No. 61411140247.

\section*{References}

\bibliography{extra}

\end{document}
