\documentclass[conference]{IEEEtran}

\usepackage{url,color}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amsmath}
\interdisplaylinepenalty=2500
\usepackage{array}
\usepackage{threeparttable}
\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\tabref}[1]{Table \ref{#1}}

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
\usepackage{stfloats}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
\newcommand{\KZ}[1]{\textcolor{blue}{Kenny: #1}}
\newcommand{\XY}[1]{\textcolor{red}{Xinyu: #1}}
\newcommand{\YF}[1]{\textcolor{blue}{Yifan: #1}}

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Mining topics from source code repositories}



% make the title area
\maketitle

\begin{abstract}
%This paper presents a retrieval based method to achieve action conceptualization,
% which is the process of abstracting action concepts into noun concepts. Action
% concepts are predicate together with argument concepts such as for subject and
% object. For example the noun concept ``acquisition'' would be a good abstraction
% of the action concept ``company buy company''.
% Our work is based on the assumption that the word used in news title are
% usually generalization or abstraction of the event discussed in the news content.
% We use online textual news as our corpus, and build a tripartite graph to model
% the relation between noun, news and action. We subsequently build an action-noun map
% by mining relatedness between noun and action. This work can be useful in various
% domains. As a showcase we build a news search engine with semantic search enabled
% by our conceptualization result. On a human labeled evaluation dataset our method
% outperforms a topic model baseline and a TF-IDF baseline.
We try to design a system to automatically suggest people the themes of all the method
in a code repository. This system can help people better understand and get the information
more quickly. Source code repositories have features that different from ordinary text files
in natural language, which is the significance to establish our model.
Our work is based on a previous model which combines the structural information of a code
snippet and its related description in natural language. We introduced more information,
such as the semantic information, into this model to enlarge the ability to process code
repositories. After inserting the extra information, the experiments on five different
code repositories show that our model performs better than the previous one in MRR and accuracy.
\end{abstract}




% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle



\input{tex/intro}
\input{tex/related}
\input{tex/model}
\input{tex/eval}



\section{Conclusion}
We designed a system to automatically suggest people the themes of all the function in a code repository based on the model applied in [1] which combines the structural information of a code snippet and its related description in natural language. But because we want to mine topics from source code repositories, we add the call graph among functions in the model and split all identifiers which appears in the code. After adding these two changes, our model's results are better than [1]'s model, readers can see more details in section Result.

Our model can only recommend tags for every function now, 


\section*{Acknowledgment}
We thank Miltiadis Allamanis for his help.

\bibliographystyle{IEEEtran}
\bibliography{icdm}

\end{document}
