\section{List of 79 Drugs Studied}
\label{apx:drugs}

\begin{longtable}{m{0.2\textwidth}m{0.12\textwidth}m{0.15\textwidth}m{0.22\textwidth}m{0.12\textwidth}}
%	\centering
%	\caption*{List of Drugs Studied} 
	\label{tab:addlabel} \\
	%		\begin{tabular*}{10cm}{lllll}
%	\begin{supertabular}
		%{p{3cm}p{2cm}p{2cm}p{3cm}p{2cm}}
		%\begin{tabular}{lllll}
		\hline
		\textbf{Category} & \textbf{Drug Name} & \textbf{English Name} & \textbf{Manufactor} & \textbf{Total Num of posts} \\
		\hline
		\textbf{鼻炎 (Rhinitis)} & 雷诺考特 & Rhinocort & AstraZeneca & 8164 \\
		\hline
		\textbf{肺癌 (Lung Cancer)} & 易瑞沙 & Iressa & AstraZeneca & 16481 \\
		\hline
		\multirow{29}[2]{3cm}{\textbf{高血压 (Hypertension)}} & 倍他乐克 & Betaloc & AstraZeneca & 37250 \\
		& 波依定 & Plendil & AstraZeneca & 7089 \\
		& 颉沙坦 & Valsartan & Norvatis & 2468 \\
		& 乌拉地尔 & urapidil & Nycomed GmbH & 151 \\
		& 替米沙坦 & Telmisartan & Boehringer Ingelheim & 1949 \\
		& 瑞泰 & Tritace & Sanofi-Aventis & 380 \\
		& 雅施达 & Acertil & LES LABORATOIRES SERVIER & 1133 \\
		& 科素亚 & Cozaar & Merck Sharp \& Dohme Limited & 2853 \\
		& 海捷亚 & Hyzaar & Merck Sharp \& Dohme Limited & 613 \\
		& 赖诺普利 & lisinopril & AstraZeneca UK Limited & 287 \\
		& 再宁平 & Zanidip & Recordati S.P.A. & 75 \\
		& 乐息平 & Lacipil & GLAXOSMITHKLINE & 693 \\
		& 马来酸伊索拉定 & Gaslon N & Nippon Shinyaku Co.,Ltd. & 29 \\
		& 安博维 & APROVEL & Sanofi Pharma Bristol-Myers Squibb SNC & 2522 \\
		& 寿比山 & Indapamide & Servier & 1773 \\
		& 达爽 & Tanatril & 天津田边制药有限公司 & 386 \\
		& 蒙诺 & Monopril & 中美上海施贵宝制药有限公司 & 1222 \\
		& 多沙唑嗪 & Cardura XL & Pfizer Pharma GmbH & 229 \\
		& 合心爽 & Altiazem & 天津田边制药有限公司 & 1522 \\
		& 卡维地洛片 & Carvedilol & ROCHE S.P.A. & 562 \\
		& 必洛斯 & Blopress & Takeda Pharmaceutical Company Limited & 523 \\
		& 康忻 & Concor &  Merck Serono GmbH & 3104 \\
		& 贝尼地平 & Coniel & Kyowa Hakko Kirin Co.,Ltd. & 180 \\
		& 阿替洛尔 & Atenolol & AMRI India Pvt. Ltd. & 877 \\
		& 尼群地平 & Nitrendipine & Alvogen Malta Operations Ltd & 874 \\
		& 阿尔马尔 & Almarl & Dainippon Sumitomo Pharma Co., Ltd. & 901 \\
		& 络活喜 & Norvasc & Pfizer Australia Pty Limited & 4636 \\
		& 锐思力 & Rasilez & Novartis Pharma Schweiz AG & 2 \\
		& 特拉唑嗪 & Terazosin & Abbott & 1316 \\
		\hline
		\multirow{9}[2]{3cm}{\textbf{他汀类药物 (Statins)}} & 可定 & Crestor & AstraZeneca & 2179 \\
		& 阿伐他汀 & Lipitor & Pfizer Ireland Pharmaceuticals & 134 \\
		& 辛伐他汀 & Simvastatin Tablets & Merck Sharp \&amp; Dohme (Australia) Pty. Ltd. & 1140 \\
		& 普伐他汀 & Pravastatin & 华北制药股份有限公司 & 110 \\
		& 洛伐他汀 & Lovastation & AstraZeneca & 751 \\
		& 氟伐他汀 & Fluvastatin & Novartis & 267 \\
		& 葆至能 & VYTORIN & MSP Singapore Company,LLC & 7 \\
		& 匹伐他汀 & LIVALO KOWA &  Kowa Company, Ltd. & 57 \\
		& 氨氯地平阿托伐他汀 & Amlodipine Besylate and Atorvastatin Calcium Tablets &  Pfizer Inc. & 85 \\
		\hline
		\multirow{2}[2]{3cm}{\textbf{胃酸过多 (GERD)}} & 洛赛克 & Losec & AstraZeneca & 41,957 \\
		& 耐信 & Nexium & AstraZeneca & 12,890 \\
		\hline
		\textbf{急性冠脉综合征 (Acute coronary)} & 倍林达 & BRILINTA & AstraZeneca & 179 \\
		\hline
		\textbf{精神分裂 (Schizophrenia)} & 思瑞康 & Seroquel & AstraZeneca & 10,859 \\
		\hline
		\textbf{麻醉 (Sedation)} & 得普利麻 & Diprivan & AstraZeneca & 578 \\
		\hline
		\textbf{乳腺癌 (Breast Cancer)} & 瑞宁得 & ARIMIDEX & AstraZeneca & 1915 \\
		\hline
		\multirow{18}[2]{3cm}{\textbf{糖尿病\quad (Diabetes)}} & 安立泽 & Onglyza &  Bristol-Myers Squibb Company & 269 \\
		& 百泌达 & BYETTA & Eli Lilly Nederland B.V. & 198 \\
		& 伏格列波糖 & Voglibose & Ranbaxy Laboratories Limited & 419 \\
		& 维格列汀 & Galvus & Novartis Europharm Ltd. & 114 \\
		& 捷诺维 & JANUVIA & Merck Sharp \&amp; Dohme (Australia) Pty Ltd & 208 \\
		& 罗格列酮 & Avandamet & GlaxoSmithKline & 449 \\
		& 瑞格列奈片 & NovoNorm & Novo Nordisk A/S & 1157 \\
		& 吡格列酮 & Actos & Takeda Pharmaceutical Company Limited & 822 \\
		& 赛尼可 & Xenical & Roche Pharma(Schweiz) Ltd & 993 \\
		& 那格列奈片 & Nateglinide Tablet & 北京诺华制药有限公司 & 273 \\
		& 诺和力 & Victoza & Novo Nordisk A/S & 59 \\
		& 长秀霖 & Basalin & 甘李药业股份有限公司 & 530 \\
		& 来得时 & LANTUS & Sanofi-Aventis Deutschland GmbH & 1719 \\
		& 诺和锐 & NovoRapid FlexPen & Novo Nordisk A/S & 1337 \\
		& 格列吡嗪控释片 & Glucotrol XL & Pfizer Inc. & 224 \\
		& 格列美脲片 & Amaryl & Sanofi-Aventis Deutschland GmbH & 771 \\
		& 达美康 & Diamicron MR & Les Laboratoires Servier & 1675 \\
		& 拜唐苹 & Glucobay & Bayer Vital GmbH & 2141 \\
		\hline
		\multirow{15}[2]{3cm}{\textbf{哮喘 (Asthma)}} & 普米克 & Pulmicort & AstraZeneca & 10621 \\
		& 信必可 & Symbicort & AstraZeneca & 8349 \\
		& 安可来 & ACCOLATE & AstraZeneca UK Limited & 14 \\
		& 氨茶碱 & Aminophylline & Sannova Co & 9881 \\
		& 沙丁胺醇 & Salbutamol & EugenPharm Inc, USA & 4028 \\
		& 美普清 & Meptin & 中国大冢制药有限公司 & 4252 \\
		& 吡嘧司特钾 & Pemirolast Potassium Tablets & 河北医科大学制药厂 & 216 \\
		& 盐酸奥洛他定 & Allelock & Kyowa Hakko Kirin Co.,Ltd. & 1414 \\
		& 顺尔宁 & Singulair & Merck Sharp \&amp; Dohme Australia Pty Ltd & 54,621 \\
		& 阿乐迈 & Alomide & s.a. ALCON-COUVREUR n.v. & 108 \\
		& 奥克斯都保 & Oxis Turbuhaler & AstraZeneca AB & 609 \\
		& 舒利迭 & Seretide & Glaxo Wellcome UK Limited & 19147 \\
		& 依匹斯汀 & Alesion & Nippon Boehringer Ingelheim Co.,Ltd. & 296 \\
		& 阿米迪 & Amiaid & Nitto Denko Corporation & 1601 \\
		& 帮备 & Bambec & AstraZeneca & 313 \\
		\hline
		\textbf{Total} & 
		\multicolumn{3}{l}{} 
		& \textbf{302,180} \\
       	\hline
%	\end{supertabular}
\end{longtable}%

