% sage_latex_guidelines.tex V1.20, 14 January 2017

\documentclass[Afour,sageh,times]{sagej}

\usepackage{moreverb,url}

\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}

\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\def\volumeyear{2018}

\usepackage[ruled]{algorithm2e}
%\usepackage{algorithmic}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{times,epsfig,proof,url}
\usepackage{epsfig}
\usepackage{epstopdf}
\usepackage{listings}
\usepackage{subfig}
%\usepackage{lipsum}
%%\usepackage{subfigure}
%\usepackage{multicol,multirow}
%%\usepackage{algorithm}
%\usepackage[noend]{algpseudocode}
%\usepackage{textcomp}
%\usepackage{color}
%%\usepackage[lined,algonl,ruled]{algorithm2e}
%% \usepackage{subfigure}
%\usepackage{graphicx}
%\usepackage[T1]{fontenc}
%%\usepackage{subfloat}
%
\newcommand{\secref}[1]{Section \ref{#1}}
\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\tabref}[1]{Table \ref{#1}}
\newcommand{\equref}[1]{Equation (\ref{#1})}
%\renewcommand{\algorithmicrequire}{\textbf{Input:}} 
%\renewcommand{\algorithmicensure}{\textbf{Output:}}

\begin{document}

\runninghead{}

\title{Fault-tolerant Information Extraction from Semi-structured OCR Images}
%\author{}
%\corrauth{}
%\email{}

\begin{abstract}
Optical character recognition (OCR) has been widely used in digitizing scanned
documents into text. Good results have been achieved in applying OCR to textual
documents such as novels and reports where the 
content is virtually all words, and in many languages. 
For semi-structured documents that combine graphics and words,
such as medical images, extraction of useful textual information is difficult
due to the discontinuity of text flows. In this paper, we 
propose a spatial, fault-tolerant description language that allows users to 
specify a rough format of the image along with type information and
constraints. 
%Our work can be regarded as preprocessing of the information 
%extracting process since it takes the semi-structured data as the input 
%and transforms the data into a form which is more structured and 
%with useless noises removed so that the downstream extraction of 
%information can be easier. 
The evaluation engine of this language automatically generates a
reliable parser of the OCR output from an image according to 
its description. This parser extracts all useful textual components specified
by the description. Moreover, the system allows
the user to make incremental corrections to parsing results 
and learns from these corrections so as to make better parses in future. 
Our experimental results show
that this system outperforms existing academic and commercial systems by
substantial margins in terms of extraction accuracy.
\end{abstract}

%\keywords{Class file, \LaTeXe, \textit{SAGE Publications}}

\keywords{Information extraction, optical character recognition, document analysis, 
description language, fuzzy parser, spatial information, 
medical images, medical information systems
}
\maketitle


\input{intro}
\input{approach}
\input{syntax}
\input{semantics}
\input{correction}
\input{eval}
\input{discuss}
\input{related}
\input{conclusion}


%\begin{thebibliography}{99}
%\bibitem[Kopka and Daly(2003)]{R1}
%Kopka~H and Daly~PW (2003) \textit{A Guide to \LaTeX}, 4th~edn.
%Addison-Wesley.
%
%\bibitem[Lamport(1994)]{R2}
%Lamport~L (1994) \textit{\LaTeX: a Document Preparation System},
%2nd~edn. Addison-Wesley.
%
%\bibitem[Mittelbach and Goossens(2004)]{R3}
%Mittelbach~F and Goossens~M (2004) \textit{The \LaTeX\ Companion},
%2nd~edn. Addison-Wesley.
%
%\end{thebibliography}

\bibliographystyle{SageH}
\bibliography{ocr.bib}

\end{document}
