\section{Conclusion}
\label{sec:conclusion}
In this paper, we tackle the real-world slot filling task 
in a novel Chinese online shopping assistant system. 
We proposed a deep multi-task sequence learning framework with 
cascade and residual connection. 
Our model achieves comparable results with 
several state-of-the-art models on the common slot filling dataset ATIS. 
On our real-world Chinese E-commerce dataset ECSA, 
our proposed model DCMTL also achieves best F1 score comparing 
to several strong baselines.
DCMTL have already been deployed on the online E-commerce shopping assistant of Taobao.
Online testing results show that our model meets better understanding of users utterances
and improves customer’s shopping experience.

Our future research may include a joint model for category classification 
and slot filling.
Active learning for slot filling can also be investigated by involving human-beings interaction with our system.
We will also continue to explore new model architectures.
For example, attention mechanism can be involved in our model (e.g. self-attention) \cite{tan2017deep,vaswani2017attention}.
Despite the tremendous potential for further improvements on
this task of slot filling for shopping assistant or
E-commerce conversational search,
the results in this paper already demonstrate a significant
first step forward in real-world application,
which can be incorporated into and improve
any of the aforementioned conversational technologies,
and have shown that deep multi-task sequence labeling
is a promising approach for this task.

%\KZ{I think one of the most important contributions is the release of the
%taobao slot filling data set. However, this data set have to be high quality.
%Maybe you can sample some to get human to examine it and give an human/machine correlation score. If the quality is indeed high, u %should def claim this as
%a major contribution in the intro.}
