\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables

% Copyright
\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

%Conference
\acmConference[CIKM'18]{The 2018 Conference on Information and Knowledge Management}{October 2018}{Lingotto, Turin, Italy} 
\acmYear{2018}

\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{CJKutf8}
\usepackage{epsfig}
\usepackage{algorithm, algpseudocode}
\usepackage{algpseudocode}
\usepackage{booktabs}
\usepackage{multirow}

\usepackage{makecell}
\usepackage{CJKutf8}
\usepackage{epsfig}
\usepackage{algorithm, algpseudocode}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{color}
\usepackage{subfigure}
\usepackage{url}
\usepackage{mathrsfs}
\usepackage{amsmath}

\usepackage{url}


\newcommand\BibTeX{B{\sc ib}\TeX}
\newcommand{\secref}[1]{Section \ref{#1}}
\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\eqnref}[1]{Eq. (\ref{#1})}
\newcommand{\exref}[1]{Example \ref{#1}}
\newcommand{\algoref}[1]{Algorithm \ref{#1}}
\newcommand{\tabref}[1]{Table \ref{#1}}
\newcommand{\bi}[1]{\textbf{\textit{#1}}}

\newcommand{\yu}[1]{{\bf \color{orange} [[Yu says ``#1'']]}}
\newcommand{\xusheng}[1]{{\bf \color{blue} [[Xusheng says ``#1'']]}}
\newcommand{\KZ}[1]{{\bf \color{red} [[Kenny says ``#1'']]}}

\newcommand{\lstm}{\operatornamewithlimits{LSTM}}
\newcommand{\bilstm}{\operatornamewithlimits{BiLSTM}}
\newcommand{\argmax}{\operatornamewithlimits{argmax}}
\newcommand{\seg}{\operatornamewithlimits{seg\_tag}}
\newcommand{\ner}{\operatornamewithlimits{ne\_tag}}
\newcommand{\slot}{\operatornamewithlimits{slot\_fill}}
\newcommand{\batch}{\operatornamewithlimits{Batch}}

\begin{document}
\title{Deep Cascade Multi-task Learning for Slot Filling in \\ Chinese Online Shopping Assistant}

%\subtitle{Extended Abstract}



\author{
	Yu Gong$^1$ \footnotemark[1], 
	Xusheng Luo$^2$ \footnotemark[1], 
	Kenny Q. Zhu$^3$ \footnotemark[2],
	Xi Chen$^4$,
	Yunlun Yang$^5$,
	Jiawei Wu$^6$,
	Wenwu Ou$^7$
}
\affiliation{
  \institution{$^1$ $^2$ $^4$ $^5$ $^6$ $^7$ Search Algorithm Team, Alibaba Group \\
  		$^3$ Shanghai Jiao Tong University}}
\email{{gongyu.gy, lxs140564}@alibaba-inc.com, kzhu@cs.sjtu.edu.cn, gongda.cx@taobao.com}
\email{{yunlun.yyl,wujiawei}@alibaba-inc.com, santong.oww@taobao.com}

%\author{John Smith}
%\affiliation{\institution{The Th{\o}rv{\"a}ld Group}}
%\email{jsmith@affiliation.org}

%\author{Julius P.~Kumquat}
%\affiliation{\institution{The Kumquat Consortium}}
%\email{jpkumquat@consortium.net}

% The default list of authors is too long for headers.
\renewcommand{\shortauthors}{Y. Gong et al.}
\renewcommand{\authors}{Yu Gong, Xusheng Luo, Kenny Q. Zhu, Xi Chen, Yunlun Yang, Jiawei Wu, Wenwu Ou}
\renewcommand{\shorttitle}{DCMTL Slot Filling in Chinese Online Shopping Assistant}

\begin{abstract}
Slot filling is a critical task in natural language understanding
(NLU) for dialog systems.
State-of-the-art approaches treat it as a sequence labeling problem
and adopt such models as BiLSTM-CRF.
While these models work relatively well on standard 
benchmark datasets, they face challenges in the context of
Chinese E-commerce where the slot labels are more informative
and carry richer expressions.
In this work, we propose a novel multi-task model
with cascade and residual connections, and
jointly learns segment tagging, named entity tagging and slot filling.
Experiments show the effectiveness of the proposed
cascade and residual structures. 
Our model has a 14.6\% advantage in F1
score over the strong baseline methods on a new Chinese E-commerce
shopping assistant dataset, while achieving competitive accuracies on
a standard dataset.  
Furthermore, online test in the operational system of Taobao search 
shows 130\% improvement on accuracy of understanding user utterances.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%


%\ccsdesc[500]{Computer systems organization~Embedded systems}
%\ccsdesc[300]{Computer systems organization~Redundancy}
%\ccsdesc{Computer systems organization~Robotics}
%\ccsdesc[100]{Networks~Network reliability}


%\keywords{ACM proceedings, \LaTeX, text tagging}


\maketitle

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\footnotetext[1]{Equal contribution.}
\footnotetext[2]{Corresponding author.}
\renewcommand{\thefootnote}{\arabic{footnote}}

\begin{CJK}{UTF8}{gbsn}
	
	\input{intro}
	
	\input{problem}
	
	\input{approach}
	
	\input{experiment}
	
	\input{related}
	
	\input{conclusion}
	
\end{CJK}

\bibliographystyle{ACM-Reference-Format}
\bibliography{ref}

\end{document}
