% This must be in the first 5 lines to tell arXiv to use pdfLaTeX, which is strongly recommended.
\pdfoutput=1
% In particular, the hyperref package requires pdfLaTeX in order to break URLs across lines.

\documentclass[11pt]{article}

% Remove the "review" option to generate the final version.
\usepackage[]{EMNLP2023}

% Standard package includes
\usepackage{times}
\usepackage{latexsym}

% For proper rendering and hyphenation of words containing Latin characters (including in bib files)
\usepackage[T1]{fontenc}
% For Vietnamese characters
% \usepackage[T5]{fontenc}
% See https://www.latex-project.org/help/documentation/encguide.pdf for other character sets

% This assumes your files are encoded as UTF8
\usepackage[utf8]{inputenc}

% This is not strictly necessary, and may be commented out.
% However, it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

% This is also not strictly necessary, and may be commented out.
% However, it will improve the aesthetics of text in
% the typewriter font.
\usepackage{inconsolata}

%my packages
\usepackage{times}
\usepackage{soul}
\usepackage{url}
\usepackage{microtype}
\usepackage[utf8]{inputenc}
\usepackage{color}
\usepackage{epsfig}
\usepackage{booktabs}
\usepackage{courier}
\usepackage{array}
\usepackage{multicol}
%\usepackage{threeparttable}
\usepackage{epstopdf}
\usepackage{listings}
\usepackage{multirow}
%\usepackage{subfigure}
\usepackage{ragged2e}
\usepackage{xassoccnt}
%\usepackage{amsmath,amsfonts,amssymb,amsthm,amsopn}
\usepackage{colortbl}
\definecolor{mygray}{gray}{.9}
%\newcommand{\ft}[1]{\textsc{#1}}
\newtheorem{example}{Example}
\newcommand{\secref}[1]{Section \ref{#1}}
\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\eqnref}[1]{Eq. (\ref{#1})}
\newcommand{\tabref}[1]{Table \ref{#1}}
\newcommand{\exref}[1]{Example \ref{#1}}
\newcommand{\cut}[1]{}
%\newcommand{\citealp}[1]{\citeauthor{#1}~\shortcite{#1}}
\newcommand{\KZ}[1]{\textcolor{blue}{Kenny: #1}}
\newcommand\BibTeX{B\textsc{ib}\TeX}
\usepackage{amsmath}
\newcommand{\sgn}{\text{sgn}}
\usepackage[section]{placeins}
\usepackage{afterpage}
%\newcommand{\sgn}{\operatorname{sgn}}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}


% If the title and author information does not fit in the area allocated, uncomment the following
%
%\setlength\titlebox{<dim>}
%
% and set <dim> to something 5cm or larger.

\title{Statistically Profiling Biases in Natural Language Reasoning Datasets and Models}

% Author information can be set in various styles:
% For several authors from the same institution:
% \author{Author 1 \and ... \and Author n \\
%         Address line \\ ... \\ Address line}
% if the names do not fit well on one line use
%         Author 1 \\ {\bf Author 2} \\ ... \\ {\bf Author n} \\
% For authors from different institutions:
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \And  ... \And
%         Author n \\ Address line \\ ... \\ Address line}
% To start a seperate ``row'' of authors use \AND, as in
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \AND
%         Author 2 \\ Address line \\ ... \\ Address line \And
%         Author 3 \\ Address line \\ ... \\ Address line}

\author{Shanshan Huang \\ 
        Shanghai Jiao Tong University \\
	Shanghai, China\\
        \texttt{huangss\_33@sjtu.edu.cn} 
        \\\And
        Kenny Q. Zhu\thanks{~~The corresponding author.} \\
        University of Texas at Arlington  \\
	Arlington, Texas, USA\\
        \texttt{kenny.zhu@uta.edu} 
        \\}


\iffalse
\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\}
\fi
\begin{document}
\maketitle
\begin{abstract}
Recent studies have shown that many natural language understanding and reasoning datasets contain statistical cues that can be exploited by NLP models, resulting in an overestimation of their capabilities. Existing methods, 
such as ``hypothesis-only'' tests and CheckList, 
are limited in identifying these cues and evaluating model weaknesses.
We introduce ICQ (I-See-Cue), a lightweight, general statistical profiling framework that automatically identifies potential biases in multiple-choice NLU datasets without requiring additional test cases. ICQ assesses the extent to which models exploit these biases through black-box testing, addressing the limitations of current methods. In this work, we conduct a comprehensive evaluation of statistical biases in 10 popular NLU datasets and 4 models, confirming prior findings, revealing new insights, and offering an online demonstration system to encourage users to assess their own datasets and models.
Furthermore, we present a case study on investigating ChatGPT's bias, providing valuable recommendations for practical applications.



\end{abstract}
\input{intro}
\input{formulation}
\input{approach}
\input{experiment}
\input{case}
\input{related}
\input{conclusion}


\bibliography{anthology,custom}
\bibliographystyle{acl_natbib}


\end{document}
