 \section{Applications}
\label{sec:application}
AliCoCo has already supported a series of downstream applications in Alibaba's ecosystem, especially in search and recommendation, two killer applications in e-commerce.
In this section, we introduce some cases we already succeed, those we are attempting now, and some other we would like to try in the future.

\subsection{E-commerce Search}

\subsubsection{Search relevance}
% 直接用isa关系，搜索相关性1个点的auc, 线上bad case下降4%

Relevance is the core problem of a search engine, and one of the main challenges is the vocabulary gap between user queries and documents. 
This problem is more severe in e-commerce since language in item titles is more professional. 
Semantic matching is a key technique to bridge the gap in between to improve relevance.
IsA relations is important in semantic matching. 
For example, if a user search for a ``top'', search engine may classify those items whose title only contains ``jacket'' but without ``top'' as irrelevance.
Once we have the prior knowledge that ``jacket is a kind of top'', 
this case can be successfully solved.
Comparing to a former category taxonomy, which only has 15k different category words and 10k isA relations,
AliCoCo containing 10 times categories words and isA relations.
Offline experiments show that our data improves the performance of the semantic matching model by $1\%$ on AUC, 
and online tests show that the number of relevance bad cases is dropped by $4\%$, meaning user satisfaction is improved.

\subsubsection{Semantic search \& question answering}
% semantic search，本体的理解
As shown in \figref{fig:cloud}(a),
semantic search empowered by AliCoCo is ongoing at the time of writing. 
Similar to searching ``China'' on Google and then getting a knowledge card on the page with almost every important information of China, 
we are now designing a more structured way to display the knowledge of ``Tools you need for baking'' once a customer searching for ``baking''.
On the other hand, this application requires a high accuracy and recall of relations, which are still sparse in the current stage of AliCoCo.
Question answering is a way of demonstrating real intelligence of a search engine. 
Customers are used to keyword based search for years in e-commerce.
However, at some point we may want to ask an e-commerce search engine ``What should I prepare for hosting next week's barbecue?''. 
We believe AliCoCo is able to provide ample imagination towards this goal with continuous efforts to integrate more knowledge especially concerning common sense.

\subsection{E-commerce Recommendation}

\subsubsection{Cognitive recommendation}
% 云主题，0-1全新的产品，用户体感提升，推荐创新
As we introduce in \secref{sec:intro},
a natural application of e-commerce concepts is directly recommending them to users together with 
its associated items.
In the snapshot shown in \figref{fig:cloud}(b), concept ``Tools for Baking'' is displayed as a card, with the picture of a representative item.
Once users click on this card, 
it jumps to a page full of related items such as egg scrambler and strainer.
We perform thorough offline and online experiments in a previous work
\cite{luo2019conceptualize}.
It has already gone into production for more than 1 year with high click-through rate and satisfied GMV (Gross Merchandise Value).
According to a survey conducted by online users, 
this new form of recommendation brings more novelty and further improve user satisfaction. 
This application is totally based on the complete functionality of AliCoCo, which demonstrates its great value and potential. 



\subsubsection{Recommendation reason}

% 推荐理由，正在尝试
The advantages of e-commerce concepts include its clarity and brevity, which make them perfect recommendation reasons to display when recommending items to customers.
This idea is currently experimented at the time of writing.


