\section{Evaluations}
\label{sec:eval}
In this section, we first give a statistical overview of AliCoCo.
Next we present experimental evaluations for five main technical modules 
during the construction of AliCoCo.

\subsection{Overall Evaluation}

\tabref{tab:data} shows the statistics of AliCoCo.
%~\footnote{We attempt to release an API for visiting AliCoCo in the near future.}.
There are $2,853,276$ primitive concepts and $5,262,063$ e-commerce concepts in total at the time of writing.
There are hundreds of billions of relations in AliCoCo, including $131,968$ isA relations within \textit{Category} in the layer of primitive concepts and $22,287,167$ isA relations in the layer of e-commerce concepts.
For over $3$ billion items in Alibaba, $98\%$ of them are linked to AliCoCo.
Each item is associated with $14$ primitive concepts and $135$ e-commerce concepts on average.
Each e-commerce concept is associated with $74,420$ items on average.
The number of relations between e-commerce concept layer and primitive concept layer is $33,495,112$.

AliCoCo is constructed semi-automatically.
For those nodes and relations mined by models, 
we will randomly sample part of data and ask human annotators to label.
Only if the accuracy achieves certain threshold,
the mined data will be added into AliCoCo to ensure the quality.
Besides, for those dynamic edges (associated with items),
we monitor the data quality regularly.


\begin{table}[th]
%	\centering
	\small
	\begin{tabular}{|l|l|l|l|}
		\hline
		\multicolumn{4}{|l|}{\textbf{Overall}} \\ 
		\hline
		\multicolumn{2}{|l|}{\# Primitive concepts} &
		\multicolumn{2}{l|}{2,853,276}  \\
		\hline
		\multicolumn{2}{|l|}{\# E-commerce concepts} &  
		\multicolumn{2}{l|}{5,262,063}  \\ 
		\hline
		\multicolumn{2}{|l|}{\# Items} &
		\multicolumn{2}{l|}{> 3 billion} \\ 
		\hline
		\multicolumn{2}{|l|}{\# Relations} &
		\multicolumn{2}{l|}{> 400 billion} \\ 
		\hline
		\hline
		\multicolumn{4}{|l|}{\textbf{Primitive concepts}} \\ 
		\hline
		\# Audience &\# Brand &\# Color &\# Design  \\
		\cline{1-4}
		15,168 & 879,311 & 4,396 & 744 \\
		\cline{1-4}
		\# Event & \# Function & \# Category &\# IP  \\
		\cline{1-4}
		 18,400 & 16,379 & 142,755 & 1,491,853
		  \\
		\cline{1-4}
		\# Material & \# Modifier & \# Nature &\# Organization  \\
		\cline{1-4}
		 4,895 & 106 & 75 & 5,766 \\
		\cline{1-4}
		\# Pattern & \# Location & \# Quantity &\# Shape  \\
		\cline{1-4}
		 486 & 267,359 & 1,473 & 110 \\
		\cline{1-4}
		\# Smell & \# Style & \# Taste &\# Time  \\
		\cline{1-4}
		 9,884 & 1,023 & 138 & 365 \\
		\hline
		\hline
		\multicolumn{4}{|l|}{\textbf{Relations}} \\ 
		\hline
		\multicolumn{2}{|l|}{\# IsA in primitive concepts} &
		\multicolumn{2}{l|}{131,968 (only in \textit{Category})}  \\
		\hline
		\multicolumn{2}{|l|}{\# IsA in e-commerce concepts} &
		\multicolumn{2}{l|}{22,287,167}  \\
		\hline
		\multicolumn{2}{|l|}{\# Item - Primitive concepts} &
		\multicolumn{2}{l|}{21 billion}  \\
		\hline
		\multicolumn{2}{|l|}{\# Item - E-commerce concepts} &
		\multicolumn{2}{l|}{405 billion}  \\
		\hline
		\multicolumn{2}{|l|}{\# E-commerce - Primitive cpts} &
		\multicolumn{2}{l|}{33,495,112}  \\
		\hline
		%		\bottomrule
	\end{tabular}
	\caption{Statistics of AliCoCo at the time of writing.}
	\label{tab:data}
\end{table}

To evaluate the coverage of actual shopping needs of our customers, we sample $2000$ search queries at random and manually rewrite them into coherent word sequences, then we search in AliCoCo to calculate the coverage of those words. 
We repeat this procedure every day, in order to detect new trends of user needs in time. 
AliCoCo covers over $75\%$ of shopping needs on average in continuous $30$ days, while this number is only $30\%$ for the former ontology mentioned in \secref{sec:intro}.


\input{exp_vocab}
\input{exp_isa}
\input{exp_concept}
\input{exp_linking}
\input{exp_match}