\section{Overview} 
\label{sec:overview}


AliCoCo provides an alternative to describing and understanding user needs and items in e-commerce within the same, universal framework.
As shown in \figref{fig:overview}, 
AliCoCo consists of four components:
\textbf{E-commerce Concepts}, \textbf{Primitive Concepts}, \textbf{Taxonomy} and \textbf{Items}.


As the core innovation, 
we represent various user needs as \textbf{E-commerce Concepts} (orange boxes) in the top layer of \figref{fig:overview}.
E-commerce concepts are short, coherent and plausible phrases such as ``outdoor barbecue'', ``Christmas gifts for grandpa''
or ``keep warm for kids'', which describe specific shopping scenarios.
User needs in e-commerce are not formally defined previously,
hierarchical categories and browse nodes \footnote{\url{https://www.browsenodes.com/}} are usually used to represent user needs or interests \cite{zhou2018deep}.
However, we believe user needs are far broader than categories or browse nodes. 
Imaging a user who is planning an outdoor barbecue, or who is concerned with how to get rid of a raccoon in his garden.
They have a situation or problem but do not know what products can help.
Therefore, user needs are represented by various concepts in AliCoCo,
and more details will be introduced in \secref{sec:ecommerce}.


To further understand high-level user needs (aka. e-commerce concepts), 
we need a fundamental language to describe each concept.
% as structured \textit{<property: value>} pairs. 
For example, ``outdoor barbecue'' can be expressed as ``\textit{<Event: Barbecue>} | \textit{<Location: Outdoor>} | \textit{<Weather: Sunny>} | ...''.
Therefore, 
we build a layer of \textbf{Primitive Concepts}, where
``primitive'' means concept phrases in this layer are relatively short and simple such as ``barbecue'', ``outdoor'' and ``sunny'' (blue boxes in \figref{fig:overview}), 
comparing to e-commerce concepts above which are compound phrases in most cases.
To categorize all primitive concepts into classes, a \textbf{Taxonomy} in e-commerce is also defined, where classes with different granularities form a hierarchy via \textit{isA} relations.
For instance, there is a path top-down being ``\textit{Category->ClothingAndAccessory->Clothing->Dress}'' in the taxonomy (purple ovals in \figref{fig:overview}) .

%From the highest and coarsest classes such as 
%``\textit{Time}'', ``\textit{Location}'' and  ``\textit{Category}'', classes gradually become more fine-grained. 
%For instance, there is a path top-down being ``\textit{Category->ClothingAndAccessory->Clothing->Dress}'' in the taxonomy.
We also define a schema on the taxonomy, 
to describe relations among different primitive concepts. For example, there is a relation ``\textit{suitable\_when}'' defined between ``class:\textit{ Category-Clothing->Pants}'' and ``class: \textit{Time->Season}'', so the primitive concept ``cotton-padded trousers'' is ``suitable\_when'' the season is ``winter''. 

In the layer of \textbf{Items}, billions of items \footnote{Items are the smallest selling units on Alibaba. Two iPhone Xs Max (each of them is an item) in two shops have different IDs.} on Alibaba are related with both primitive concepts and e-commerce concepts.
Primitive concepts are more like the properties of 
items, such as the color or the size.
However, the relatedness between e-commerce concepts and items represents that certain items are necessary or suggested under a particular shopping scenario. 
As the example shown in \figref{fig:overview},
items such as grills and butter are related to the e-commerce concept ``outdoor barbecue'', 
while they can not be associated with the primitive concept ``outdoor'' alone.

Overall, we represent user needs as e-commerce concepts, then adopt primitive concepts with a class taxonomy to describe and understand both user needs and items in the same framework. 
Besides, e-commerce concepts are also associated directly with items, to form the complete structure of AliCoCo.



%categories, brands respectively, mainly adopting the idea of semantic matching \cite{huang2013learning, shen2014learning}.
%It should be noticed that there is a hierarchy within each domain. For example, ``Shanghai'' is a city in ``China'' in the domain of \textit{Location} and ``pregnancy'' is a special stage of a ``woman'' in the domain of \textit{Object}.  Vocabulary terms at different levels can be combined and result in different concepts.
%Accordingly, those concepts are naturally related to form a hierarchy as well.
%Besides the vocabularies to describe concepts, there are constraints to each concept. 
%The aspects of concept \textit{schema} include
%\textit{gender}, \textit{life stage} \footnote{Life stage is divided into: pregnancy, infant, kindergarten, primary school, middle school and high school in Taobao.}, etc.
%which actually corresponds to user profile.
%For example, the schema of ``Breakfast for Pregnancy'' will be ``\textit{gender}: female, \textit{life stage}: pregnancy'', which indicates the group of users who are most likely to need this concept.




%user needs are conceptualized as ``concepts'' which include a set of particular items in e-commerce.
%Generally, a concept is a fluent short phrase which contains clear semantic meaning and appeals to common sense.
%Furthermore, we divided various concepts into two main types: \textbf{shopping scenarios} such as ``Family Barbecue'', ``European Baking'' or ``Keep warm for Kids'', may consisting of items from several categories,
%and \textbf{extensible categories} such as ``Shoes'', ``Bohemian Dress'', or ``Messi Shoes for Kids'', representing needs for a specific category \footnote{The range of extensible categories is much larger than existing standard categories. We basically regard every product type appeared in human language as our category.} with unlimited constraints.
%In order to cover as many user needs as possible, we generate concepts from two perspectives:
%1) mine enormous raw concept phrases from large amount of query logs, product titles and open-domain web texts.
%2) generate more complex concepts using existing concepts through combination.

%
%In order to understand raw concept phrases and then organize concepts to form a structural network or graph, we define the schema of concept nodes, the core components of AliNet as below:
%
%\noindent
%\textbf{Attributes}
%
%\noindent
%Based on years of experience in e-commerce,
%we express each concept using values drawn from 8 different domains of
%an ``e-commerce concept vocabulary'', which is shown in \figref{fig:kg} (b).
%For example, ``Outdoor Barbecue'' can be written as 
%``\textit{Location}: outdoor, \textit{Incident}: barbecue'', 
%and ``Breakfast for Pregnancy'' can be written as ``\textit{Object}: pregnant women, \textit{Cate/Brand}: breakfast''.
%This vocabulary can be seen as a external semantic universe for concept understanding.
%We construct this vocabulary by integrating WordNet\cite{miller1998wordnet}, Wikipedia\footnote{\url{https://www.wikipedia.org/}} and other general knowledge bases.
%
%\noindent
%\textbf{Relations}
%
%\noindent 
%Concepts are related to representative items, categories, brands respectively, to form the complete concept net.
%Besides 3 \textit{related\_to} relations between concepts and 3 existing nodes in e-commerce, we define another 13 relations within different concepts such as: \textit{isA}, \textit{used\_for}, \textit{part\_of}, etc.
%It should be noticed that there is a hierarchy within each domain mentioned above. For example, ``Shanghai'' is a city in ``China'' in the domain of \textit{Location} and ``pregnancy'' is a special stage of a ``woman'' in the domain of \textit{Object}.  Vocabulary terms at different levels can be combined and result in different concepts.
%Accordingly, those concepts are naturally related to form a hierarchy as well.
%

\input{taxonomy}
\input{primitive}
\input{ecommerce}
\input{item}