\section{Related Work}
\label{sec:related}

Great human efforts have been devoted to construct open domain KGs such as Freebase \cite{bollacker2008freebase} and DBpedia \cite{auer2007dbpedia}, 
which typically describe specific facts with well-defined type systems rather than inconsistent concepts from natural language texts. 
Probase \cite{wu2012probase} constructs a large-scale probabilistic taxonomy of concepts, organizing general concepts using isA relations. 
Different from AliCoCo, concepts in Probase do not have classes so that semantic heterogeneity is handled implicitly.
From this perspective, the structure of AliCoCo is actually more similar to KGs with a type system such as Freebase.
ConceptNet \cite{speer2012representing} tries to include common sense knowledge by recognizing informal relations between concepts, where the concepts could be the conceptualization of any human knowledge such as ``games with a purpose'' appearing in free texts.
%Our e-commerce concept net is entirely focusing on conceptualizing user needs in e-commerce.
Inspired by the construction of open-domain KGs, different kinds of KGs in e-commerce are constructed
%, in order to tackle different challenges in e-commerce scenario.
%Generally, KGs in e-commerce 
to describe relations among users, items and item attributes \cite{catherine2017explainable,ai2018learning}.
One famous example is the ``Product Knowledge Graph'' (PG) \footnote{\url{http://conferences.cis.umac.mo/icde2019/wp-content/uploads/2019/06/icde-2019-keynote-luna-dong.pdf}} of Amazon, another e-commerce giant in the world. The major difference is that they do not focus on user needs as we do.
In AliCoCo, we formally define user needs and introduce a new type of nodes named e-commerce concepts to explicitly represent various shopping needs and further link them to the layer of primitive concepts for semantic understanding. 
Although we do not discuss much, AliCoCo can be connected to open-domain KGs through the layer of primitive concepts (e.g. IP, Organization, etc) just like PG, 
making it more powerful.

