\section{Related Work}
In this section, we discuss works in the area of news recommendation and session-based recommendation in news and other domains like e-commerce or music, and we also compare them with our proposed approach.

\subsection{News Recommendation}
First, the news recommendation task can be formulated as conventional recommendation tasks, the account of a user is reserved and articles are recommended based on users' long-term click history. Some works use a well-designed graph network to represent the target user and the clicked article~\cite{hu2020graph,ge2020graph}.
In this situations, the relation of items and users are well exploited. Unfortunately, in real-time scenarios, new articles and anonymous users emerge, causing a severe cold-start problem. Then if we want to capture users' preferences
within sessions and recommend articles with their several interactions as input, this kind of approach with the static user-item matrix is not suitable. Some propose incremental matrix factorization algorithm based on classic MF algorithm by adding a new user or a new article to the matrices with a random initialization~\cite{al2018adaptive}, and others apply meta-learning which aims to train a model that can rapidly adapt to a new task with a few examples~\cite{lee_melu:_2019}, but do not solve the problem fundamentally.

Second, some news recommendation systems use clicked articles to represent a user, which can be adaptive to anonymous users. Some of them encode the article text with fine-grained attention mechanism~\cite{zhu2019dan,wu_neural_2019-1,wu2019npa,wang2020fine}, some consider the relation between the dwell time of the user and satisfaction of the user~\cite{wu2020CPRS}, and others use the knowledge graph of entities in the news title as affiliated information~\cite{wang2018dkn,wang_ripplenet:_2018}. They mainly focus on the textual feature of articles in order to aggregate users' preference while paying less attention to the click behavior. Although they can be applied for anonymous users by replacing long-term history clicks with articles within the session when fetching user representations, challenges are that they cannot take full advantage of the textual information due to the limited interactions and the overload of training cannot be avoided. Besides, they evaluate their methods by classifying the real clicked article and several constructed distractors from the impression list, and this is not consistent with the real recommendation scenario, where the recommender retrieves top-K recommendation lists from all candidates.

For the rest of the work, one uses the information of how frequent user returns to help improve recommendation~\cite{zheng2018drn}, another work jointly models click, unclick and dislike as explicit/implicit feedback~\cite{xie2020deep}, and others excavate the quality of news articles~\cite{lu_quality_2019} or the backtracking behavior as the user feedback~\cite{smadja_understanding_2019}.
\subsection{Session-based News Recommendation}
\label{sec:related session}
Many online recommender systems are proposed to deal with the session-based scenarios~\cite{epure_recommending_2017,zhou_variational_2019}, where the user interaction information is limited and items are increasingly generated. Usually session-based news recommendation approaches integrate content-based similarity~\cite{sottocornola2018session}, and many of them introduce external knowledge to recommend top-K similar articles~\cite{symeonidis2021session,sheu2020context,sheu2021knowledge}. Some recommenders consider the past sessions of the same user~\cite{zhang2019dynamic,zhang2018deep}, which is not consistent with our anonymous settings, and that is why we do not compare experiment results with them.

Many other session-based recommenders are in the e-commerce domain, which can also be converted to deal with news articles. Here RNN, LSTM and GNN possess properties that make them attractive for sequence modeling of user sessions~\cite{guo_streaming_2019,hidasi2015session,wang2019modeling,gabriel2019contextual,wu2019session}. Further, a hybrid encoder with an attention mechanism is introduced to model the sequential behavior of users~\cite{li2017neural,liu2018stamp,xu2019time,song_islf_2019,zhang_feature-level_2019}. 
Besides, many sequential recommendation systems~\cite{pereira2019online,xu2019graph} on music listening, games playing construct assorted RNN-related architectures (e.g, RCNN~\cite{xu_recurrent_2019}, GRU~\cite{hidasi2018recurrent}, HGN~\cite{xiao2019hierarchical,ma2019hierarchical}), showing RNN's high capacity to modeling user shift preference.

Although above works naturally take the content information and preference shifting into account, the implicit user feedback are neglected. When sampling negative articles, an adaptive negative sampling method based on GAN is proposed~\cite{wang_neural_2018}. Beyond that, few works pay attention to the implicit meaning of negative samples. Randomly sampling from such continuously increasing and high-volume news articles might be fast but will not be effective enough.

\subsection{The Use of Temporal Information}
Sequence and Time-Aware Neighborhood (STAN)~\cite{garg2019sequence} takes vanilla SKNN as its special case. They build static time decay functions for three factors: the position of an item in the current session, recency of a past session w.r.t. to the current session, and the position of a recommendable item in a neighboring session. This approach can be regarded as rule-based SKNN, with exponential decay function, and the experiment result on e-commerce websites even outperforms some deep-learning-based approaches. 
In the deep learning model, some works design different temporal kernel functions or decay functions for different consumption scenarios~\cite{wang2020make,wu2020deja,zhang2019dynamic}. However, these functions of news articles is fixed, which may undermine the ability to model user's short-term preferences towards different articles. Dwell time is considered in~\cite{wu2020CPRS} as the user satisfaction, but the difference of users' reading speed is hard to capture in our session-based scenario. A time-interval-based GRU is proposed to model user session-level representations~\cite{lei_tissa_2019}, and some work~\cite{rakkappan2019context,xu2019time,wu_recommender_2019} treat the time feature of interactions as a temporal context, while they fail to consider the publishing/click/active time in the different dimension.
