\section*{Ethical Statement}
\label{sec:ethics}

Our research abides by the existing ethics standards, and we make every effort to 
protect the privacy of the online users.

When collecting the posts of users in Weibo Depression Super Topic Community, we anonymize the users and never disclose their personal information. All information we store and process is
public information open to everyone on the Internet. 
\ZT{In our publicly available dataset, user privacy information such as nicknames and user IDs has been encrypted to ensure that the original users cannot be re-identified, while still allowing researchers to use the data appropriately.}
%We will handle their sensitive information carefully and ensure the data security.

When our chatbot proactively interacts with patients, it ensures transparency and legitimacy in the interaction. Although the roles we created were not held by actual users of that kind, we ensured no negative effects on these depressive users. We meticulously crafted our profiles to be convincing, and our authenticity was not questioned.
We are dedicated to communicating with depressed users in a professional and responsible manner to understand and improve their conditions. As detailed in the case study, we received numerous responses expressing gratitude and providing emotional support, with no negative feedback received. Thus, our interactions did not cause any adverse effects on depressed users.
Furthermore, testing in real-life settings without disclosing our roles in advance helped prevent bias in their responses. Our goal is to assist these patients in managing their emotions and encourage them to actively seek professional mental health support. 

All response templates and strategies used in this study are documented in the Appendix \ref{apd:icebreaker_ge}.
And our three-round of interactive data will make personal information private and public.
%\KZ{Discuss a bit the effect of ``profile building'' of our bots.
%Does it amount to ``cheating''? Does it have any adverse effects on the user?}

%\KZ{Add these to the appendix so that readers can check and verify if any of the 
%responses are \textbf{toxic}. I'm thinking that maybe we should not release this data to the public?}


