%!TEX program = xelatex
\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{rotating}
\usepackage{color}
\usepackage{epsfig,caption,subcaption, multicol,multirow}
\usepackage{amsmath,algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{url}	
%\usepackage{subfigure}
\graphicspath{{figures/}}
\newcommand{\KZ}[1]{\textcolor{blue}{Kenny: #1}}
\newcommand{\ZY}[1]{\textcolor{red}{J: #1}}
\newcommand{\ZYBEGIN}{\textcolor{red}{\{BEGIN}}
\newcommand{\ZYEND}{\textcolor{red}{END\}}}
\newcommand{\tabref}[1]{Table \ref{#1}}
\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\secref}[1]{Section \ref{#1}}
\newcommand{\eqnref}[1]{Equation (\ref{#1})}
\newcommand{\cut}[1]{}
\newtheorem{example}{Example}
%\usepackage{mathrsfs}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}


\begin{document}

\title{%Commonsense Causal Reasoning by Causal Relation Extraction from the Web
Reasoning Causality between Short Texts 
%\thanks{This work has been supported by NSFC-NRF Joint Research Scheme.}
}

%\author{Zhiyi Luo \and Yuchen Sha \and Kenny Q. Zhu\\
%Shanghai Jiao Tong University\\
%Shanghai, China
%\And
%Seung-won Hwang\\
%POSTECH\\
%Pohang, Korea
%}

\maketitle
\begin{abstract}
% \ZY{Causal reasoning on text is }
Causality reasoning is the process of capturing and understanding
the causal dependencies amongst events and actions.
% using general causality knowledge. 
Such events and actions can be expressed in terms, phrases or 
sentences in natural language text.
Therefore, one possible way of obtaining causal knowledge is by extracting
causal relations between terms or phrases from a large text corpus. 
However, causal relations in text are sparse, ambiguous, and sometimes implicit,
and thus difficult to obtain.
This paper attacks the problem of causality reasoning between short 
texts (phrases and sentences) using a data driven approach.
We propose a framework that automatically harvests a network of
causal-effect terms from a large web corpus.
%We encode causal directions and strengths on the
%network based on lexico-syntactic analysis of the sentences from which
%the terms are extracted.
Backed by this network, we propose a novel and effective metric to properly 
model the causality strength between terms. We show these signals
can be aggregated for causality reasonings between 
short texts, including sentences and phrases. 
In particular, our approach outperforms all previously 
reported results in the standard SEMEVAL COPA task by substantial margins.

\end{abstract}

%%\terms{Framework; Algorithms; Experimentation}

%%\keywords{Commonsense causal reasoning; causal strength metric; causality detection}

\input{intro}
\input{approach}
\input{eval}
\input{related}
\input{conclusion}

%\section*{Acknowledgments}
%% The file named.bst is a bibliography style file for BibTeX 0.99c
%%\bibliographystyle{abbrv}%named
\bibliographystyle{aaai}
\bibliography{causal}

\end{document}
