\documentclass[conference,letterpaper]{IEEEtran}
\usepackage{times,amsmath,amsfonts,amssymb,algorithm}
\usepackage{epsfig,caption,subcaption,multirow}
\usepackage[noend]{algpseudocode}
\usepackage{mathtools}
\usepackage{color,url}
%\usepackage{balance}
\newcommand{\secref}[1]{Section \ref{#1}}
\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\equref}[1]{Equation (\ref{#1})}
\newcommand{\exref}[1]{Example \ref{#1}}
\newcommand{\tabref}[1]{Table \ref{#1}}
\newcounter{copyrightbox}
\newcommand{\KZ}[1]{\textcolor{red}{[Kenny: #1]}}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

\title{SAR: A Sentiment-Aspect-Region Model for User Preference Analysis in
Geo-tagged Reviews}

\author{%
% author names are typeset in 11pt, which is the default size in the author block
{Kaiqi Zhao, Gao Cong, Quan Yuan}%
% add some space between author names and affils
\vspace{1.6mm}\\
\fontsize{10}{10}\selectfont\itshape
% 20080211 CAUSAL PRODUCTIONS
% separate superscript on following line from affiliation using narrow space
School of Computer Engineering\\
Nanyang Technological University, Singapore\\
\fontsize{9}{9}\selectfont\ttfamily\upshape
%
% 20080211 CAUSAL PRODUCTIONS
% in the following email addresses, separate the superscript from the email address
% using a narrow space \,
% the reason is that Acrobat Reader has an option to auto-detect urls and email
% addresses, and make them 'hot'.  Without a narrow space, the superscript is included
% in the email address and corrupts it.
% Also, removed ~ from pre-superscript since it does not seem to serve any purpose
%$^{1}$\,first.author@first-third.edu\\
%$^{3}$\,third.author@first-third.edu%
% add some space between email and affil
\{kzhao002@e., gaocong@, qyuan1@e.\}ntu.edu.sg
\vspace{1.2mm}\\
\fontsize{10}{10}\selectfont\rmfamily\itshape
% 20080211 CAUSAL PRODUCTIONS
% separated superscript on following line from affiliation using narrow space \,
\and
Kenny Q. Zhu
\vspace{1.6mm}\\
\fontsize{10}{10}\selectfont\itshape
Department of Computer Science \& Engineering\\
Shanghai Jiao Tong University, Shanghai, China\\
\fontsize{9}{9}\selectfont\ttfamily\upshape
% 20080211 CAUSAL PRODUCTIONS
% removed ~ from pre-superscript since it does not seem to serve any purpose
%$^{2}$\,second.author@second.com
kzhu@cs.sjtu.edu.cn
}

\begin{document}
%
% --- Author Metadata here ---
%\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

%\title{SAR: A Sentiment-Aspect-Region Model for User Preference Analysis in
%Location-based Services}
%
%\numberofauthors{2}
%\author{
%% 1st. author
%\alignauthor
%Kaiqi Zhao, Gao Cong, Quan Yuan\\
%       \affaddr{School of Computer Engineering}\\
%       \affaddr{Nanyang Technological University}\\
%       \affaddr{Singapore 639798}\\
%       \email{\{kzhao002@e.,gaocong@,qyuan1@e.\}ntu.edu.sg}
%% 2nd. author
%%\alignauthor
%%Gao Cong \\
%%       \affaddr{School of Computer Engineering}\\
%%       \affaddr{Nanyang Technological University}\\
%%       \affaddr{Singapore 639798}\\
%%       \email{gaocong@ntu.edu.sg}
%% 3rd. author
%\alignauthor
%Kenny Q. Zhu \\
%       \affaddr{Department of Computer Science}\\
%       \affaddr{Shanghai Jiao Tong University}\\
%       \affaddr{Shanghai, China}\\
%       \email{kzhu@cs.sjtu.edu.cn}
%}

\maketitle
\begin{abstract}
Many location based services, such as FourSquare,
 Yelp, TripAdvisor, Google Places, etc., allow
 users to compose reviews or tips
on points of interest (POIs), each having a geographical
coordinates. These services have accumulated
a large amount of such
geo-tagged review data,
which allows deep analysis of user preferences in POIs.
This paper studies two types of
user preferences to POIs: topical-region preference
and category aware topical-aspect preference.
We propose a unified probabilistic model to
capture these two preferences simultaneously.
In addition, our model is capable of capturing
the interaction of different factors, including topical aspect,
sentiment, and spatial information. The model can be used in
a number of applications, such as POI recommendation
and user recommendation, among others. In addition, the model
enables us to investigate whether people like
an aspect of a POI or whether people like a
topical aspect of some type of POIs (e.g., bars) in a region,
which offer explanation for recommendations.
Experiments on real world datasets
show that the model achieves significant improvement in POI
recommendation and user recommendation in comparison to
the state-of-the-art methods. We also propose an efficient online
recommendation algorithm based on our model, which saves up
to 90\% computation time.
\end{abstract}

% A category with the (minimum) three required fields
%\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

%\terms{Theory}

%\keywords{ACM proceedings, \LaTeX, text tagging}

\input{intro}
\input{related}
\input{model}
\input{eval}
\input{conclude}
\section*{Acknowledgement}
This work is supported in part by a grant awarded by a Singapore MOE AcRF Tier 2 Grant (ARC30/12), and a grant awarded by Microsoft Research Asia.
Kenny Q. Zhu has been partially supported by NSFC Grants 61033002, 61100050 and 61373031, and Google Faculty Research Award.




\bibliographystyle{abbrv}
\bibliography{../bibs/poi}  % sigproc.bib is the name of the Bibliography in this case
\end{document}
