We consider all the information extracted to be a hupergraph.
Firstly,we assume every value to be a node of  the supergraph,but all values 
are contained in a certain type(For instance, director). we don't need to 
consider the relationship in a type, we just need to consider relationships between 
values of different relationships. We denote the relationship to be an edge connecting 
several nodes.

	But in implementation, we form a binary relationship between every two type, ie , 
(director , actor , weight ). Anything of the two type will be inserted to the relationship 
as long as they appear in some program. And the weight will be accumulated as those two values 
appear more. What's more, every time the weight will be added by different weight, according to 
the reliability of the source program.

	When applied to inferring, we will use the known to infer the unknown. For example, in the program 
we extracted from Web, we know the actors and producer of the program(In fact a film) and wan't to know the 
director. We will search the relationship between actor and director, between producer and director. We find 
the instance of the relationship contain known actors and producers. For every value of director that appear 
in those instances, compute the total weight of those instances including it. The one with the highest weight 
is the most probable. But the probability remains to learn.

	Besides,to accelerate searching, we decide to insert indexes.
	 