\section{Experiment}
We build a demo search engine to test the system. And we also evaluate the accuracy of 
our Action-noun mapping.
\begin{table*}[th]
    \centering
    \caption{ Some results for Action-noun mapping }
    \begin{tabular} {c|c}
        \hline
        Action & Top 10 nouns\\
        \hline
        country invade country & \parbox[t]{12cm}{ war,exhibition,anniversary, lesson, incident, movement, experiment, memorial, research, battle}\\
        \hline
        company buy company & \parbox[t]{12cm} { approval,acquisition,purchase, opening, theater, practice, anniversary, conference, holding, test}\\
        \hline
        person play instrument & \parbox[t]{12cm} {band, concert, music, song, test, orchestra,show,festival, play, prayer}\\
        \hline
        group boycott group & \parbox[t]{12cm} {protest, anniversary, show,theater, trial, story, compaign, work, attack, party}\\
        \hline
        person accept payment & \parbox[t]{12cm} {donation, joint, concert, ceremony, sport, fair, dance, celebration, lunch, dinner}\\
        \hline
    \end{tabular}
\end{table*}
\subsection{Experiment Setup}
We use Lucene index to build our search engine interface. There are 39800 BBC news in our
database. And we have 50 actions for evaluation, and the sie of our noun dictionary is
145 words.
\subsection{Methods}
In order to compare our method with traditional keyword search,
we display the result of three different methods on the same webpage.


In baseline method column, the results are from Action-noun mapping 
generated by our baseline method.Namely by just using Wordnet derivational
 related words to transfer a verb into a noun.
For example ``invade'' will be translated into ``invasion''. 

In our method column, the results are from Action-noun mapping generated by
our retrieval method, where we find the top 3 noun concepts with the highest
TFIDF score for input actions. 
\subsection{Evaluation}
We evaluated both the accuracy of the Action-noun mapping and the end-to-end system.
In Action-noun mapping evaluation. We asked three people to give scores to nouns generated
by our system. 

\begin{table*}[ht]
    \caption{Results for 50 action concepts}
\small
\centering
    \begin{tabular} {l|l|c|c}
    \hline
    & policy & exclude direct change  & include direct change\\
    \hline \hline
   Baseline & Num of actions with correct nouns & 28/50 & 47/50 \\
    \cline{2-4}
    & Num of correct nouns & 49/218 & 95/218 \\
        \hline
        & top $k$ & 5 & 10 \\
    \hline
   Our method & Num of actions with correct nouns & 29/50 & 34/50 \\
    \cline{2-4}
    & Num of correct nouns & 37/250 & 52/500 \\
    \hline

\end{tabular}
\end{table*}



