\def\year{2015}
%File: formatting-instruction.tex
\documentclass[letterpaper]{article}

\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{amsmath,amsfonts,amssymb,amsthm,amsopn}
\usepackage{times}
\usepackage{url}
\usepackage{color}
\usepackage{latexsym}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{diagbox}
\usepackage{array}
\usepackage{multicol}
\usepackage{threeparttable}
\usepackage{epstopdf}

\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\tabref}[1]{Table \ref{#1}}
\newcommand{\eqnref}[1]{Eq. (\ref{#1})}
\newcommand{\defref}[1]{Def. \ref{#1}}

\newcolumntype{I}{!{\vrule width 1pt}}
\newlength\savedwidth
\newcommand\whline{\noalign{\global\savedwidth\arrayrulewidth
                            \global\arrayrulewidth 1pt}%
                   \hline
                   \noalign{\global\arrayrulewidth\savedwidth}}
\newlength{\Oldarrayrulewidth}
\newcommand{\Cline}[2]{%
  \noalign{\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}}%
  \noalign{\global\setlength{\arrayrulewidth}{#1}}\cline{#2}%
  \noalign{\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}}}


\theoremstyle{plain}
\newtheorem{thm}{Theorem}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem*{cor}{Corollary}

\theoremstyle{definition}
\newtheorem{defn}{Definition}
%\newtheorem{defn}{Definition}[section]
\newtheorem{conj}{Conjecture}[section]
\newtheorem{exmp}{Example}[section]

\theoremstyle{remark}
\newtheorem*{rem}{Remark}
\newtheorem*{note}{Note}

\newcommand{\KZ}[1]{\textcolor{blue}{Kenny: #1}}
\newcommand{\KQ}[1]{\textcolor{red}{Kangqi: #1}}
\newcommand{\XS}[1]{\textcolor{blue}{Xusheng: #1}}


\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Insert Your Title Here)
/Author (Put All Your Authors Here, Separated by Commas)}
\setcounter{secnumdepth}{0}


\begin{document}
\title{Paraphrasing Binary Relations from Natural Language to Knowledge Graphs}
%\author{Kangqi Luo, Xusheng Luo \and Kenny Q. Zhu\\
%Shanghai Jiao Tong University\\
%}
\maketitle


\begin{abstract}
% 5 sentences
%1. gap between NL and KB
The task of paraphrasing to translate a natural language relation into structured knowledge.
Due to the incompleteness of a knowledge base (KB), paraphrasing is important for
bridging semantic gaps between NL representations and canonical forms in KB.
%2. presents
We presents a framework to model the semantic representation of a binary relations based on
a small set of relation instances, and to infer a set of relation schemas.
%3. what's the schema look like
Each relation schema is a graph which combines different predicates in KB.
%4. MDL principle
Our framework follows the \textit{minimum description length} principle, which optimizes the
cost of transmitting relation instances and the schemas.
%5. apply to  &  competitive
Comparing with state-of-the-art paraphrasing systems, the experiments show that our system can improve
both schema quality and the F1 score of binary relation instances extracted by schemas over different knowledge bases.

\end{abstract}
\input{intro}

\input{problem}

\input{scoring}

\input{candidate}

\input{search}

%\bibliographystyle{acl}
%\bibliography{qa}

\input{experiment}

\input{related}

\bibliographystyle{aaai}
\bibliography{reference}

\end{document}
