\section{Conclusion}
\label{sec:conclusion}
In this paper, we propose a task to computational infer inter-personal
relationships between two speakers in a dialogue. 
We build a new dataset with dialogues from movie scripts for this task. 
%With reference to humam's inference process, 
We identify and extract multiple indicative features of dialogues from texts. 
Logistic Regression with those features achieved a $78.49\%$ accuracy on 
our test set, which significantly outperforms other baselines,
and is close to the $81.69\%$ human performance. 
Analyzing indicative power of each feature, we find that lexical features, 
namely address terms and frequencies
of selected words that are unevenly distributed across 2 classes(d-BOW), 
play important role in classification. Syntactic structures and 
linguistic features (e.g. entrainment), however, are not as informative,
either used alone or together with lexical features, despite that their 
distribution in the data also showed disparity.

Beyond this specific task, we believe our dataset, 
the identified features and methods can also be applied to 
research on language phenomenon (e.g., entrainment),  dialogue intentions, 
emotions and more specific characteristics of relationships 
revealed by language (e.g., whether the relationship is equal 
or dominated by one side). An automatic relationship classification system 
can help social psychologists prepare large-scale data. Also it can 
be used to construct relationship networks for movies and tv shows, 
which is an important but missing from existing movie/tv-show databases 
such as IMDb, TMDb\footnote{\url{https://www.themoviedb.org/}} and 
OMDb\footnote{\url{http://www.omdbapi.com/}}. 
