% LREC-COLING 2024 Example; 
% LREC Is now using templates similar to the ACL ones. 
\documentclass[10pt, a4paper]{article}
\usepackage{lrec-coling2024} % this is the new style
% \usepackage{fontspec}
% \setmainfont{Arial}

\usepackage{natbib}
\usepackage{multibib}
\makeatletter
\def\@mb@citenamelist{cite,citep,citet,citealp,citealt,citepalias,citetalias}
\makeatother
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{soul}
\usepackage{bm}
\usepackage{bbm}
\usepackage{algorithm,algorithmicx}
\usepackage{amsmath}
\usepackage{verbatim}
\usepackage{booktabs}
\usepackage{amsfonts,amssymb} 
\usepackage[noend]{algpseudocode}


\usepackage{xcolor}
\usepackage{hyperref}
 \definecolor{darkblue}{rgb}{0, 0, 0.5}
  \hypersetup{colorlinks=true, citecolor=darkblue, linkcolor=darkblue, urlcolor=darkblue}

\usepackage{xstring}

\usepackage{color}
\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\eqnref}[1]{Eq. (\ref{#1})}
\newcommand{\tabref}[1]{Table \ref{#1}}
\newcommand{\exref}[1]{Example \ref{#1}}
\newcommand{\KZ}[1]{\textcolor{blue}{Kenny: #1}}


\title{Low-Rank Prune-And-Factorize for Language Model Compression}


\name{Siyu Ren, Kenny Q. Zhu\textsuperscript{*}\thanks{*The correspondence author, and was partially supported by Meituan-SJTU Joint Research Scheme and NSF Award No. 2349713.}} 

\address{Shanghai Jiao Tong University, University of Texas at Arlington \\
         Shanghai China, USA \\
         roy0702@sjtu.edu.cn, kenny.zhu@uta.edu \\
         }


\abstract{
The components underpinning PLMs—large weight matrices—were shown to bear considerable redundancy. Matrix factorization, a well-established technique from matrix theory, has been utilized to reduce the number of parameters
in PLM. However, it fails to retain satisfactory performance under moderate to high compression rates. In this paper, we identify the full-rankness of fine-tuned PLM as the fundamental bottleneck for the failure of matrix factorization and explore the use of network pruning to extract low-rank sparsity pattern desirable to matrix factorization. We find such a low-rank sparsity pattern exclusively exists in models generated by first-order pruning, which motivates us to unite the two approaches and achieve more effective model compression. We further propose two techniques: sparsity-aware SVD and mixed-rank fine-tuning, which improve the initialization and training of the compression procedure, respectively. Experiments on GLUE and question-answering tasks show that the proposed method has a superior compression-performance trade-off compared to existing approaches.
}


\begin{document}
\maketitleabstract
	\input{intro}
	\input{method}
	\input{experiment}
	\input{conclusion}
\nocite{*}
\section{Bibliographical References}\label{sec:reference}

\bibliographystyle{lrec_natbib}
\bibliography{lrec-coling2024-example}

\section{Language Resource References}
\label{lr:ref}

\bibliographystylelanguageresource{lrec_natbib}
\bibliographylanguageresource{languageresource}


\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
