I would like to thank all the people who made this thesis possible and help me through my undergraduate research.
I wish to express my sincere thanks to my advisor, Prof. Kenny Q.Zhu. I had a great time working with him at ADAPT lab and I learned a lot about every small aspect of research.
I also want to thank Prof. Yong Yu, for offering me the platform of ACM class, the opportunity of doing undergraduate research at a very early stage and my internship at MSRA. But more importantly, he guided me through my toughest times during my undergraduate and help shaped who I am now, which I will always be grateful.
Lots of my inspirations came from my classmates, Siqi Chen, Hao Tan, Chao Liao, Yao Li, Yiqing Hua, Zhuoyue Zhao and many others. I'd like to thank them for listening to my crazy ideas and sharing their insights. 
I'm also grateful to my friends in the soccer team, Zhenyu Wang, Yunbo Gao and Fan Xu, for their support and the great time we shared together.
I'm grateful to my parents from the bottom of my heart. They supported all my decisions, including going abroad for a PhD, both spiritually and financially. They are always there for me and I can never repay enough.
I'd like to thank my labmates at ADAPT for their great talks at the seminars and the discussions we have. Those talks greatly broadened my horizon in research, and they were a lot of fun.
I own my thanks to faculties of Zhiyuan College, especially Qin Luo, Xu Wang, who helped me a lot in the thesis writing and the graduation process. Without their help, everything couldn't have been carried out smoothly and we would be distracted by many things.
My internship at MSRA was a great experience. I need to thank my mentor Dr. Mu Li, for teaching me a lot of stuff about research; researcher Dr. Shujie Liu, Dr. Nan Yang and Dr. Dongdong Zhang, who I worked very closely with, for their insights and lessons; Zhirui Zhang and Shuangzhi Wu for the discussions we shared and inspirations for research topics.
I owe my knowledge to all my teachers during college, among which Prof. Enshao Shen wield the most influence on how I think about math and theory. I especially need to thank Prof. John Hopcroft and Prof. Lorenzo Alvisi. They made the most influence on my thoughts about PhD and general carear decision. Talking to them was like exploring a whole new world. I also need to thank the professors and students I talked at Cornell, those talks matter a lot to me.
Finally I want to thank my closest friend, Xinrui Li. Wish him good luck with his study in France.
