\section{Related Work}
\label{sec:related}
%\kz{premable?}
Our work applies the latest Deep Learning technology to solve a new type of 3D BPP. In this section, we will go through the main research result of 3D BPP and machine learning method in combinatorial optimization.

\subsection{3D bin packing problem}

Bin packing problem is a classical and popular optimization problem. Since 1970s, it has attracted great interest of many researchers and some valuable achievements have been obtained. As a strongly NP-hard problem, a lot of research focuses on approximation and heuristic algorithms for 3D BPP. \cite{scheithauer1991three} proposes the first approximation algorithm for 3D BPP and investigates the performance bound of the algorithm. And many effective heuristic algorithms, such as genetic algorithm \cite{gonccalves2013biased}, guided local search \cite{faroe2003guided}, extreme point-based heuristics \cite{crainic2008extreme}, hybrid genetic algorithm \cite{kang2012hybrid}, have been proposed. There are also some research about exact solution method for 3D BPP. \cite{chen1995analytical} considers a problem of loading containers with cartons of non-uniform size, which is a generalization of 3D BPP where bins may have different sizes, and a mixed integer programming model is developed to obtain optimal solutions. Some variants of BPP from real world are also studied, such as variable size bin packing problem \cite{kang2003algorithms}, bin packing problem with conflicts \cite{khanafer2010new,gendreau2004heuristics} and bin packing problem with fragile objects \cite{clautiaux2014lower}. 

Another class of geometrical packing problem, named strip packing problem (SPP), is also worth mentioning here, because it is very similar to the problem we studied. In SPP, a given set of cuboid-shaped items should be packed into a given strip orthogonally by minimizing the height of packing. The length and width of the strip is fixed and limited, and the height is infinite (for 2D SPP, the width of strip is fixed and the length is infinite). Different types of algorithms have been proposed to solve the problem, such as exact algorithms in \cite{kenmochi2009exact}, approximation algorithm in \cite{steinberg1997strip}, heuristic algorithm in \cite{bortfeldt2007heuristic} and meta-heuristic algorithms in \cite{bortfeldt2006genetic} and \cite{hopper2001review}.

Our work focus on a new type of 3D BPP and its objective is to minimize the surface area of the bin that could place all the items. As shown in the Appendix \ref{np-hard}, this is a NP-hard problem. Previous methods of solving typical 3D BPP could not achieve persuasive performance (BRKGA) and we propose a new well-designed heuristic algorithm(NBPH). The heuristic algorithm can be seen as a series of decisions. We believe that if we use DNN to parameterize these decision processes, we can obtain a more powerful algorithm, similar to the performance boosted in \cite{Hu2017Solving}

%\kz{You need to say the differences between all the previous study on 3D bin packing and this paper. Why this work is worthwhile. If this is just another method on an
%old problem, our burden is to show that this method indeed outperforms the previous ones. This subsection can be expanded}

\subsection{Machine Learning in combinatorial optimization}
%\kz{This subsection can be reduced.}
Even though machine learning and combinatorial optimization have been studied for decades respectively, there are few investigations about application of machine learning method in combinatorial optimization problems. One research direction is designing hyper-heuristics based on reinforcement learning ideas. An overview of hyper-heuristics is presented in \cite{burke2013hyper}, in which some hyper-heuristics based on learning mechanism are discussed. %In \cite{nareyek2003choosing}, the heuristics selection probability is updated based on non-stationary RL. 
%In addition, various score updating methods have been proposed in the area of hyper-heuristics, such as binary exponential back-off \cite{remde2009binary} and choice function \cite{cowling2000hyperheuristic}.

%Some hyper-heuristics in ~\cite{sutton1998reinforcement} use RL ideas to guide the choice of the heuristics during the search. In ~\cite{nareyek2003choosing}, the heuristics selection probability is updated based on non-stationary RL. To deal with the problem that evolutionary algorithm often neither offers worst-case bounds nor any guarantee of optimality when used to solve individual problems, ~\cite{ross2002hyper} tried to learn a solution process, in which one of various simple non-evolutionary heuristics is chosen to apply to each state of a problem, gradually transforming the problem from its initial state to a solved state. %
%Attention networks are now a standard part of the deep learning toolkit, contributing to impressive results in neural machine translation (Bahdanau et al., 2015; Luong et al., 2015), image captioning (Xu et al., 2015), speech recognition (Chorowski et al., 2015; Chan et al., 2015), question answering (Hermann et al., 2015; Sukhbaatar et al., 2015), abstractive summarization(\cite{paulus2017deep}),and algorithm-learning (Graves et al., 2014; Vinyals et al., 2015), among many other applications (see Cho et al. (2015) for a comprehensive review).%

Recent advances in sequence-to-sequence model \cite{sutskever2014sequence} have motivated the research about neural combinatorial optimization. Attention mechanism, which is used to augment neural networks, contributes a lot in areas such as machine translation (\cite{bahdanau2014neural}) and abstractive summarization \cite{paulus2017deep}. In \cite{paulus2017deep}, intra attention mechanism is proposed to address the repeating phrase problem in abstractive summarization. In \cite{vinyals2015pointer}, a neural network with a specific attention mechanism named Pointer Net was proposed and a supervised learning method is applied to solve the TSP. \cite{bello2016neural} develops a neural combinatorial optimization framework with RL, and some classical problems, such as TSP and Knapsack Problem are solved in this framework. %Besides, \cite{Hu2017Solving} proposes a DRL framework to solve new 3D Bin packing Problem based on effectiveness and generality of the methodology proposed in \cite{bello2016neural}. However,our research is an extension of the previous method in \cite{Hu2017Solving}.


