\documentclass{sig-alternate}%[conference][letterpaper]
\usepackage{times,amsmath}
\usepackage{epsfig,algorithm,caption,subcaption,multirow}
\usepackage[noend]{algpseudocode}
\usepackage[normalem]{ulem}
\usepackage{color,url}
\usepackage{balance}
\DeclareCaptionType{copyrightbox}

\newcommand{\secref}[1]{Section \ref{#1}}
\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\equref}[1]{Equation (\ref{#1})}
\newcommand{\exref}[1]{Example \ref{#1}}

\newcommand{\KZ}[1]{\textcolor{green}{[KZ: #1]}}
\newcommand{\HAIXUN}[1]{\textcolor{red}{[HAIXUN: #1]}}
\newcommand{\myurl}[1]{\textsf{{\uline{#1}}}}

\newcommand{\cut}[1]{}
\newcommand{\myskip}{\vspace*{1ex}}
\newcommand{\shrink}{\vspace*{-1ex}}

%\theoremstyle{definition}
%\newenvironment{example}[1][Ex.]{\begin{trivlist}
%\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newtheorem{example}{Example}

\newcommand{\lbb}{{\color{black} \textbf{[}}}
\newcommand{\rbb}{{\color{black} \textbf{]}}}
%
%
\newfont{\mycrnotice}{ptmr8t at 7pt}
\newfont{\myconfname}{ptmri8t at 7pt}
\let\crnotice\mycrnotice
\let\confname\myconfname
\conferenceinfo{CIKM'13,}{Oct. 27--Nov. 1, 2013, San Francisco, CA, USA.}
\copyrightetc{Copyright 2013 ACM \the\acmcopyr}
\crdata{978-1-4503-2263-8/13/10\ ...\$15.00.\\
http://dx.doi.org/10.1145/2505515.2505521}
\clubpenalty=10000
\widowpenalty = 10000

\begin{document}
%\conferenceinfo{EDBT'13,} {Mar 18-22, 2013, Genoa, Italy.}
%\CopyrightYear{2013}
%\crdata{978-1-4503-1462-6 /12/08}
%\clubpenalty=10000
%\widowpenalty = 10000
\title{Wikification via Link Co-occurrence}

\numberofauthors{3}
\author{%
\alignauthor
Zhiyuan Cai \hspace*{3mm} Kaiqi Zhao\\
	\affaddr{Shanghai Jiao Tong University}\\
	\affaddr{Shanghai, China}\\
    \affaddr{\{luckyvega,kaiqi\_zhao\}@sjtu.edu.cn}
    %\email{\small \{luckyvega,kaiqi\_zhao\}@sjtu.edu.cn}
	%\email{luckyvega,kaiqi\_zhao@sjtu.edu.cn}
    %\affaddr{\small \{luckyvega,kaiqi\_zhao\}@sjtu.edu.cn}
    %\affaddr{\{luckyvega,kaiqi\_zhao\}@sjtu.edu.cn}
\alignauthor
Kenny Q. Zhu\\
	\affaddr{Shanghai Jiao Tong University}\\
	\affaddr{Shanghai, China}\\
    \affaddr{kzhu@cs.sjtu.edu.cn}
	%\affaddr{\small kzhu@cs.sjtu.edu.cn}
\alignauthor
Haixun Wang\\
	\affaddr{Google Research}\\
	\affaddr{Mountainview, CA, USA}\\
    \affaddr{haixun@google.com}
	%\affaddr{\small haixun@google.com}
}
\maketitle

\begin{abstract}
Wikification, which stands for the process of linking terms in a
plain text document to Wikipedia articles which represent the correct
meanings of the terms, can be thought
of as a generalized Word Sense Disambiguation problem.
It disambiguates multi-word expressions (MWEs) in addition to single words.
Existing Wikification techniques either models the context of a given
term as well as the Wikipedia article as bags of words, or compute
global constraints among Wikipedia concepts by the link graph or
link distributions. The first method doesn't achieve good results
because the MWEs can have very different meanings than its constituent
words which themselves are ambiguous. The second method doesn't produce
high accuracy because the link structure or link distribution is often
biased or incomplete by themselves due to the fact that Wikipedia pages
are often sparsely linked.
In this paper, we present a simple but powerful framework
of sense disambiguation
using co-occurrences of Wikipedia links in the Wikipedia
corpus. We propose an iterative method to enrich the sparsely-linked
articles by adding more links and then use the resulting
link co-occurrence matrix to disambiguate an input document by a sliding
window algorithm.  Our prototype system achieves 89.97\% precision
and 76.43\% recall on average for three benchmark data and
compares favorably against four state-of-the-art wikification techniques.
\footnote{Kenny Q. Zhu (corresponding author) is partially
supported by NSFC grants 61100050 and 61373031.}
\end{abstract}

\category{I.2.7}{ARTIFICIAL INTELLIGENCE}{Natural Language Processing}

% NOTE keywords are not used for conference papers so do not populate them
\begin{keywords}
Wikification; phrase sense disambiguation; link co-occurrence; iterative
algorithm
\end{keywords}
\setlength{\floatsep}{2.2mm plus 1mm minus 1mm}
\setlength{\textfloatsep}{2.2mm plus 1mm minus 1mm}
\setlength{\intextsep}{2.2mm plus 1mm minus 1mm}
\input{intro}
\input{overview}
\input{parser}
\input{algo}
\input{implement}
\input{eval}
\input{related}
\input{conclude}

\bibliographystyle{abbrv}
\bibliography{../bibs/wiki}
\end{document}
