%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\usepackage{color}
\newcommand{\ZY}[1]{\textcolor{blue}{Zhiyi: #1}}
\newcommand{\KZ}[1]{\textcolor{red}{Kenny: #1}}

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{Dr. Jim Jansen \\
Editor-in-Chief  \\
Information Processing and Management} 

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\begin{center}
\large\bf Zhiyi Luo, Shanshan Huang, Kenny Q. Zhu \\ % Your name
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
Department of Computer Science and Engineering \\ Shanghai Jiao Tong University \\ 800 Dongchuan Road, Shanghai, China 200240 \\
jessherlock@sjtu.edu.cn
 % Your address and phone number
\end{center} 
\vfill

\signature{Zhiyi Luo} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Dear Dr. Jim Jansen,} 

I am pleased to submit an original research article entitled 
"Knowledge empowered prominent aspect extraction from product reviews" by Zhiyi Luo, Shanshan Huang and Kenny Q. Zhu for consideration for publication in \textit{Information Processing and Management}. This manuscript builds a knowledge empowered system (ExtRA) for extracting the prominent aspects from product reviews, which benefits the analysis and summarization of customer reviews about cross-domain products or services. 

 In this manuscript, we show that the proposed system ExtRA benefits  both qualitative and quantitative aspect-based review summarization. 
 ExtRA can generate reasonable aspect clusters and produce
 the  aspect terms that are both important and non-overlapping
 in semantics. 
 Extensive experiments show that ExtRA outperforms
 multiple strong baselines by a substantial margin.
 
 We believe that this manuscript is appropriate for publication by
 \textit{Information Processing and Management}
because it belongs to the topic of text information extraction and 
text mining. 
In addition, our manuscript propose the prominent
aspect extraction problem as well as the evaluation dataset for
future work in this research area.

This manuscript has not been published and is not under
consideration for publication elsewhere. 
If you feel that the manuscript is appropriate for your journal, 
we suggest the following reviewers: 
\begin{enumerate}
	\item[-] Wenya Wang (wa0001ya@e.ntu.edu.sg)
	\item[-] Haixun Wang (haixun@gmail.com)
	\item[-] Wentao Wu (Wentao.Wu@microsoft.com)
	\item[-] Gao Cong (gaocong@ntu.edu.sg)
	\item[-] Eric Lo (ericlo@cse.cuhk.edu.hk)
	\item[-] Seung-won Hwang (seungwonh@yonsei.ac.kr)
	\item[-] H. V. Jagadish (jag@eecs.umich.edu)
\end{enumerate}

Thank you for your consideration!

\closing{Sincerely yours,}


%\encl{Curriculum vitae, employment form} % List your enclosed documents here, comment this out to get rid of the "encl:"

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}