\def\year{2018}\relax
%File: formatting-instruction.tex
\documentclass[letterpaper]{article} %DO NOT CHANGE THIS
\usepackage{aaai18}  %Required
\usepackage{times}  %Required
\usepackage{helvet}  %Required
\usepackage{courier}  %Required
\usepackage{url}  %Required
\usepackage{graphicx}  %Required
\frenchspacing  %Required
\setlength{\pdfpagewidth}{8.5in}  %Required
\setlength{\pdfpageheight}{11in}  %Required

\usepackage[cmex10]{amsmath}
\usepackage{multirow}
\usepackage{paralist}
\usepackage{diagbox}
\usepackage{framed}
\usepackage{color}
\usepackage{tikz}
\usepackage{listings}
\usepackage{threeparttable}

%code environment
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=Java,
  aboveskip=1.0mm,
  belowskip=1.0mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\scriptsize\ttfamily},
  numbers=none,
  numberstyle=\scriptsize\color{gray},
  keywordstyle=\scriptsize\color{blue},
  commentstyle=\scriptsize\color{dkgreen},
  stringstyle=\scriptsize\color{mauve},
  breaklines=true,
  breakatwhitespace=true
  tabsize=2
}

\newcommand{\red}[1]{\colorbox{red}{#1}}
\newcommand{\KZ}[1]{\textcolor{blue}{Kenny: #1}}

%PDF Info Is Required:
  \pdfinfo{
/Title (Automatic Generation of Descriptive Comments for Code Blocks)
%/Author (AAAI Press Staff)
}
\setcounter{secnumdepth}{2}
 \begin{document}
% The file aaai.sty is the style file for AAAI Press
% proceedings, working notes, and technical reports.
%
\title{Automatic Generation of Text Descriptive Comments for Code Blocks}
\author{
		Yuding Liang and
		Kenny Q. Zhu$^*$
		\\[0.5ex]
		\url{liangyuding@sjtu.edu.cn, kzhu@cs.sjtu.edu.cn}\\[0.5ex]
		Department of Computer Science and Engineering\\[0.5ex]
		Shanghai Jiao Tong University\\[0.5ex]
		800 Dongchuan Road, Shanghai, China 200240
}


\maketitle
\begin{abstract}
We propose a framework to automatically generate descriptive
comments for source code blocks. While this problem has been studied by many researchers previously, their methods are mostly based on
fixed template and achieves poor results.
Our framework does not rely on any template, but makes use
of a new recursive neural network called Code-RNN to extract features
from the source code and embed them into one vector. When this vector
representation is input to a new recurrent neural network (Code-GRU),
the overall framework generates text descriptions of the code with
accuracy (Rouge-2 value) significantly higher than other learning-based
approaches such as sequence-to-sequence model. The Code-RNN
model can also be used in other scenario where the representation
of code is required.~\footnote{Kenny Q. Zhu is the contact author.}
\end{abstract}

\input{intro.tex}
\input{model.tex}
\input{eval.tex}
\input{related.tex}
\input{conclusion.tex}
\section*{Acknowledgement}
This work was supported by Oracle-SJTU Joint Research Scheme, NSFC Grant No. 91646205£¬71421002 and 61373031, and SJTU funding project 16JCCS08. Hongfei Hu
contributed to the identifier semantics part of the work.
\bibliographystyle{aaai}
\bibliography{aaai}

\end{document}
