\section{Related Work}

%\subsection{Source Code}

Mining of source code repositories becomes increasingly popular in
recent years. Existing work in source code mining include
code search, clone detection, software evolution,
models of software development processes, bug localization,
software bug prediction, code summarization and so on.
Our work can be categorized as code summarization and comment generation.

%\subsubsection{Code Summary}
Sridhara et al.~\cite{sridhara2010towards} proposed an automatic
comment generator that identifies the content for the summary and
generates natural language text that summarizes the method¡¯s overall
actions based on some templates.
Moreno et al.~\cite{moreno2013automatic} also proposed a
template based method but it is used on summarizing Java classes.
McBurney and McMillan~\cite{mcburney2014automatic}  presented a novel approach
for automatically generating summaries of Java methods that summarize
the context surrounding a method, rather than details from the
internals of the method.
These summarization techniques \cite{murphy1996lightweight,sridhara2011generating,moreno2013automatic,haiduc2010use} work by selecting a
subset of the statements and keywords from the code, and
then including information from those statements and keywords in the
summary. To improve them, Rodeghero et al.~\cite{rodeghero2014improving}
presented an eye-tracking study of programmers
during source code summarization, a tool for selecting keywords
based on the findings of the eye-tracking study.

These models are invariably based on templates and careful selection
of fragments of the input source code. In contrast, our model is
based on learning and neural network. There are also some models
that apply learning methods to mine source code.

Movshovitz-Attias and Cohen~\cite{movshovitz2013natural}
predicted comments using topic models and n-grams.
Like source code summarization,
Allamanis et al.~\cite{allamanis2015suggesting} proposed a
continuous embedding model to suggest accurate method and class names.


%\subsubsection{Other Area of Source code}

Iyer et al.~\cite{iyer2016summarizing} proposed a new model called CODE-NN
that uses Long Short Term Memory (LSTM) networks with attention
to produce sentences that can describe C\# code snippets and SQL queries.
Iyer et al.'s work has strong performance on two tasks,
code summarization and code retrieval.
This work is very similar to our work,
in that we both use the Recurrent NN to generate sentences for source code.
What differs is that we propose a new type of Recurrent NN.
Adrian et al.~\cite{kuhn2007semantic} utilized the information of
identifier names and comments to mine topic of source code repositories.
Punyamurthula~\cite{punyamurthula2015dynamic} used call graphs to
extract the metadata and dependency information from the
source code and used this information to analyze the source code
and get its topics.

%In code search, most search engines solve the problem by keyword extraction
%and signature matching.

In other related domains of source code mining,
code search is a popular research direction.
Most search engines solve the problem by keyword extraction and
signature matching.  Maarek et al.~\cite{maarek1991information} used
keywords extracted from man pages written in natural language and
their work is an early example of approaches based on keywords.
Rollins and Wing~\cite{rollins1991specifications} proposed an
approach to find code with the signatures present in code.
Mitchell~\cite{mitchell2008hoogle} combined signature matching with
keyword matching. Then Garcia et al.~\cite{garcia2016semantic} focused
on querying for semantic characteristics of code and
proposed a new approach which combines semantic characteristics and
keyword matching.

%In other related domains of source code mining,
Cai~\cite{cai2016code} proposed a method
for code parallelization through sequential code search.
That method can also be used for clone detection.
Williams and Hollingsworth~\cite{williams2005automatic}
described a method to use the source code change history of a
software project to drive and help to refine the search for bugs.
Adhiselvam et al.~\cite{adhiselvam2015enhanced} used MRTBA algorithm
to localize bug to help programmers debug. The method proposed in this paper
can also benefit natural language search for code fragments.

%\subsection{RNN}

%In our paper, we totally use two kinds of RNN, one is Recursive Neural Network and the other one is Recurrent Neural Network. These two neural networks are all widely used now.
%
%%\subsubsection{Recursive Neural Network}
%
%R. Socher did many works
% on Recursive Neural Network and proposed many kinds of Recursive Neural Network, for example, basic RNN~\cite{socher2011parsing}, Recursive Autoencoders (RAE)\cite{socher2011semi}, Unfolding Recursive Autoencoder~\cite{socher2011dynamic}, Recursive Matrix-Vector Model~\cite{socher2012semantic} and Recursive Neural Tensor Network~\cite{socher2013recursive}.
% O. Irsoy and C. Cardie~\cite{irsoy2014deep} introduced an architecture called deep RNN that constructed by stacking multiple recursive layers.
%
% Recurrent Neural Network is much more popular than Recursive Neural Network, there are many kinds of Recurrent Neural Network such as GRU~\cite{cho2014learning}, LSTM~\cite{hochreiter1997long} and Hierarchical RNN~\cite{schmidhuber1992learning}~\cite{paine2005hierarchical}. It is widely used in Summarization~\cite{nallapati2016abstractive}, QA~\cite{malinowski2015ask}, Action Recognition~\cite{du2015hierarchical}~\cite{veeriah2015differential} and so on.


%\subsubsection{Recurrent Neural Network}

