\def\year{2018}\relax
%File: formatting-instruction.tex
\documentclass[letterpaper]{article} %DO NOT CHANGE THIS
\usepackage{aaai18}  %Required
\usepackage{times}  %Required
\usepackage{helvet}  %Required
\usepackage{courier}  %Required
\usepackage{url}  %Required
\usepackage{graphicx}  %Required
\frenchspacing  %Required
\setlength{\pdfpagewidth}{8.5in}  %Required
\setlength{\pdfpageheight}{11in}  %Required
%PDF Info Is Required:
  \pdfinfo{
/Title (2018 Formatting Instructions for Authors Using LaTeX)
/Author (AAAI Press Staff)}
%\setcounter{secnumdepth}{2}  

%\usepackage{etoolbox}
%\newcommand{\zerodisplayskips}{%
%	\setlength{\abovedisplayskip}{0pt}%
%	\setlength{\belowdisplayskip}{0pt}%
%	\setlength{\abovedisplayshortskip}{0pt}%
%	\setlength{\belowdisplayshortskip}{0pt}}
%\appto{\normalsize}{\zerodisplayskips}
%\appto{\small}{\zerodisplayskips}
%\appto{\footnotesize}{\zerodisplayskips}
%\usepackage{enumitem}
%\setlist{nosep}

\usepackage{CJKutf8}
\usepackage{amsmath,amsfonts,amsthm}
\usepackage{color}
\usepackage{array}
\usepackage{epsfig}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{array}
\usepackage{ragged2e}
\usepackage{pbox}

\usepackage[ruled,vlined,boxed,linesnumbered]{algorithm2e}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\usepackage{float}
\restylefloat{table}
\newcolumntype{P}[1]{>{\RaggedRight\hspace{0pt}}p{#1}}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}


\newcommand{\secref}[1]{Section \ref{#1}}
\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\eqnref}[1]{Eq. (\ref{#1})}
\newcommand{\tabref}[1]{Table \ref{#1}}
\newcommand{\exref}[1]{Example \ref{#1}}
\newcommand{\algref}[1]{Algorithm \ref{#1}}
\newcommand{\socvec}{SocVec}
\newcommand{\argmin}{\operatornamewithlimits{argmin}}
\newcommand{\argmax}{\operatornamewithlimits{argmax}}
\newtheorem{example}{Example}
\newtheorem{lemma}{Lemma}
\newtheorem{definition}{Definition}
\newcommand{\cut}[1]{}

\newcommand{\li}{\uline{\hspace{0.5em}}}
\newcommand{\BL}[1]{\textcolor{blue}{Bill: #1}}
\newcommand{\HY}[1]{\textcolor{red}{Hanyuan: #1}}
\newcommand{\KZ}[1]{\textcolor{green}{Kenny: #1}}
\newcommand{\SH}[1]{\textcolor{green}{Seung: #1}}
\newcommand{\FX}[1]{\textcolor{blue}{Frank: #1}}

\begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Supplementary Material for 
	``Understanding Slang Terms across Languages'':\\
Computing Cross-cultural Similarities and Differences}
\author{
	Bill Y. Lin\thanks{Phone: +86 13120889217; URL: https://yuchenlin.github.io},
	Frank F. Xu and
	Kenny Q. Zhu
	\\[0.5ex]
	\url{{yuchenlin, frankxu}@sjtu.edu.cn, kzhu@cs.sjtu.edu.cn}\\[0.5ex]
	Department of Computer Science and Engineering\\[0.5ex]
	Shanghai Jiao Tong University\\[0.5ex]
	800 Dongchuan Road, Shanghai, China 200240
}
\maketitle
\begin{abstract}

\textbf{In this supplementary material, we generalize our work in the student abstract ``Understanding Slang Terms across Languages'' in a broader context of capturing cross-cultural differences. 
We propose one more task as the application of our proposed \textit{\socvec}.	We also present our models with more detail as well as more experiments.} 

Capturing cross-cultural differences between terms is an important challenge in bilingual text understanding
and machine translation. 
This paper presents a novel framework for obtaining bilingual
word representations from social media by leveraging ``social vocabularies''. 
Such representations can act as a building block for cross-lingual and cross-cultural studies in computational social science.
We evaluate our framework on two tasks: 
1) detection of cross-cultural differences of named entities in social media
and 
2) to explain slang terms in one language with terms in another language. 
We also release two new datasets for these tasks.
Experimental results show that simple methods based on our proposed word representations outperform a number of strong baseline methods by 
substantial margins.
\end{abstract}
\begin{CJK}{UTF8}{gkai}
	\input{intro}
	\input{SocVec}
	\input{eval}
	\input{related}
	\input{conclude} 
	\bibliographystyle{aaai}
	\bibliography{aaai}
	
\end{CJK}

\end{document}
