\begin{chnabstract}[互联网信息提取, ``top-$k$''列表]
列表信息是互联网上一种很重要的结构化数据。
本论文主要关注于一种特殊的列表信息，我们称之为``top-$k$''网页，
这种网页主要关于一个$k$项的排行榜列表。
这样的网页形如``世界上最高的10个人''和``2012年十大必看电影''等等。
与一般的网页表格数据相比，``top-$k$''网页包含更有价值的信息，并且更容易进行分析理解。
因此抓取这样的列表有助于充实已有的知识库或者作为一个常识搜索引擎的预处理步骤。
我们的系统能够有效的抽取互联网上的``top-$k$''列表。
基本上，该系统包含以下几个部分：
1，基于CRF模型的网页标题识别模块；2，基于HTML标签路径聚合算法的``top-$k$''列表抽取模块；3，基于Probase的列表内容分析理解模块。
为了评估系统性能，我们将此系统部署在大型分布式计算系统中，处理了多达1.6个亿的网页，
从中我们提取了129000个``top-$k$''列表，其准确率高达 90.4\%。

\end{chnabstract}

\begin{enabstract}{Lists extraction, HTML pages}
List data is an important source of structured data on the web.
This paper is concerned with ``top-$k$ list'' pages, which are
web pages that describe a list of $k$ instances of a
particular topic or concept. Examples include ``the
10 tallest persons in the world'' and ``the 50 hits of 2010 you
don't want to miss''.
Compared to normal web list data,
``top-k list'' contains richer information and are easier to understand.
Therefore the extraction of such lists can help
enrich existing knowledge bases about general concepts, or
act as a preprocessing step to produce facts for a fact answering engine.
We present an efficient system
that extracts the target lists from web pages with high accuracy.
Generally the system contains the following components:
1) title recognition to identify a ``top-k'' page by its title;
2) list extraction to extract the target list in the ``top-k'' page;
3) content processing and understanding.
To evaluate the performance of the system,
we have used the system to process up to 160 million, or
1/10 of a high-frequency web snapshot from Bing, and obtained
over 129,000 lists with 90.4\% precision.
\end{enabstract}

%% A category with the (minimum) three required fields
%\category{H.4}{Information Systems Applications}{Miscellaneous}
%%A category including the fourth, optional field follows...
%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
%
%\terms{Algorithm, Information extraction}

