\chapter*{Acknowledgement}
\phantomsection
\addcontentsline{toc}{chapter}{Acknowledgement}

\label{sec:ack}

My deepest gratitude goes first and foremost to Professor Kenny Q. Zhu, my supervisor, for his constant encouragement and guidance. 
He has walked me through all the stages of the project. 
Since the first time I entered his laboratory as a summer intern, we have collaborated on this project for a year.
During this year, I realize that Kenny may be the best researcher and professor in the world. His academic expertise, international vision and especially enthusiasm on research keep encouraging me to work hard and perked me up when I had difficulties on the project and wanted to give up.
Without his consistent and illuminating instruction, I would not enter this field and this project could not have reached its present form.

Second, I would like to express my heartfelt gratitude to Professor Haixun Wang from MSRA, he is the collaborator and co-author of our demo paper. 
His strong insight and contribution about the overall framework benefits our project very much.
He is always the first visitor of our demo website after every update, and comes up with many instructive comments.

Third, I want to show my thanks to Hongsong Li, who is also from MSRA. He helps us to deploy the program onto the Cosmos and complete experiments of massive web pages, which is a significant progress to our project. 

Fifth, I am very grateful to Zheng Wang, a lab member of Advanced Data and Programming Technologies (ADAPT). He is also the predecessor and pioneer of our project. He built a basic framework, a prototype of the demo website as well as a lot of tools, which make me much easier to continue his work.
There is an old Chinese saying that ``One generation plants the trees in whose shade another generation rests.''. He really planted a big tree.

Fourth, I would like to thank KDD2012, which is the premier international forum for data mining researchers and practitioners. She just accepted my first paper in life.

Also I would like to thank other ADAPTers, including Zhiyuan Cai, Xinhui Xu, Kaiqi Zhao, Alex Wang, Jack Sun, Tianwan Zhao, Zexiong Ma and so on. And I would like to thank my friends, including Chen Wang, Chong Fu, Yimao Wang, Lin Li, Zetan Cao, Yujiao Cai, Mengjie Yu, Siyun Li, Yu Du, Wenbing Yu, Youqi Wu, Yang Geng, Zhenzhong Gu, Peng Chen, Zhen Jiang and so on. They give me a lot of help and joy during the last year.

Last my thanks would go to my beloved parents, my father Mr. Yiman Zhang and my mother Mrs. Jin Cui, for their loving considerations and great confidence in me all through these years.

In addition, I will like to thank all the readers of this thesis. And I will give my special regards to you who can infer my favourite NBA player from this thesis: you really read it very carefully! 