\section{Conclusion}

In this paper, we investigated the spatial features in 
assisting the classification of POI. Existing works are mainly 
based on user behaviors which come from both social networks 
and smart phone data. In our work, we explored the geographic coordinates, 
and introduce several spatial features including the neighborhood POIs 
category distribution, nearest POIs category distribution, 
distance to different kinds of POIs and check-in records 
comparison to other POIs in the same region. We analyzed 
them separately on the ability of improving 
classification results on different categories.

In order to prove the effectiveness of spatial features, 
we test their performance on four datasets from Foursquare. 
We choose two cities, New York and Singapore, with different 
scales to test on features. We add spatial features on NAME feature 
we extracted from POI's name and BASE feature including user check-in 
analysis features introduced by Ye et al.'s work. As for the 
feature combination selection and parameter determination, 
we first trained a binary classifier on every possible combination 
for each category, and chose the best combination on tuning set 
for each category. Then we apply the feature combination selected 
to the test set. Given classifiers for each category, we combined 
the results from all the binary classifiers, and produced binary 
multi-label prediction output as well as probability output. 
The results of our experiments on spatial features show significant 
improvements on both individual category and overall multi-label classification. 
We conducted experiments both on the first level and second level categories. 
Spatial features show solid improvements on both 
while the BASE features do not work as effective in 
second level categories as in first level categories.

In summary, POI classification is a practical problem in Location-based Social Network, 
and spatial features help in the classification and work steadily in both general 
and specific categories, for both large and small datasets.
