% This must be in the first 5 lines to tell arXiv to use pdfLaTeX, which is strongly recommended.
\pdfoutput=1
% In particular, the hyperref package requires pdfLaTeX in order to break URLs across lines.
\documentclass[11pt]{article}

% Remove the "review" option to generate the final version.
%\usepackage[review,nohyperref]{emnlp2021}
\usepackage[review]{emnlp2021}
% Standard package includes
\usepackage{times}
\usepackage{latexsym}


% For proper rendering and hyphenation of words containing Latin characters (including in bib files)
\usepackage[T1]{fontenc}
% For Vietnamese characters
% \usepackage[T5]{fontenc}
% See https://www.latex-project.org/help/documentation/encguide.pdf for other character sets

% This assumes your files are encoded as UTF8
\usepackage[utf8]{inputenc}

% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

% If the title and author information does not fit in the area allocated, uncomment the following
%
%\setlength\titlebox{<dim>}
%
% and set <dim> to something 5cm or larger.

%\renewcommand{\UrlFont}{\ttfamily\small}

\usepackage{url}

\usepackage{soul}
%\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage[ruled,vlined]{algorithm2e}
\urlstyle{same}

\usepackage{tablefootnote}
\usepackage{helvet}
\usepackage{courier}
\usepackage{color}
\usepackage{amsmath,amsfonts} %,amssymb,amsthm,amsopn}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{diagbox}
\usepackage{array}
\usepackage{multicol}
\usepackage{threeparttable}
\usepackage{epstopdf}
\usepackage{listings}
\usepackage{multirow}
\usepackage{subfigure}
\usepackage{makecell}

%\theoremstyle{definition}
\newtheorem{example}{Example}

\newcommand{\secref}[1]{Section \ref{#1}}
\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\eqnref}[1]{Eq. (\ref{#1})}
\newcommand{\tabref}[1]{Table \ref{#1}}
\newcommand{\exref}[1]{Example \ref{#1}}
\newcommand{\cut}[1]{}
\newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}

\newcommand{\KZ}[1]{\textcolor{blue}{Kenny: #1}}
\newcommand{\JQ}[1]{\textcolor{red}{JQ: #1}}
\newcommand{\YZ}[1]{\textcolor{red}{Yizhu: #1}}


%\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{849} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\BibTeX{B\textsc{ib}\TeX}

\title{Abstractive Opinion Summarization by Weak-Supervision from
Semi-Structured Data}

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\}

\date{}

\begin{document}
\maketitle

\begin{abstract}
Abstractive opinion summarization of multiple reviews
 using deep learning techniques suffers from a lack 
of reference summary.
Previous dataset creation methods are based on
textual similarities between reviews.
In this way,
some information of the summary may be missing from its input reviews.
%In the summary thus created, some information 
%from the input reviews may be missed out.
%Previous dataset creation methods take a review as a summary 
%and select its multiple reviews 
%based on textual similarities.
% between the summary and other reviews.
%In this way,
%some information of the summary may be
%missing from its %matching  
%input reviews.
In this paper, 
%we first summarize opinions of reviews by
%extracting aspects and opinions from reviews
%in advance. 
we convert each textual review into a semi-structured
%review
version consisting of 
opinion-aspect pairs (OAs) and implicit sentences (ISs).
We propose a new data creation method to get a semi-structured training data 
with OAs and ISs as input and summary as output,
%create the synthetic training data by sampling a review as summary 
%and constructing the noisy version of its semi-structured information as input together with 
and design an aspect-guided 
encoder-decoder model.
Experiments on the Yelp and Amazon datasets show 
favorable results of our approach over
previous state-of-the-art baselines.
\cut{%%%%%
we present a semi-structured review that consists of
opinion-aspect pairs extracted from the review
and sentences without opinion-aspect pairs.
%, extracted {\em opinion-aspect pairs} (OAs) of this review 
%and {\em other sentences} (OSs) without extracted OAs.
%that do not contain OAs. 
%Each product has an OAs group and an OSs group.
%\KZ{The following three sentences can be simplified and combined to
%one.}
We create the synthetic training data 
by sampling a review as summary and
generating the noisy version of semi-structured summary 
as semi-structured multiple reviews. 
We introduce variant aspect guided summarization models
for producing summaries from semi-structured multiple reviews.
%We design a data aggregation heuristics to sample a review as summary
%and generate noisy versions of semi-structured summary as input
%to simulate semi-structured form of actual multi-review .
%as input.
%which simulates the OAs and OSs of multi-review and summary during generation.
%We propose an aspect guided encoder-decoder model
%to generate summary from reconstructed semi-structured data.
%During test, the input of model is the extracted OAs and OSs of multi-review
%with opinion attention and context attention, 
}%%%%%%%
% in terms of automatic and manual evaluation metric.
\cut{%%%%% submitted abstract
	Abstractive opinion summarization using deep learning techniques lacks training data. Previous dataset creation methods always select summary and its multi-review by the textual similarity between reviews.
	However, summary and its multi-review in these datasets are inconsistent in aspect and opinion.
	In this paper, we represent a review by extracted opinion-aspect pairs (OAs) of this review and other sentences (OSs) without extracted OAs. We design a data aggregation heuristics to sample a review as summary and generate noisy versions of OAs and OSs as input to simulate them in actual multi-review. We propose an aspect guided encoder-decoder model to generate summary from selected OAs and OSs. The results shows that our model outperforms the state-of-the-art models on Yelp and Amazon.
}%%%%
\end{abstract}



\input{intro}
\input{approach}
\input{eval}
\input{related} 
\input{conclude}
\bibliographystyle{acl_natbib}
\bibliography{opinionsum}

%\appendix
\end{document}

