\section{Results on the Ubuntu Dialogue Corpus}
\label{sec:results}

The Ubuntu dataset~\cite{lowe2015ubuntu} is a large unannotated dialogue corpus designed for next utterance classification and dialogue generation. It is extracted from multi-party dialogues, while conversation disentanglement is still an unsolved problem. So, many dialogues in this dataset don't make much 
sense because the two parties are not actually talking to each other (they were
talking to a third party whose utterances were removed). 
It maybe a good dialogue resource with 930,000 dialogues, but it is 
impossible to label such large amount of dialogues to filter out all
the irrelevant turns.

We randomly sampled 1000 dialogues having more than 10 turns. Then we annotated the extracted corpus with (Q, A, O) labels as mentioned above. If there is no Q-NQ pairs existing in the dialogue, it is replaced by a new dialogue with similar number of turns. Finally, we collected 1000 annotated dialogues. The QAs in Ubuntu corpus mainly focus on step-by-step operations and the dialogues are lack of long distance QAs. The results are showed in Table \ref{tab:mainResults-ubuntu}.

\begin{table}[th]
	\scriptsize
	\centering
	\begin{tabular}{p{1cm}<{\centering}p{1cm}<{\centering}ccc}
		\toprule[1.5pt]
		Models &P&R& F1\\
		\midrule[1pt]
		GD1&89.33&58.96&71.03\\
		GDN  &84.62&78.86&81.64\\
		GD1+J&83.62&65.02&73.16\\
		GDN+J&57.05&89.49&69.68\\
		\hline
		mLSTM&64.88&0.37&0.73\\
		Distance&84.97&78.99&81.87\\
		RPN&71.33&61.80&66.23\\
		\hline
		DIS&85.36&66.21&74.57\\
		HTY&85.25&77.53&81.20\\
		HDM&85.88&77.53&81.48\\
		\hline
		Human &90.28&84.42&87.25\\
		\bottomrule[1.5pt]
	\end{tabular}
	\vspace{-0.25cm}
	\caption{The end-to-end performance of all methods on the Ubuntu test dataset.}
	\label{tab:mainResults-ubuntu}
\end{table}

The results of Distance and GDN achieves the top-2 highest F1 score, which is consistency with the fact that 41.95\% of questions have no answers and 79.55\% of the QA pairs are consecutive in the dialogue. However, it still shows the effectiveness of our full model HDM, which achieve the competitive results to the best results.
%perfectly takes use of the distance and history information and achieve the competitive results to the best results. 

%Since the doctor-patient corpus better meets our needs, we didn't list the results on the Ubuntu corpus.


%41.95\%of questions have no answers and 79.55\% of the QA pairs are consecutive in the dialogue, which reflective the obvious weakness of regarding the Ubuntu dataset as a QA matching dataset with limited annotations.
