%# -*- coding: utf-8-unix -*-
% !TEX program = xelatex
% !TEX root = ../thesis.tex
% !TEX encoding = UTF-8 Unicode

\chapter{面向复杂语义的知识库自动问答研究}
\label{chap:compqa}

本章的研究为基于知识库的自动问答任务。
用户提出的问句可能具有复杂语义，其中包含了未知答案与相关实体的多种关系，
因此复杂问句的回答过程充满了挑战。
我们提出了面向复杂语义的知识库问答模型，
主要特点在于，我们利用神经网络学习复杂语义结构的整体连续特征表示，
从而捕捉不同语义成分之间的信息交互。
%本章提出的模型复杂问题数据集上取得了优秀的结果，
%在多个简单问题数据集上依然保持竞争力。

%Answering complex questions that involve multiple entities and
%multiple relations using a standard knowledge base is an open and 
%challenging task. Most existing KBQA approaches focus on
%simpler questions and do not work very well on complex questions
%because they were not able to simultaneously represent the question
%and the corresponding complex query structure.
%In this work, we encode such complex query structure into a uniform vector 
%representation, and thus successfully capture the interactions between
%individual semantic components within a complex question. This approach
%consistently outperforms existing methods on complex questions while
%staying competitive on simple questions.


\input{tex/compqa_intro}
\input{tex/compqa_related}

%============================================================%

\section{我们的方法}%xxxx模型  %approach
\label{sec:compqa-approach}

本节将具体阐述复杂语义下的自动问答模型。
主要包括四个部分：
\begin{enumerate*}
\item{基于分阶段的方式生成所有候选查询图；}
\item{通过神经网络定义问句和查询图整体之间的语义相似度；}
\item{基于集成的方式对已有的实体链接结果进行扩充；}
\item{具体的训练以及测试流程。}%就是paper里面没有提及的细节（分拆F1 list）
\end{enumerate*}

%In this section, we present our approach for solving complex KBQA.
%First, we generate candidate query graphs by staged generation method (\secref{sec:candgen}).
%Second, we measure the semantic similarities between the question and each query graph using deep neural networks (\secref{sec:rm}).
%Then we introduce an ensemble approach for entity linking enrichment (\secref{sec:ensemble}),
%Finally, we discuss the prediction and parameter learning step of this task (\secref{sec:train}).

\input{tex/compqa_candgen}
\input{tex/compqa_nn}

%============================================================%

\input{tex/compqa_exp}

\section{小结}%conclusion
%半页总得要的吧

本章讨论了面向复杂语义的知识库自动问答任务，
其难点在于复杂问句中包含多个关系，
并不能转换为知识库上的简单三元组查询。
我们沿用关系理解中的模式图思路，提出了基于复杂查询图的语义解析模型，
以解决复杂问句的语义结构表示和语义匹配计算。
据我们所知，我们的工作是首次通过神经网络模型学习查询图整体的连续语义表示，
相对于已有工作，整体语义表示通过池化操作，聚合查询图中不同语义成分的特征，
以捕捉其中的语义相近、互补等交互。
与此同时，我们研究了提升问答效果的多种不同的方法，
主要包括候选查询图生成的时间、类型限制优化，
引入依存语法信息捕捉与特定语义成分的局部匹配，
以及利用集成方法扩充实体链接结果，提高候选查询图的召回率。
我们在三个广泛使用的问答数据集上进行了测试，
在全部由复杂问题组成的ComplexQuestions中，
我们提出的模型取得了目前最好的效果，并且显著优于已有模型；
在主要由简单问题构成的WebQuestions，以及全部为简单问题的SimpleQuetions中，
基于复杂查询图的模型依然拥有竞争力，领先于绝大部分已有模型，
同时语义匹配模型具有轻量级、参数少等优势，证明了其有效性。

后续的研究主要包括了对更多种语义限制的挖掘，
例如隐含时间限制，即问句中不出现具体的时间，而是以从句形式描述与该时间相关的事件。
一些研究工作对问句进行从句提取的方式，先回答从句部分，再将时间答案代回主句进行第二次回答。
为了减少对问句进行特殊处理的步骤，我们会研究如何将隐含时间限制的挖掘纳入现有的查询图框架中，
进一步提升问答模型效果和适用性。

%%In this work, we propose a semantic parsing based approach to handle complex KBQA task.
%%aims at  handle complex questions on KBQA in SP + NN.
%To the best of our knowledge, this is the first work to handle
%complex KBQA task by explicitly encoding the complete semantics of a complex query graph
%using neural networks.
%We studied different methods to further improve the performance,
%mainly leveraging dependency parse and the ensemble method for linking enrichment.
%%encode represent question
%%and predicate sequences, and leveraging dependency parse information
%%and   ensemble  entity linking  enrichment method.
%%to improve the 
%%And we present a 
%Our model becomes the state-of-the-art on ComplexQuestions dataset,
%and produces competitive results on other simple question based datasets.
%%compQ : 42.8 \% signifiantly higher than
%%simple: SimpQ and WebQ outperforming lot of works
%Possible future work includes supporting more complex semantics like implicit time constraints.
%
%%complex questions in different categories,
%%such as questions implicit time constraints and syntactically simple
%%but semantically complex questions.
%%understanding implicit time constraints within in a question,
%%and 
%%future work: understand vague constraints,
%%implicit time constraints.


本章的研究成果已发表于2018年国际会议Empirical Methods in Natural Language Processing
(EMNLP 2018)，论文题目为
``Knowledge Base Question Answering via Encoding of Complex Query Graphs'' 。
%\cite{luo2015inferring,luo2018cross,luo2017data,luo2018knowledge}
