%# -*- coding: utf-8-unix -*-
% !TEX program = xelatex
% !TEX root = ../thesis.tex
% !TEX encoding = UTF-8 Unicode

\chapter{自然语言关系的语义理解研究}
\label{chap:relation}


本章的研究中，我们关注从海量纯文本数据中挖掘出的关系三元组。
%给定一个具体的关系三元组，主语和宾语可以直接对应为知识库中的实体，
二元关系是一个三元组的语义核心，它扮演谓语的成分，描述了主语和宾语实体间具有的特定联系。
%以此，本章的目标是以知识库中的内容为桥梁，学习关系谓语的语义表示。
%由于事实三元组和关系三元组具有结构相似性，
%若能建立从关系谓语到知识库谓语的映射，机器将很容易理解一个关系的语义。
然而，由于关系具有多义性，以及知识库与自然语言间存在的语义间隔，
我们很难直接像实体理解那样，建立关系和知识库谓词的一一对应。
因此，我们尝试从多个角度出发，寻找关系与知识库之间存在的复杂匹配。

% 本章的第一部分利用知识库蕴含的类型层次关系，挖掘不同关系谓语所连接的实体所具有的类型偏好，
% 通过具有代表性的（主语，宾语）类型搭配，在粗粒度上区分关系谓语的不同含义；
% 第二部分则站在更细的粒度，利用知识库中已有的谓语、实体等元素，构造能和关系谓语
% 精确匹配的语义结构，我们称其为模式图，它能很好地支持复杂语义。
% %本章分为两部分。第一部分以粗粒度视角挖掘关系谓语的不同含义，
% %第一部分中，我们对  
% %我们首先对关系   进行了初步
% %第一部分的研究
% %对每一种关系谓语，我们利用知识库中蕴含的类型层次关系，
% %挖掘不同关系谓语所连接的主语和宾语实体所具有的类型偏好，
% %并生成一系列具有代表性的（主语，宾语）类型搭配，在粗粒度上区分关系谓语的不同含义。
% %第二部分  则站在更细的粒度，利用知识库中已有的谓语和实体，构造能和关系谓语精确匹配的语义结构。
% %我们将这种结构化表示称为模式图，与传统路径规则相比，模式图可以更好地支持复杂语义。
% %对于每个关系谓语，我们根据其已知的三元组搜索出候选模式图，
% %并提出了数据驱动的方式学习不同模式图的重要性。
% 我们在多个开放式信息抽取数据集上进行实验，
% 不同粒度的关系语义表示均具有良好的的可解释性，
% 与此同时，细粒度的语义结构能够用于知识库补全任务，具有非常不错的表现。


%============================================================%

\section{关系的主宾语类型搭配挖掘}
\label{sec:tinf}

这一节的研究中，我们旨在寻找不同关系连接的实体所具有的类型偏好，
并利用知识库中的实体信息构建丰富的类型层次关系，
从而挖掘具有代表性的(主语，宾语)类型搭配，
在粗粒度上展现关系的不同含义。

\input{tex/tinf_intro}
%\input{tex/tinf_problem}
\input{tex/tinf_approach}
\input{tex/tinf_exp}

%============================================================%

\section{关系的结构化语义挖掘}
\label{sec:schema}

%This paper studies the problem of discovering the structured knowledge representation of binary natural language relations.
%The representation, known as the schema, generalizes the traditional path of predicates to support more complex semantics.
%We present a search algorithm to generate schemas over a knowledge base,
%and propose a data-driven learning approach to discover the most suitable representations to one relation.
%Evaluation results show that inferred schemas are able to represent precise semantics,
%and can be used to enrich manually crafted knowledge bases.

上一节的研究目标是挖掘一个关系所存在的主宾语类型搭配，用于区分不同的语义。
本节的研究重点放在了深入理解关系本身，用结构化的符号代替字符形式的描述。
我们提出了基于模式图的语义表示方法，与传统路径规则相比，
图结构具有的分支可以更好地支持复杂语义，
具有良好可解释性的同时，也可被用于知识库补全任务中。


\input{tex/schema_intro}
\input{tex/schema_related}
\input{tex/schema_problem}

\subsection{我们的方法}
\label{sec:schema-approach}

本节主要介绍将自然语言关系映射为模式图的具体方式。
给定关系$r$以及其一系列关系实例作为训练数据，
我们首先依据给定的主宾语对($e_{subj}$, $e_{obj}$)，
从它们支持的所有模式图中寻找可能性较高的候选模式图，
然后对具有不同粒度的模式图进行重要性衡量。
由于没有直接的\textless 关系，模式图 \textgreater 对作为训练数据，
我们提出了一种基于远距离监督学习的方式，
学习所有候选图上的概率分布。

%TODO: candgen可以多讲一些，为了凑IJCAI篇幅，这里的内容实在是有点少。
\input{tex/schema_candgen}
\input{tex/schema_inference}

\input{tex/schema_exp}


\section{本章小结}

本章的研究着眼于自然语言中的二元关系，根据关系已有的三元组实例，
推理出其所具有的语义。
第一部分的工作将关系模式定义为知识库中的主宾语类型搭配，
并利用知识库的类型层次结构实现模式推理。
我们提出的方法基于一个直观的思路，即尽可能使用具体的模式匹配更多的已知实例。
在ReVerb上进行的人工测评实验表明，
此方法推理出的最具有代表性的模式具有较高的准确度，
效果优于传统的选择偏好模型。
% In summary, our work describes a data driven approach of
% relation schema inference.
% By maximizing the support of both arguments simultaneously,
% our system is able to generate human-readable type pairs for 
% a binary relation from Open IE systems. 
% % what is the result
% Our experiments shows that the top ranked relation schemas for 
% each relation are accurate according to human judges.
% The proposed framework can be integrated with future Open IE systems.
% % what's the future vision
% %In the future, we are going to explore researches on question answering field, leveraging these
% %type pair information to improve answer quality.

第二部分的工作直接挖掘关系语义和结构化知识之间的匹配。
为了使语义理解具有良好的可解释性，我们提出了基于模式图的规则推导模型，
模式图是对传统路径规则的泛化，以 ``{路径+分支}'' 的结构描述具有更多限制的复杂语义。
该模型将关系语义表示为多个模式图的概率分布，以适应关系的多义性。
我们对PATTY中的热门关系进行模式图推理，
多个具体例子表明，基于模式图的结构表示有能力描述更加细化的关系语义，
而且质量优于其它已有的规则推导模型。
此外，基于模式图的语义表示还可用于知识库补全任务中，
在主宾语预测和三元组分类两个子任务上，
效果优于其它规则推导及知识库向量模型。

后续的研究主要包括两部分：
数据预处理方面，关系三元组的实体链接需要优化，主语和宾语都可能存在不可链接实体，需要进行识别从而过滤杂乱三元组；
语义理解模型方面，本章的两个工作均基于数据驱动，对于已知三元组较少的长尾关系，模型效果会明显降低，
如何利用关系本身的短语信息作为额外特征进行推理，是值得研究的方向。
%提高准确率 用于问答系统


% This work mines the equivalence between natural language relations and structured 
% knowledge known as schemas.  It generalizes the simple path representation 
% by adding constraints along the path and thus support more complex semantics.
% Experiments show that schema representation is able to describe the concrete 
% and precise semantic meaning. Schemas thus learned have higher quality than
% those learned by existing rule induction approaches. Our approach can also be applied
% to the traditional knowledge base completion problem and yield good results. 
% %and performs as well as the state-of-the-art methods on ordinary relations.
% %To the best of our knowledge, this is the first attempt to directly model complex NL relations in knowledge bases.
% %We have observed that this data-driven approach benefits from 
% %increasing amount of training data, but it's sensitive to the noisy pairs in the input.
% %Future research may aim at designing a self-adaptive algorithm to detect and filter noisy data
% %from relation instances, and leverage the structural knowledge to improve performance of QA systems.
% %
% %Future direction of this research includes schema inference from
% %small data sets, efficient generation of
% %more complex schemas, including comparative and aggregative constraints, 
% %and the exploration of other features during
% %schema weighting.
% %

本章中，关系主宾语类型搭配挖掘的研究成果已发表于
2015年国际会议Empirical Methods in Natural Language Processing
(EMNLP 2015)，论文题目为
``Inferring Binary Relation Schemas for Open Information Extraction'' ；
关系结构化语义挖掘的研究成果已发表于
2017年国际会议International Joint Conference on Artificial Intelligence
(IJCAI 2017)，论文题目为
``A Data-Driven Approach to Infer Knowledge Base Representation for Natural Language Relations'' 。






% =============== original abstract ================ %

% This paper presents a framework to model the semantic representation
% of binary relations produced by open information extraction systems.
% For each binary relation, we infer a set of preferred types on the two
% arguments simultaneously,
% and generate a ranked list of type pairs which we call schemas.
% All inferred types are drawn from the Freebase type taxonomy,
% which are human readable. Our system collects 171,168 binary
% relations from ReVerb, and is able to produce
% top-ranking relation schemas with a mean reciprocal rank of 0.337.
% 
% This paper studies the problem of discovering the structured knowledge representation of binary natural language relations.
% The representation, known as the schema, generalizes the traditional path of predicates to support more complex semantics.
% We present a search algorithm to generate schemas over a knowledge base,
% and propose a data-driven learning approach to discover the most suitable representations to one relation.
% Evaluation results show that inferred schemas are able to represent precise semantics,
% and can be used to enrich manually crafted knowledge bases.
% 
