%# -*- coding: utf-8-unix -*-
% !TEX program = xelatex
% !TEX root = ../thesis.tex
% !TEX encoding = UTF-8 Unicode

\chapter{自然语言关系的深度语义挖掘}
\label{chap:schema}

挖掘更深层的语义结构

This paper studies the problem of discovering the structured knowledge representation of binary natural language relations.
The representation, known as the schema, generalizes the traditional path of predicates to support more complex semantics.
We present a search algorithm to generate schemas over a knowledge base,
and propose a data-driven learning approach to discover the most suitable representations to one relation.
Evaluation results show that inferred schemas are able to represent precise semantics,
and can be used to enrich manually crafted knowledge bases.

\input{tex/schema_intro}
\input{tex/schema_related}
\input{tex/schema_problem}

%============================================================

\section{我们的方法}
\label{sec:schema-approach}

本节主要介绍将自然语言关系映射为模式图的具体方式。
给定关系$r$以及其一系列三元组作为训练数据，
我们首先依据给定的主宾语对($e_{subj}$, $e_{obj}$)，
从它们支持的所有模式图中寻找可能性较高的候选模式图，
然后对具有不同粒度的模式图进行重要性衡量。
由于没有直接的\textless 关系，模式图 \textgreater 对作为训练数据，
我们提出了一种基于远距离监督学习的方式，
学习所有候选图上的概率分布。

%TODO: candgen可以多讲一些，为了凑IJCAI篇幅，这里的内容实在是有点少。
\input{tex/schema_candgen}
\input{tex/schema_inference}

%============================================================

\input{tex/schema_exp}


\section{小结}
This work mines the equivalence between natural language relations and structured 
knowledge known as schemas.  It generalizes the simple path representation 
by adding constraints along the path and thus support more complex semantics.
Experiments show that schema representation is able to describe the concrete 
and precise semantic meaning. Schemas thus learned have higher quality than
those learned by existing rule induction approaches. Our approach can also be applied
to the traditional knowledge base completion problem and yield good results. 
%and performs as well as the state-of-the-art methods on ordinary relations.
%To the best of our knowledge, this is the first attempt to directly model complex NL relations in knowledge bases.
%We have observed that this data-driven approach benefits from 
%increasing amount of training data, but it's sensitive to the noisy pairs in the input.
%Future research may aim at designing a self-adaptive algorithm to detect and filter noisy data
%from relation instances, and leverage the structural knowledge to improve performance of QA systems.
%
%Future direction of this research includes schema inference from
%small data sets, efficient generation of
%more complex schemas, including comparative and aggregative constraints, 
%and the exploration of other features during
%schema weighting.
%

本章的研究成果已发表于2017年国际会议International Joint Conference on Artificial Intelligence
(IJCAI2017)，论文题目为
``A Data-Driven Approach to Infer Knowledge Base Representation for Natural Language Relations''。
