\section{Refined Approach}
\label{sec:refine}
The baseline approach introduced in Section~\ref{sec:basic} is not
sensitive to different senses of a term. In this section, we introduce
a refined approach to address this problem.

\subsection{Overview}

It is necessary to identify and disambiguate senses of the terms in
computing semantic similarity. A simple solution is to use an
existing knowledge database containing sense labels of terms such as
the glosses in WordNet. But none of the handcrafted knowledge bases
has the sufficient data coverage. Our solution to this problem is to
automatically determine senses in computing semantic similarity.

% cluster the concept context of a term into different groups, each
% representing a unique sense of the term. More details of this method
% and the significant refinement to the basic approach is presented in
% the next section.


Given a term, we define its {\it concept context} as the entire set of
concepts that the term belongs to in Probase.  We perform automatic
sense disambiguation by concept clustering. % , and we introduce a new
% similarity function based on the clustered concept contexts to compute
% similarity of two terms.
Then, given two terms such as ``microsoft'' and ``apple'', we define
their similarity as the highest similarity between any sense of the
first term and any sense of the second term. Thus, we will be
comparing the company sense of ``apple'' with ``microsoft''.

The above approach has a potential challenge. Consider two terms such
as ``music'' and ``lunch'', which do not have much
similarity. However, each of them has a general and vague sense of~``activity'', which is captured by a small cluster of concepts. If we
compare the two terms on this sense, we will find they have high
similarity. To deal with this problem, we introduce an optimization
known as cluster pruning to our algorithm. % to
% remove small clusters and vague (general) senses and thus improve the
% effectiveness of the framework.

\input{Clustering}

\input{OurAlgorithm}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "paper"
%%% End:
