\def\year{2019}\relax
%File: formatting-instruction.tex
\documentclass[letterpaper]{article} %DO NOT CHANGE THIS
\usepackage{aaai19}  %Required
\usepackage{times}  %Required
\usepackage{helvet}  %Required
\usepackage{courier}  %Required
\usepackage{url}  %Required
\usepackage{graphicx}  %Required
\frenchspacing  %Required
\setlength{\pdfpagewidth}{8.5in}  %Required
\setlength{\pdfpageheight}{11in}  %Required

\usepackage{latexsym}
\usepackage{makecell}
\usepackage{epsfig}
\usepackage{algorithm, algpseudocode}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{color}
\usepackage{subfigure}
\usepackage{url}
\usepackage{mathrsfs}
\usepackage{amsmath}
%\usepackage[small]{caption}

\newcommand\BibTeX{B{\sc ib}\TeX}
\newcommand{\secref}[1]{Section \ref{#1}}
\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\eqnref}[1]{Eq. (\ref{#1})}
\newcommand{\exref}[1]{Example \ref{#1}}
\newcommand{\algoref}[1]{Algorithm \ref{#1}}
\newcommand{\tabref}[1]{Table \ref{#1}}
\newcommand{\bi}[1]{\textbf{\textit{#1}}}

\newcommand{\lstm}{\operatornamewithlimits{LSTM}}
\newcommand{\bilstm}{\operatornamewithlimits{BiLSTM}}
\newcommand{\argmax}{\operatornamewithlimits{argmax}}
\newcommand{\seg}{\operatornamewithlimits{seg\_tag}}
\newcommand{\ner}{\operatornamewithlimits{ne\_tag}}
\newcommand{\slot}{\operatornamewithlimits{slot\_fill}}
\newcommand{\batch}{\operatornamewithlimits{Batch}}

%PDF Info Is Required:
\pdfinfo{
	/Title (Deep Cascade Multi-task Learning for Slot Filling in Online Shopping Assistant)
	/Author (Yu Gong,Xusheng Luo,Yu Zhu,Wenwu Ou,Zhao Li,Muhua Zhu,Kenny Q. Zhu,Lu Duan,Xi Chen)}
\setcounter{secnumdepth}{2}

\begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Deep Cascade Multi-task Learning for Slot Filling in Online Shopping Assistant}

\author{
	Yu Gong{$^{1}$\footnotemark[1]\footnotemark[2]},
	Xusheng Luo{$^{1}$\footnotemark[1]},
	Yu Zhu{$^{1}$},
	Wenwu Ou{$^{1}$},
	Zhao Li{$^{1}$},
	Muhua Zhu{$^{1}$},\\
	\bf{\Large{Kenny Q. Zhu{$^{2}$},
	Lu Duan{$^{3}$},
	Xi Chen{$^{1}$}}} \\
	{$^{1}$} Search Algorithm Team, Alibaba Group \\
	{$^{2}$} Shanghai Jiao Tong University \\
	{$^{3}$} Artificial Intelligence Department, Zhejiang Cainiao Supply Chain Management Co.\\
	\{gongyu.gy, lxs140564, zy143829, lizhao.lz, muhua.zmh\}@alibaba-inc.com, \\
	\{santong.oww, gongda.cx\}@taobao.com, kzhu@cs.sjtu.edu.cn, duanlu.dl@cainiao.com
}

\maketitle
\begin{abstract}
%\begin{quote}
Slot filling is a critical task in natural language understanding
(NLU) for dialog systems.
State-of-the-art approaches treat it as a sequence labeling problem
and adopt such models as BiLSTM-CRF.
While these models work relatively well on standard 
benchmark datasets, they face challenges in the context of
E-commerce where the slot labels are more informative
and carry richer expressions.
In this work, inspired by the unique structure of E-commerce knowledge base,
we propose a novel multi-task model
with cascade and residual connections, which 
jointly learns segment tagging, named entity tagging and slot filling.
Experiments show the effectiveness of the proposed
cascade and residual structures. 
Our model has a 14.6\% advantage in F1
score over the strong baseline methods on a new Chinese E-commerce
shopping assistant dataset, while achieving competitive accuracies on
a standard dataset.  
Furthermore, online test deployed on such dominant E-commerce platform
shows 130\% improvement on accuracy of understanding user utterances.
Our model has already gone into production in the E-commerce platform.
%\end{quote}
\end{abstract}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\footnotetext[1]{Equal contribution.}
\footnotetext[2]{Corresponding author.}
\renewcommand{\thefootnote}{\arabic{footnote}}

\input{intro}
	
\input{approach}
	
\input{experiment}
	
\input{related}
	
\input{conclusion}

%\newpage
\bibliographystyle{aaai}
\bibliography{ref}

\end{document}
