\documentclass[letterpaper]{article}

\usepackage{aaai16}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}

\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}

\usepackage{amsmath,amsfonts}
\usepackage{multicol,multirow}
\usepackage{amsthm}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{graphicx,subfigure,epsfig}
\usepackage{url}
\usepackage{color}
\usepackage{array}
\usepackage{diagbox}
\graphicspath{{figures/}}
\newcommand{\KZ}[1]{\textcolor{blue}{[KZ: #1]}}
\newcommand{\KQ}[1]{\textcolor{red}{[KQ: #1]}}
\newcommand{\GY}[1]{\textcolor{red}{[GY: #1]}}
\newcommand{\secref}[1]{Section \ref{#1}}
\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\eqnref}[1]{Eq. (\ref{#1})}
\newcommand{\tabref}[1]{Table \ref{#1}}
\newcommand{\exref}[1]{Example \ref{#1}}
\newcommand{\argmin}{\operatornamewithlimits{argmin}}
\newcommand{\argmax}{\operatornamewithlimits{argmax}}
\newtheorem{example}{Example}
\newtheorem{lemma}{Lemma}
\newtheorem{definition}{Definition}
\newcommand{\cut}[1]{}
\newcommand{\pair}[2]{$\langle$#1, #2$\rangle$}

\newcolumntype{I}{!{\vrule width 1pt}}
\newlength\savedwidth
\newcommand\whline{\noalign{\global\savedwidth\arrayrulewidth
                            \global\arrayrulewidth 1pt}%
                   \hline
                   \noalign{\global\arrayrulewidth\savedwidth}}
\newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}% 放在导言区

\pdfinfo{
/Title (Representing Verbs as Argument Concepts)
/Author (Yu Gong,Kaiqi Zhao,Kenny Q. Zhu)}

\setcounter{secnumdepth}{2}

\begin{document}
\title{Representing Verbs as Argument Concepts}

\author{
Yu Gong{\small $~^{1}$} \and Kaiqi Zhao{\small $~^{2}$} \and
Kenny Q. Zhu{\small $~^{3}$}\\
Shanghai Jiao Tong University, Shanghai, China\\
{\small $~^{1}$}gy910210@163.com, {\small $~^{2}$}kaiqi\_zhao@163.com,
{\small $~^{3}$}kzhu@cs.sjtu.edu.cn}

\maketitle
\begin{abstract}
Verbs play an important role in the understanding of natural
language text. This paper studies the problem of abstracting
the subject and object arguments of a verb into a set of noun
concepts, known as the ``argument concepts''.
This set of concepts, whose size is parameterized,
represents the fine-grained semantics of a verb. For example,
the object of ``enjoy'' can be abstracted into time, hobby and event, etc.
We present a novel framework to automatically infer human
readable and machine computable action concepts
with high accuracy.
\end{abstract}

\input{intro}
\input{problem}
\input{algo}
\input{eval}
\input{related}
\input{conclude}
\section*{Acknowledgments}
Kenny Q. Zhu is the corresponding author, and is partially supported by
the 2013 Google Faculty Research Award. We thank Dr. Haixun Wang
for his valuable comments.

\bibliographystyle{aaai}
\bibliography{./ac}

\end{document}
