\section{Ethical Statement}

% folloing the previous best practices (cite)
% \KZ{Ethical considerations should come after conclusion and are not counted toward the page limit.}
We rely on publicly available Reddit posts\footnote{In the privacy policy of Reddit, the posts are public and accessible to everyone, and Reddit allows third parties to access public Reddit content via the Reddit API and other similar technologies. See \url{https://www.reddit.com/policies/privacy-policy} for more detailed information.} in our work and we make every possible effort to minimize the risk of leaking privacy of individuals in the data collection process. We made no attempt to contact users or link users to other social media accounts following the previous best practices~\cite{cohan2018smhd,losada2017erisk,Suhavi2022TwitterSTMHDAE}. We also replace usernames with random identifiers to prevent users’ identities from being known without the use of external information. 
For the usage of symptom identification dataset, we sign and comply with the data usage agreement to prevent the invasion of privacy or other potential misuses.
% \KZ{We are referring to Zhang too many times. Readers will surely know we are just Zhang et al.}
What's more,  we carefully consider the application of mental disease detection from social media. The purpose of this work are not to replace psychiatrists. Instead, we expect our model to be used as an effective auxiliary tool by experienced psychiatrists in the future.
