\section{Introduction}
\label{sec:intro}


Abstractive opinion summarization~\cite{GeraniMCNN14} belongs to multi-document summarization task,
which aims at automatically
producing a summary from multiple reviews ({\em multi-review})
of an entity 
(a product, a service, et.al.). 
The sequence-to-sequence (seq2seq) models 
have made a great success 
in abstractive summarization
~\cite{NallapatiZSGX16,SeeLM17,LiuLZ18,CelikyilmazBHC18,BART20}. 
The recent opinion summarization methods~\cite{Copycat20, Denoise20, Fewshot20, Plansum20} 
always adopt the seq2seq models, which take summaries as output and create the inputs of these summaries for training and testing,
because of the lack of the (multi-review, summary) pairs.
According to the format of the input, the existing opinion summarization approaches can be
divided into {\em textual} input 
and  {\em structured} input.

\begin{table}[th]
	\centering
	\small


	\begin{tabular}{|m{1.6cm}|m{0.28cm}<{\centering}|m{5.45cm}|}
	\hline
	\multicolumn{3}{|c|}{\rule{0pt}{10pt} \bf Input}  \\	
	\hline
	\multirow{4}{1.4cm}{Textual~\cite{Plansum20}} & $R_1$ & food is very good , service and atmosphere really poor . best to get take out . the rice and beef kabob was really off the charts .\\
	\cline{2-3}
	& $R_2$&the portions are super - generous , and the price is amazing . it also does not hurt that the people there are very nice and friendly .
\\
	\cline{2-3}
	& $R_3$ & it was one of the best lunches in my life ! in addition to great meal i ' ve been enjoying the family atmosphere - i appreciate a lot this part in restaurant business ! 
	\\
	\hline
   Structured~\cite{OpiDig20} & OA &  very good, food \textbf{;} best, lunches \textbf{;} amazing,  price \textbf{;} appreciate restaurant 
	\\
	\hline
	\multirow{2}{0.1cm}{Semi-Structured} & OA &very good, food \textbf{;} poor service \textbf{;} poor atmosphere \textbf{;} generous, portions \textbf{;} amazing,  price \textbf{;} nice, people \textbf{;} friendly people \textbf{;} best, lunches \textbf{;}  great, meal \textbf{;} family, atmosphere \textbf{;} appreciate restaurant\\
	\cline{2-3}
	& IS &best to get take out . \textbf{;} the rice and beef kabob was really off the charts .\\
	\hline
\end{tabular}

	\begin{tabular}{|p{8.05cm}|}
	\hline \rule{0pt}{10pt}
	\makecell[c]{\bf Reference Summary} \\
	\hline
	this place has a excellent \textbf{price point} , and the \textbf{portions} are generous . the \textbf{kabobs} are wonderful . the \textbf{food} is cooked and seasoned well . offers \textbf{take out} as well .
	\vspace{0.2em}\\
	\hline
\end{tabular}

	\begin{tabular}{|m{1.6cm}|m{6.1cm}|}
	\hline
	\multicolumn{2}{|c|}{\rule{0pt}{10pt} \bf Generated Summary}  \\	
	\hline
	Textual~\cite{Plansum20} & i love this place . the \textbf{food} is delicious and the staff is very friendly . i enjoy the atmosphere and the \textbf{prices} are very reasonable . i will definitely be back .
	\\
	\hline
	Structured~\cite{OpiDig20} & the \textbf{food} was good . the \textbf{price} was amazing ! it was the best i have ever had . the restaurant was great and the \textbf{food} came out pretty .
	\\
	\hline
	Semi-Structured ({\em our best})& the \textbf{food} is delicious and can be \textbf{taken out} . the \textbf{price} is amazing and the \textbf{portions} are very generous . the \textbf{kabob} is wonderful . \\
	\hline
\end{tabular}

	\caption{The summaries generated from the input in different formats. 
		%The underlined sentence has no OA pair.  
	%$R$ is textual review, OA is opinion-aspect pair and IS is implicit sentence. 
	Bold words in the input and output are matched.
	``;'' delimites opinion-aspect pairs and implicit sentences.
	}\label{tab:previous_data}  
\end{table}



To create {\em textual} input, the existing methods first sample
a review as a summary and then sample multi-review for this summary.
A textual input is always a set of reviews sampled from all reviews
under the same entity.
FewShot~\cite{Fewshot20}
randomly samples several reviews as the input.
Other approaches create input based on the contents of the summary. 
Denoise~\cite{Denoise20} rewrites the summary to generate the syntatically different inputs and 
extracts lexically similar reviews as inputs. 
PlanSum~\cite{Plansum20} first calculates the aspect and sentiment probability distribution of reviews and summary, and then samples some reviews that are most similar to the summary in terms of such distribution.
However, as shown in  \tabref{tab:previous_data}, 
the textual inputs do not highlight the opinion information, 
The generated summary cannot match
the reference summary in the information about 
``protions'' and ``kabobs''.
Therefore, the summaries generated from textual input always
miss some important opinion information.

The {\em structured} input consisting of the opinion-aspect pairs from reviews can highlight the opinion information well,
but always ignores the sentences that cannot extract opinion-aspect pairs.
OpiDig~\cite{OpiDig20} trains a seq2seq model by taking a review as output and extracting the opinion-aspect pairs from this review as input. 
In this way, OpiDig transforms opinion summarization into making sentences by
opinion-aspect pairs.
At testing, OpiDig clusters the opinion-aspect pairs 
of multi-reviews and selects the center pairs as input to 
generate a summary. 
As shown in \tabref{tab:previous_data}, 
the generated summary from structured input 
is a set of sentences produced only by filtered centre opinion-aspect pairs, which ignores some important sentences that cannot extract typical opinion-aspect pairs of input, such as ``take out'', 
and miss some opinion imformation due to the noise from clustering,
such as ``portions''. 
Thus, the structured input always makes the generated summaries lose important information with respect to reference summary.

To tackle the above problems, we present the semi-structured input consisting of all {\em opinion-aspect pairs} (\textbf{OA}s) and {\em implicit sentences} (\textbf{IS}s) extracted from a set fo reviews.
The IS is the sentence that cannot extract typical OAs from. 
OAs are always the most important information of the reviews
and ISs ensure the integrity of information.
In this paper, 
we convert textual input into semi-structured input and take textual summary as output.
As shown in \tabref{tab:previous_data}, 
compared with the textual input or structured input,
the semi-structured input consisting of OAs and ISs help model attend to salient opinion information,
and avoid that the summary cannot be generated from the synthetic input.

Using semi-structured input to generate summary is the process of extending important OAs to sentences and summarizing
all ISs.
To effectively capture the information of OAs and ISs at same time,
we propose a dual-encoder seq2seq model with an OA encoder and an IS encoder, which can realize the complementarity between OA and IS to prevent the information loss in generated summary. 

In summary, our contributions are as follows:
\begin{enumerate}
\item We construct the semi-structured version of the synthetic datasets on opinion summarization and observe that semi-structured input composed of OAs and ISs is more helpful than textual or structured input.
%\KZ{We need a better word for ``other sentence''
%so people can understand immediately.}
%We show that this is more effective than relying on
%only textual reviews or only opinion-aspect pairs in previous work. 
%(\tabref{tab:traindata})

%\item We propose aspect-variant guided models to deal with
%opinion-aspect pairs and other sentences. (\secref{sec:model}) 
\item 
We propose a seq2seq model with OA encoder and IS encoder for semi-structured input.
This model trained on semi-structured data outperforms previous  
state-of-the-art (SOTA) approaches on the Yelp and Amazon datasets.
%(\tabref{tab:traindata})
\end{enumerate}
