\section{Related Work}
\label{sec:related}

Opinion summarization~\cite{GeraniMCNN14} is a multi-document summarization task,
which can generates
a summary from multiple reviews. 
Different from other multi-document tasks, opinion summarization focuses on opinions and aspects of the product or service.

As the lack of training pairs,
some opinion summarization work~\cite{MeanSum19} uses auto-encoder to train the model 
by a reconstruction loss and a similarity loss. 
Others construct synthetic datasets for training. 
The input format of the synthetic datasets can be divided into the textual input and the structured input.
For the textual input,
the most intuitive way 
\citet{Copycat20, Fewshot20} is to 
regard one review for a product as the summary 
\citet{Plansum20} took the nearest neighbors as inputs based on review representations.
\citet{Denoise20} obtained the input through the segment noising at the token and chunk level, and document noising by replacing the whole review by a similar one. Such textual input makes the generated summary lose important
opinion information because of the neglect of the opinion-aspect pairs.

For the structured input, 
%as the aspects and opinions are quite important for opinion summarization~\cite{MukherjeePVGBG20},
 \citet{AngelidisL18} extracted aspect-specific opinions by out-of-review knowledge. 
%\citet{TianY019} classified words into three types, including aspect, opinion and context and predicted the work type as a first step. 
\citet{OpiDig20} clustered the opinion-aspect pairs extracted from the multi-review and took the centers of the clusters as the input. 
However, all of these works ignore that some detailed other information are left in the sentences without typical opinion-aspect pairs. 

Thus, we takes semi-structured data with
opinion-aspect pairs and implicit sentences as input,
which leads to better summaries.  
