\documentclass{sig-alternate}%[conference][letterpaper]
\usepackage{times,epsfig,proof,url,algorithm,bm}
\usepackage[noend]{algpseudocode}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{multirow}
\usepackage{color}
%\newcommand{\tab}{\hspace*{2ex}}
%\newcommand{\shrink}{\vspace*{-2ex}}
%\newcommand{\cut}[1]{}

\newtheorem{newproperty}{Property}
\newtheorem{newrule}{Rule}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\tabref}[1]{Table \ref{#1}}
\newcommand{\secref}[1]{Section \ref{#1}}
\newcommand{\algoref}[1]{Algorithm \ref{#1}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\LEN}{\mathcal{L}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\T}{\mathcal{T}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\M}{\mathcal{M}}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\newcommand{\KZ}[1]{\textcolor{blue}{[KZ: #1]}}
\newcommand{\JK}[1]{\textcolor{red}{[JK: #1]}}
\begin{document}
\conferenceinfo{IH\&MMSec'13,} {June 17--19, 2013, Montpellier, France.} 
\CopyrightYear{2013} 
\crdata{978-1-4503-2081-8/13/06}
\clubpenalty=10000 
\widowpenalty = 10000
\title{Watermarking Road Maps against
Crop and Merge Attacks}

\numberofauthors{4}
\author{
\alignauthor
Kai Jiang\hspace*{3mm} Kenny Q. Zhu\\
       \affaddr{Shanghai Jiao Tong University}\\
       \affaddr{Shanghai, China}\\
       \email{jkai@sjtu.edu.cn, kzhu@cs.sjtu.edu.cn}
\alignauthor
Yan Huang \\
       \affaddr{University of North Texas}\\
       \affaddr{Denton, TX, USA}\\
       \email{huangyan@unt.edu}
\alignauthor 
Xiaobin Ma \\
       \affaddr{1 Sybase Dr}\\
       \affaddr{Dublin, CA 94568}\\
       \email{xiaobin@cs.umn.edu}
}

%
%\author{
%\alignauthor
%Kai Jiang\\
%       \affaddr{Shanghai Jiao Tong University}\\
%       \affaddr{Shanghai, China}\\
%       \email{jkai@sjtu.edu.cn}
%\alignauthor
%Kenny Q. Zhu \\
%       \affaddr{Shanghai Jiao Tong University}\\
%       \affaddr{Shanghai, China}\\
%       \email{kzhu@cs.sjtu.edu.cn}
%\alignauthor
%Yan Huang \\
%       \affaddr{University of North Texas}\\
%       \affaddr{Denton, TX, USA}\\
%       \email{huangyan@unt.edu}
%\alignauthor
%Xiaobin Ma \\
%       \affaddr{University of North Texas}\\
%       \affaddr{Denton, TX, USA}\\
%       \email{xiaobin@unt.edu}
%}
\maketitle

\begin{abstract}

%Protecting the copyrights of intelligent electric products is an urgent task around the world. One way to deter piracy
%of these products is to make illegal copying very difficult or impossible by approaches such as encryption. A complimentary 
%approach is to embed digital watermarks into the electric products.
%Digital road maps are a valuable resource for GPS navigation and other GIS applications. 
%It is a form of vector graphics but with spatial-geometric properties.
%Watermarking is an important mechanism to protect the copyright of digital
%road maps.  
Past research on watermarking digital road maps has been focused on
deterring common attacks such as adding noise to the whole map so as to
destroy the embedded watermarks. This paper focuses on two less common but
increasingly used types of attack: crop attacks and merge attacks. 
Crop attack crops a fragment of the original map and uses the fragment as a new
map. When the new map is much smaller than the original map, it is called
massive cropping. Merge attack merges maps from various sources together
to form a new map. 
Conventional watermarking techniques fail against these attacks
either because they require global information from the whole map or
they must add too many local watermarks and affect the usability of the maps.
%these two types of attacks totally because they detect waterwarks based on
%global information from the whole map, or they must divide the map into many small
%segments and add many more watermarks locally and thus affect the perception
%and usability of the maps. 
This paper proposes a novel quad-tree based
blind watermarking scheme that partitions the original map according to
the quad-tree and plants just one single bit in each sub-region of the
map. The approach achieves almost 100\% detection accuracy for moderate
crop and merge attacks, and over 80\% accuracy with more than 95\% of the 
original map cropped and removed. Furthermore, the method introduces 
very little distortion to the original map: 
to effectively protect a 23.5MB Minneapolis-St.Paul map against
crop and merge as well as other common attacks, only
423 bits or 53 bytes of watermark is required.
\footnote{Kenny Q. Zhu (the corresponding author) is partially supported 
by NSFC grants 61033002 and 61100050.}
% 
%
%
%
%In this research, we analyse the properties of digital road maps and propose
%a novel blind watermarking framework to protect the IP rights of owners of
%the maps.
%The framework makes use of local information which is collected by a 
%modified Quadtree structure and inserts watermarks according to the density of
%the map. The framework also allows the detection of the illegal use of a
%watermarked map without reference to the original map at all.
%The most important advantage of this framework is that it detects illegal
%use of even a small part of a protected map, in what we call ``massive crop attacks'' 
%and ``merge attacks'', which were previously unsolved problems. 
%The evaluation shows that our approach offers high accuracy with very reasonable
%time complexity.
%
%\KZ{Key points: Traditional watermarking techniques don't handle cropping and
%merging attacks well and they incur bigger distortion to the maps. We are 1) blind;
%2) light-weight (nlogn); 3) limited distortion (only a number of bits are changed);
%4) localized watermarks that can handle massive cropping and merging attacks.}
\end{abstract}
\category{D.2.11}{Software Architectures}{Information hiding} 
\keywords{Watermark, digital road map, quad-tree, crop attack, merge attack}

\input{intro}
\input{problem}
\input{approach}
\input{analysis}
\input{exper}
\input{relate}
\input{conclude}

%\bibliographystyle{abbrv}
%\renewcommand{\baselinestretch}{0.9}
%\bibliography{watermark}
% watermark.bib is the name of the Bibliography in this case
\begin{thebibliography}{10}

\bibitem{mndoturl}
{MN}/{DOT}.
\newblock \url{http://www.dot.state.mn.us/}.

\bibitem{tigerurl}
{TIGER}.
\newblock \url{http://www.census.gov/}.

\bibitem{abramowitz1965handbook}
M.~Abramowitz and I.~Stegun.
\newblock {\em Handbook of mathematical functions: with formulas, graphs, and
  mathematical tables}, volume~55.
\newblock Dover publications, 1965.

\bibitem{AgrawalK02}
R.~Agrawal and J.~Kiernan.
\newblock Watermarking relational databases.
\newblock In {\em VLDB}, pages 155--166, 2002.

\bibitem{Bird09:Shape}
S.~Bird, C.~Bellman, and R.~v. Schyndel.
\newblock A shape-based vector watermark for digital mapping.
\newblock In {\em Proceedings of the 2009 Digital Image Computing: Techniques
  and Applications}, pages 454--461. IEEE Computer Society, 2009.

\bibitem{DOUGLASD.H.:1973}
D.~H. Douglas.
\newblock Algorithms for the reduction of the number of points required to
  represent a line or its a caricature.
\newblock {\em The Canadian Cartographer}, 10(2):112--122, 1973.

\bibitem{Han06:Adaptive}
P.~Han, J.~Gong, and L.~Cheng.
\newblock An improved adaptive watermarking algorithm for vector digital maps.
\newblock In {\em Geoscience and Remote Sensing Symposium,IGARSS}, pages 2844
  --2847, 2006.

\bibitem{Huo10:Polyline}
X.-J. Huo, T.-Y. Seung, B.-J. Jang, S.-H. Lee, and K.-R. Kwon.
\newblock A watermarking scheme using polyline and polygon characteristic of
  shapefile.
\newblock In {\em ICINIS, 2010}, pages 649 --652, 2010.
\vfill\eject
\bibitem{GangKC01:mask}
H.~Kang, K.~Kim, and J.~Choi.
\newblock A vector watermarking using the generalized square mask.
\newblock In {\em ITCC}, pages 234--236. IEEE Computer Society, 2001.

\bibitem{Kim11:copyright}
J.~Kim, S.~Won, W.~Zeng, and S.~Park.
\newblock Copyright protection of vector map using digital watermarking in the
  spatial domain.
\newblock In {\em Digital Content, Multimedia Technology and its Applications
  (IDCTA), 2011 7th International Conference on}, pages 154 --159, aug. 2011.

\bibitem{Kitamura01:DFT}
I.~Kitamura, S.~Kanai, and T.~Kishinami.
\newblock Copyright protection of vector map using digital watermarking method
  based on discrete fourier transform.
\newblock In {\em Geoscience and Remote Sensing Symposium, 2001. IGARSS '01.
  IEEE 2001 International}, volume~3, pages 1191 --1193 vol.3, 2001.

\bibitem{Spr:scheme}
S.-H. Lee and K.-R. Kwon.
\newblock Vector watermarking scheme for {GIS} vector map management.
\newblock {\em DOI10.1007/s11042-011-0894-y SpringerLink}, 2011.

\bibitem{Liyuanyuan03}
Y.~Li and L.~Xu.
\newblock A blind watermarking of vector graphics images.
\newblock In {\em ICCIMA '03: Proceedings of the 5th International Conference
  on Computational Intelligence and Multimedia Applications}, page 424,
  Washington, DC, USA, 2003. IEEE Computer Society.

\bibitem{Niu06:Survey}
X.~Niu, C.~Shao, and X.~Wang.
\newblock A survey of digital vector map watermarking.
\newblock In {\em 2006 International Journal of Innovative
  Computing,Information and Control Volume 2}, 2006.

\bibitem{OhbuchiUE02}
R.~Ohbuchi, H.~Ueda, and S.~Endoh.
\newblock Robust watermarking of vector digital maps.
\newblock In {\em ICME (1)}, pages 577--580, 2002.

\bibitem{OhbuchiUE03}
R.~Ohbuchi, H.~Ueda, and S.~Endoh.
\newblock Watermarking 2d vector maps in the mesh-spectral domain.
\newblock In {\em Shape Modeling International}, pages 216--228, 2003.

\bibitem{PuDJ06}
Y.-C. Pu, W.-C. Du, and I.-C. Jou.
\newblock Toward blind robust watermarking of vector maps.
\newblock In {\em ICPR (3)}, pages 930--933, 2006.

\bibitem{Schulz:2004}
G.~Schulz and M.~Voigt.
\newblock A high capacity watermarking system for digital maps.
\newblock In {\em MM{\&}Sec}, pages 180--186, 2004.

\bibitem{SionAP02}
R.~Sion, M.~J. Atallah, and S.~Prabhakar.
\newblock On watermarking numeric sets.
\newblock In {\em IWDW}, pages 130--146, 2002.

\bibitem{SionAP03}
R.~Sion, M.~J. Atallah, and S.~Prabhakar.
\newblock Rights protection for relational data.
\newblock In {\em SIGMOD Conference}, pages 98--109, 2003.

\bibitem{DFT}
V.~Solachidis and I.~Pitas.
\newblock Watermarking polygonal lines using fourier descriptors.
\newblock {\em Computer Graphics and Applications, IEEE}, 24(3):44 -- 51,
  may-jun 2004.

\bibitem{Illustration}
H.~Sonnet, T.~Isenberg, J.~Dittmann, and T.~Strothotte.
\newblock Illustration watermarks for vector graphics.
\newblock {\em Computer Graphics and Applications, Pacific Conference on},
  0:73, 2003.

\bibitem{Voigt:2003}
M.~Voigt and C.~Busch.
\newblock Feature-based watermarking of 2d-vector data.
\newblock In {\em SPIE,Security and Watermarking of Multimedia Content.Santa
  Clara,}, pages 359--366, 2003.

\bibitem{YanLW11}
H.~Yan, J.~Li, and H.~Wen.
\newblock A key points-based blind watermarking approach for vector geo-spatial
  data.
\newblock {\em Computers, Environment and Urban Systems}, 35(6):485--492, 2011.

\end{thebibliography}
\end{document}
