%-----------------------------------------------------------------------------
%
%               Template for sigplanconf LaTeX Class
%
% Name:         sigplanconf-template.tex
%
% Purpose:      A template for sigplanconf.cls, which is a LaTeX 2e class
%               file for SIGPLAN conference proceedings.
%
% Guide:        Refer to "Author's Guide to the ACM SIGPLAN Class,"
%               sigplanconf-guide.pdf
%
% Author:       Paul C. Anagnostopoulos
%               Windfall Software
%               978 371-2316
%               paul@windfall.com
%
% Created:      15 February 2005
%
%-----------------------------------------------------------------------------


\documentclass[article,reprint]{sigplanconf}

% The following \documentclass options may be useful:
%
% 10pt          To set in 10-point type instead of 9-point.
% 11pt          To set in 11-point type instead of 9-point.
% authoryear    To obtain author/year citation style instead of numeric.

\usepackage{amsmath,amssymb,amsthm}
\usepackage{color,graphicx,subfigure}
\usepackage{algpseudocode}
\algtext*{EndWhile}% Remove "end while" text
\algtext*{EndIf}% Remove "end if" text
\algtext*{EndFor}% Remove "end for" text
\usepackage{qtree}
\usepackage{epsfig,epstopdf}
\usepackage{multirow}
\usepackage{listings}
\usepackage{url}

\newcommand{\shrink}{\vspace*{-2ex}}

\newcommand{\XJ}[1]{\textcolor{red}{[XJ: #1]}}
\newcommand{\KZ}[1]{\textcolor{blue}{[KZ: #1]}}
\newcommand{\RY}[1]{\textcolor{blue}{[RY: #1]}}

\newcommand{\nat}{\mathbb{N}}

\newcommand{\cm}{\textbf{cm}}
\newcommand{\cu}{\textbf{cu}}
\newcommand{\dm}{\mathcal{DM}}
\newcommand{\mkstore}{\Delta_0}
\newcommand{\alltype}{\mathcal{T}}
\newcommand{\allop}{\mathcal{P}}
\newcommand{\allstore}{\mathcal{D}}
\newcommand{\dtrans}{\psi}
\newcommand{\dptype}{\tau_p}
\newcommand{\dstype}{\tau_d}
\newcommand{\alluniv}{\mathcal{U}}
\newcommand{\allexpr}{\mathcal{E}}

\newcommand{\emptytop}{U_\emptyset}

\newcommand{\typeof}[1]{\tau\ldbrack #1\rdbrack}

% transition arrows
\newcommand{\uto}{\longrightarrow}
\newcommand{\gto}{\hookrightarrow}

\newcommand{\gmerge}{merge}%{\textsc{Merge}}
\newcommand{\gpaste}{paste}%{\textsc{Paste}}

\newcommand{\snapshot}{\mathcal{S}}%{\textsc{\color{red}Snapshot}}

\newcommand{\ldbrack}{[\hspace{-0.5mm}[}
\newcommand{\rdbrack}{]\hspace{-0.5mm}]}
\newcommand{\lbb}{\{\hspace{-0.7mm}|}
\newcommand{\rbb}{|\hspace{-0.7mm}\}}

\newcommand{\compact}[1]{\!\!#1\!}
\newcommand{\bk}{\hspace{-1mm}}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\newtheorem{property}{Property}
\newtheorem{axiom}{Axiom}
\newtheorem{example}{Example}

\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\tabref}[1]{Table \ref{#1}}
\newcommand{\eqnref}[1]{Eq. (\ref{#1})}

\newcommand{\nl}{\vspace*{3mm}}

\makeatletter
 \let\@copyrightspace\relax
\makeatother

\lstset{
  captionpos=b,
  tabsize=2,
  numbers=left,
  numberstyle=\tiny,
  numbersep=5pt,
  breaklines=true,
  showstringspaces=true,
  basicstyle=\scriptsize\ttfamily,
  frame=none,
  emph={label},
  escapechar=| % Escape to LaTeX between |...|
}

\begin{document}

\setlength{\abovedisplayskip}{3pt}
\setlength{\belowdisplayskip}{2pt}

\conferenceinfo{WXYZ '05}{date, City.}
\copyrightyear{2005}
\copyrightdata{[to be supplied]}

\titlebanner{banner above paper title}        % These are ignored unless
\preprintfooter{short description of paper}   % 'preprint' option specified.

%\title{A Calculus for Speculative Non-determinism}
\title{Speculative Nondeterminism}
%\subtitle{Subtitle Text, if any}

\authorinfo{Xiao Jia \and Kenny Q. Zhu}
           {Shanghai Jiao Tong University}
           {\{xjia,kzhu\}@cs.sjtu.edu.cn}
\authorinfo{Joxan Jaffar \and Roland H.C. Yap}
           {National University of Singapore}
           {\{joxan,ryap\}@comp.nus.edu.sg}

\maketitle

\begin{abstract}
We propose a new programmable concurrency control framework called
speculative nondeterminism for real time,
``open'' and distributed agents. By open, we mean the agent programs
are independent and are not necessarily constrained to operate
in a particular fashion, and they may join the system at arbitrary times.
In this framework,
agent programs execute concurrently and affect each other through
a centralized store which represents shared resources.
%There is no direct communication among the agents.
%Because a sequential agent maybe blocked due to resource constraints
%in the store,
The framework allows the agent to speculate against the future by multiple
exclusive choices that encode different strategies to achieve its goals.
As the choices are exclusive, each choice from the same agent
executes in isolation from the other, however,
agents still interact with each other through the store.
The benefit of speculation is that unlike other concurrency frameworks,
the combinatorial-choice models more possibilities and
this improves the chances of successful outcomes in a system with interacting agents.
% The choices from the same agent are meant to be executed in
% isolation from each other because they may update the store in different ways.
% Only one successful choice becomes the eventual reality. When multiple
% agents each specifies some choices, the system creates
% many stores and thus runtime environments to represent the
% different combinations of choices. We argue that combinatorial choices
% improve the likelihood of successful program completion and
% thus improve the overall system throughput.
The framework also allows the agent to specify when and where
it wants to commit to a particular choice
and thus control the space of choices and reclaim valuable computation resources.
This paper gives the formal operational semantics of speculative nondeterminism,
and presents a prototype implementation of the framework along with some
preliminary evaluation results.
\end{abstract}

%\category{CR-number}{subcategory}{third-level}

%\terms
%term1, term2

\keywords
speculation, concurrency, nondeterminism, agents

\input{intro}

\input{overview}

\input{calculus}

%\input{analysis}
\input{experiment}

\input{related}

\input{conclusion}

%\acks
%
%Acknowledgments, if needed.

% We recommend abbrvnat bibliography style.

%{\renewcommand{\baselinestretch}{0.9}
%\small
\bibliographystyle{abbrvnat}
\bibliography{ocp,gcc}
%}

\appendix
\input{commits}

\end{document}
