\begin{abstract}
Image clustering is an important technique in 
web image search and retrieval.
Given a search term, most key-word based image search engines 
return images whose title or immediate surrounding text contains the search
term as a keyword. When a search term is ambiguous and means
different things, the results often come in a mixed bag
of different entities. Even the ``sort by subject'' feature offered by 
well-known search engines distinguishes images only by the different
historical query terms and not by the entity actually in the image.
% without meaningful ordering or grouping because
%it doesn't understand the semantics or recognize the objects in the images.
%This poses inconvenience for users who are looking for a particular
%entity without knowing the exact right term to search.
Existing image clustering techniques cannot distinguish images by the
entities because they classify images using either their low level
visual signals or the mere distribution of words in the text
context.
%None of these techniques
%works well because i) techniques for visual recognition of objects
%are still immature; ii) modeling text context by bag-of-words is insufficient
%for the understanding of the context; and iii) there is a
%disconnect between visual cues and the actual semantics of the image.
This paper proposes a novel framework that understands
the context and thus infers the most likely entity in the given
image by disambiguating the terms in the context
into the corresponding concepts from external knowledge
in a process called conceptualization.
%The framework also incorporates any type of visual signals to complement
%the text signals in a tri-stage clustering algorithm
%which produces better clustering results than state-of-the-art
%approaches.
The images can subsequently be clustered by the most likely associated
entities. This approach outperforms the best competing
image clustering techniques by 29.2\% in NMI score.
In addition, the framework automatically
annotates each cluster of images by its key entities which
allows users to quickly identify the images they want.
\end{abstract}
