\section{Limitations}
\label{sec:limitation}

Our work has some limitations that could be addressed in future research. 

\begin{itemize}
    \item Despite our best efforts in designing the prompt for the psychiatrist chatbot to align with the requirements specified by psychiatrists, the final human evaluation reveals that the full prompt (i.e., \texttt{D1}) does not outperform the results obtained by removing certain parts (i.e., \texttt{D2}, \texttt{D3}) from the prompt in terms of user experience. Although we may not achieve the optimal prompt design, our comprehensive exploration provides valuable insights into what constitutes an professional psychiatrist chatbot, which can serve as a foundation for future works in this domain.
   \item In this study, our focus is on the development and evaluation of psychiatrist and patient chatbots powered by LLMs, specifically targeting depressive disorder. However, it is important to note that in reality, individuals often experience multiple mental disorders concurrently, which introduces additional challenges. For psychiatrist chatbots, simultaneously diagnosing multiple mental disorders requires managing a broader range of possibilities. On the other hand, patient chatbots need to simulate a complex mixture of symptoms, which can be difficult to accurately replicate. We hope to scale our approach to encompass a wider range of mental disorders in the future.
% \item we only involve depression in this work, .... \KZ{This will not
% be a limitation if this paper is only about depression and we be explicit
% about that in the title. In fact this can be plus, cos we can say that
% what's done here for depression can be extended to other disorders.} 
\end{itemize}