%\documentclass[conference,letterpaper]{sig-alternate}
\documentclass[conference,letterpaper]{IEEEtran}
\usepackage{times,amsmath,epsfig,proof,url}
%\usepackage{algorithmic}
\usepackage{multicol,multirow}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{textcomp}
\usepackage{color}
%\usepackage[lined,algonl,ruled]{algorithm2e}
\usepackage{subfigure}
\usepackage{graphicx}
\newcommand{\tab}{\hspace*{2ex}}
\newcommand{\shrink}{\vspace*{-2ex}}
\newcommand{\cut}[1]{}
\newcommand{\KZ}[1]{\textcolor{red}{Kenny: #1}}
\newcommand{\secref}[1]{Section \ref{#1}}
\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\eqnref}[1]{Equation (\ref{#1})}
\newcommand{\tabref}[1]{Table \ref{#1}}
\newcommand{\exref}[1]{Example \ref{#1}}
\newtheorem{newproperty}{Property}
\newtheorem{newrule}{Rule}
\DeclareMathOperator{\w}{w}

\begin{document}
%\conferenceinfo{KDD'12,} {August 12--16, 2012, Beijing, China.}
%\CopyrightYear{2012}
%\crdata{978-1-4503-1462-6 /12/08}
%\clubpenalty=10000
%\widowpenalty = 10000
%\title{Automatic Extraction of Top-k Lists from the Web}
\title{MindDrifter: An Association Network of Wikipedia Concepts}
% \numberofauthors{3}
% \author{
% \alignauthor
% Kailang Jiang\\
%        \affaddr{Shanghai Jiao Tong University}\\
%        \affaddr{Shanghai, China}\\
%        \email{kailang@sjtu.edu.cn}
% \alignauthor
% Keyang Zhang\\
%        \affaddr{Shanghai Jiao Tong University}\\
%        \affaddr{Shanghai, China}\\
%        \email{keyang@sjtu.edu.cn}
% \and
% \alignauthor
% Kenny Q. Zhu\\
% %\titlenote{Kenny Q. Zhu was supported by NSFC Grants 61100050
% %and 61373031, and the Google Faculty Research Award.\vspace*{-5mm}}\\
%        \affaddr{Shanghai Jiao Tong University}\\
%        \affaddr{Shanghai, China}\\
%        \email{kzhu@cs.sjtu.edu.cn}
% }
\author{
{Keyang Zhang{\small $~^{1}$}, Jinyi Lu{\small $~^{2}$}, 
Kenny Q. Zhu{\small $~^{3}$}, Kailang Jiang{\small $~^{4}$}}%
% add some space between author names and affils
\vspace{1.6mm}\\
\fontsize{10}{10}\selectfont\itshape
Shanghai Jiao Tong University, Shanghai, China\\
\fontsize{9}{9}\selectfont\ttfamily\upshape
$~^{1}$keyang@sjtu.edu.cn, $~^{2}$lujysrs@gmail.com, $~^{3}$kzhu@cs.sjtu.edu.cn \\
$~^{4}$cqjiangkl@163.com\\
}
\maketitle

\begin{abstract}
Term relatedness computation finds many applications in information retrieval,
data mining and natural language processing. Existing approaches rely on the
frequency of co-occurrences between the two terms in large corpus.
This is not accurate when the corpus is not big enough or the co-occurrences
are sparse. In this paper, we propose to model term relatedness in concept
association network automatically harnessed from three of the largest online
encyclopedias in Chinese language. This model simulates how people's mind
drifts from one topic to another. We further present a Hidden Markov Model style
algorithm to compute the association probability between two concepts, as well
as how the two concepts are connected in a near-human mind drifting process.
Our evaluation shows that this model overcomes the co-occurrence sparseness
problem and outperforms existing algorithms in term relatedness computation.
Moreover, this model enables better recommendation systems, both content-based
and collaborative filtering, particularly during the ``cold start'' stage.
%Experiments show that this new algorithm performs better than common algorithms based on co-occurrence and previous algorithms modeling the association process.
\end{abstract}

%% A category with the (minimum) three required fields
% \category{H.3.3}{Information Storage and Retrieval}{Information Search and Retrieval}
% \category{H.2.8}{Database Management}{Database Applications}[Data Mining]
%%A category including the fourth, optional field follows...
%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
%
%\terms{Algorithm, Information extraction}


\begin{keywords}
Concept Association, Recommendation Systems, Term Similarity.
\end{keywords}

\input{intro}
%\input{problem}
\input{datasource}
\input{approach}
\input{eval}
\input{related}
\input{conclude}

%\bibliographystyle{abbrv}.
\bibliographystyle{IEEEtran}
%{\renewcommand{\baselinestretch}{0.9}
\bibliography{../bibs/probase,../bibs/asso}
%\bibliography{../bibs/asso}
%}
% sigproc.bib is the name of the Bibliography in this case
\end{document}
