%
% File acl2021.tex
%
%% Based on the style files for EMNLP 2020, which were
%% Based on the style files for ACL 2020, which were
%% Based on the style files for ACL 2018, NAACL 2018/19, which were
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2021}
%\hypersetup{draft}
\usepackage{times}
\usepackage{latexsym}
\renewcommand{\UrlFont}{\ttfamily\small}

\usepackage{url}

\usepackage{soul}
%\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage[ruled,vlined]{algorithm2e}
\urlstyle{same}

\usepackage{tablefootnote}
\usepackage{helvet}
\usepackage{courier}
\usepackage{color}
\usepackage{amsmath,amsfonts} %,amssymb,amsthm,amsopn}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{diagbox}
\usepackage{array}
\usepackage{multicol}
\usepackage{threeparttable}
\usepackage{epstopdf}
\usepackage{listings}
\usepackage{multirow}
\usepackage{subfigure}
\usepackage{makecell}

%\theoremstyle{definition}
\newtheorem{example}{Example}

\newcommand{\secref}[1]{Section \ref{#1}}
\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\eqnref}[1]{Eq. (\ref{#1})}
\newcommand{\tabref}[1]{Table \ref{#1}}
\newcommand{\exref}[1]{Example \ref{#1}}
\newcommand{\cut}[1]{}
\newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}

\newcommand{\KZ}[1]{\textcolor{blue}{Kenny: #1}}
\newcommand{\JQ}[1]{\textcolor{red}{JQ: #1}}
\newcommand{\YZ}[1]{\textcolor{red}{Yizhu: #1}}

% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

%\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{849} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\BibTeX{B\textsc{ib}\TeX}

\title{Abstractive Opinion Summarization by Weak-Supervision from
Semi-Structured Data}

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\}

\date{}

\begin{document}
\maketitle

\begin{abstract}
Abstractive opinion summarization of multiple reviews
 using deep learning techniques suffers from the lack 
of summaries for training data.
Previous dataset creation methods are based on
textual similarities between reviews.
In the summary thus created, some of its information may be
missing from its matching input reviews.
In this paper, 
we present a method to summarize opinions by
extracting semi-structured aspects and opinions from reviews
in advance. We create the synthetic training data by sampling 
a review as summary and taking the noisy version of 
semi-structured data as input together 
with aspect-variant guided encoder-decoder 
summarization models.
Experiments on the Yelp and Amazon datasets show 
favorable results of this approach over
previous state-of-the-art models.
\cut{%%%%%
we present a semi-structured review that consists of
opinion-aspect pairs extracted from the review
and sentences without opinion-aspect pairs.
%, extracted {\em opinion-aspect pairs} (OAs) of this review 
%and {\em other sentences} (OSs) without extracted OAs.
%that do not contain OAs. 
%Each product has an OAs group and an OSs group.
%\KZ{The following three sentences can be simplified and combined to
%one.}
We create the synthetic training data 
by sampling a review as summary and
generating the noisy version of semi-structured summary 
as semi-structured multiple reviews. 
We introduce variant aspect guided summarization models
for producing summaries from semi-structured multiple reviews.
%We design a data aggregation heuristics to sample a review as summary
%and generate noisy versions of semi-structured summary as input
%to simulate semi-structured form of actual multi-review .
%as input.
%which simulates the OAs and OSs of multi-review and summary during generation.
%We propose an aspect guided encoder-decoder model
%to generate summary from reconstructed semi-structured data.
%During test, the input of model is the extracted OAs and OSs of multi-review
%with opinion attention and context attention, 
}%%%%%%%
% in terms of automatic and manual evaluation metric.
\cut{%%%%% submitted abstract
	Abstractive opinion summarization using deep learning techniques lacks training data. Previous dataset creation methods always select summary and its multi-review by the textual similarity between reviews.
	However, summary and its multi-review in these datasets are inconsistent in aspect and opinion.
	In this paper, we represent a review by extracted opinion-aspect pairs (OAs) of this review and other sentences (OSs) without extracted OAs. We design a data aggregation heuristics to sample a review as summary and generate noisy versions of OAs and OSs as input to simulate them in actual multi-review. We propose an aspect guided encoder-decoder model to generate summary from selected OAs and OSs. The results shows that our model outperforms the state-of-the-art models on Yelp and Amazon.
}%%%%
\end{abstract}



\input{intro}
\input{approach}
\input{eval}
\input{related} 
\input{conclude}
\bibliographystyle{acl_natbib}
\bibliography{opinionsum}

%\appendix
\end{document}

