\begin{abstract}
An ad hoc data source is any semi-structured, non-standard data source.  
The format of such data sources is often evolving and frequently 
lacking documentation.
Consequently, off-the-shelf tools for processing such data often
do not exist, forcing analysts to develop their own tools, a
costly and time-consuming process.
In this paper, we present an incremental algorithm that automatically
infers the format of large-scale data sources. From the resulting format
descriptions, we can generate a suite of data processing tools
automatically. The system can handle large-scale or streaming 
data sources whose formats evolve over time.  
Furthermore, it allows analysts to modify inferred
descriptions as desired and incorporates those changes in 
future revisions.
\footnote{
This work was partially supported by NSFC Grants No. 61033002 and 61100050
and by NSF grant CCF-1016937. Any opinions, findings, and recommendations
expressed in this material are those of the authors and do not
necessarily reflect the views of the NSFC or NSF.
The views expressed are those of the authors and do not reflect the official policy or position of the Department of Defense or the U.S. Government.  The views, opinions, and/or findings contained in this article/presentation are those of the author/presenter and should not be interpreted as representing the official views or policies, either expressed or implied, of the Defense Advanced Research Projects Agency or the Department of Defense.   Distribution Statement ``A'' (Approved for Public Release, Distribution Unlimited).
}
\end{abstract}
