% This must be in the first 5 lines to tell arXiv to use pdfLaTeX, which is strongly recommended.
\pdfoutput=1
% In particular, the hyperref package requires pdfLaTeX in order to break URLs across lines.

\documentclass[11pt]{article}

% Remove the "review" option to generate the final version.
\usepackage{ACL2023}

% Standard package includes
\usepackage{times}
\usepackage{latexsym}

% For proper rendering and hyphenation of words containing Latin characters (including in bib files)
\usepackage[T1]{fontenc}
% For Vietnamese characters
% \usepackage[T5]{fontenc}
% See https://www.latex-project.org/help/documentation/encguide.pdf for other character sets

% This assumes your files are encoded as UTF8
\usepackage[utf8]{inputenc}

% This is not strictly necessary, and may be commented out.
% However, it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

% This is also not strictly necessary, and may be commented out.
% However, it will improve the aesthetics of text in
% the typewriter font.
\usepackage{inconsolata}

\usepackage{amssymb}% http://ctan.org/pkg/amssymb
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\usepackage{makecell}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{subfigure}
\usepackage[normalem]{ulem}
\useunder{\uline}{\ul}{}

\newcommand{\secref}[1]{Sec. \ref{#1}}
\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\eqnref}[1]{Eq. (\ref{#1})}
\newcommand{\tabref}[1]{Table \ref{#1}}
\newcommand{\exref}[1]{Example \ref{#1}}
\newcommand{\KZ}[1]{\textcolor{blue}{(Kenny: #1})}
\newcommand{\ZL}[1]{\textcolor{red}{(Zhiling: #1})}
\newcommand{\MY}[1]{\textcolor{green}{(Mengyue: #1})}

% If the title and author information does not fit in the area allocated, uncomment the following
%
%\setlength\titlebox{<dim>}
%
% and set <dim> to something 5cm or larger.

\title{Semantic Space Grounded Weighted Decoding for Multi-Attribute 
Controllable Dialogue Generation}

% Author information can be set in various styles:
% For several authors from the same institution:
% \author{Author 1 \and ... \and Author n \\
%         Address line \\ ... \\ Address line}
% if the names do not fit well on one line use
%         Author 1 \\ {\bf Author 2} \\ ... \\ {\bf Author n} \\
% For authors from different institutions:
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \And  ... \And
%         Author n \\ Address line \\ ... \\ Address line}
% To start a seperate ``row'' of authors use \AND, as in
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \AND
%         Author 2 \\ Address line \\ ... \\ Address line \And
%         Author 3 \\ Address line \\ ... \\ Address line}

\author{Zhiling Zhang \and Mengyue Wu\thanks{~~Corresponding Authors. } \and Kenny Q. Zhu$^*$\\
Shanghai Jiao Tong University \\
Shanghai, China\\
\texttt{\{blmoistawinde, mengyuewu\}@sjtu.edu.cn, kzhu@cs.sjtu.edu.cn} }

\begin{document}
\maketitle
\begin{abstract}
Controlling chatbot utterance generation with multiple attributes such as 
personalities, emotions and dialogue acts is a practically useful but 
under-studied problem.
We propose a novel controllable generation framework called DASC 
that possesses strong controllability with weighted decoding paradigm, 
while improving generation quality with the grounding in an 
attribute semantics space. Generation with multiple attributes is then 
intuitively implemented with an interpolation of multiple attribute embeddings. 
Experiments show that DASC can achieve state-of-the-art control accuracy 
in 3-aspect controllable generation tasks while also producing interesting and 
reasonably sensible responses, even if in an out-of-distribution robustness 
test. Visualization of the meaningful representations learned in the 
attribute semantic space also supports its effectiveness.\footnote{Code and data at \url{https://github.com/blmoistawinde/DASC}.}
\end{abstract}

\input{intro.tex}
\input{related.tex}
\input{method.tex}
\input{experiment.tex}
\input{conclusion.tex}
\input{limitation.tex}
\input{ethics.tex}
% \input{ack.tex}

% Entries for the entire Anthology, followed by custom entries
\bibliography{custom}
\bibliographystyle{acl_natbib}

\input{appendix.tex}

\end{document}
