\section{Related Work}

Controllable generation has gained wide research interest recently. PPLM \citep{dathathri2019plug} proposed a plug-and-play framework to control the generation with an extra attribute classifier, but it requires costly gradient updates. Later research progress can be roughly divided into 3 categories. \textit{Reranking} methods leverage attribute classifiers to either simply rank the full generation candidates (adopted in many mature systems like LaMDA \citep{thoppilan2022lamda}), or partial generations for the guidance of future outputs \citep{yang2021fudge}. \textit{Integrated} methods integrate attribute-related trainable parameters into the generation model for finetuning, such as discrete control codes \citep{keskar2019ctrl} or continuous prompt prefix \citep{qian2022controllable}. \textit{Weighted Decoding} methods leverage token-level attribute classifiers to guide each decoding step. For example, \citet{krause2021gedi} and \citet{liu2021dexperts} utilized one/two additional class conditional language models to provide the attribute discrimination. Director \citep{arora2022director} integrates the attribute classifier as simple linear layers on top of LM hidden states, so that it exhibited efficient and effective performance in single-attribute control.  

Multi-attribute controllable generation is relatively under-explored now. \citet{lin2021plug} proposed to extend weighted decoding for the multi-attribute case with the simple product of multiple attribute conditional language models. \citet{gu2022distributional} proposed a VAE-based method combined with an intersection-searching algorithm for multi-aspect controllable generation, but their method cannot simply apply to conditional generation tasks like dialogue generation. 
% \citet{mireshghallah2022mix} proposed an energy-based controllable generation method that can combines multiple controls, but are mainly suitable for fixed-length generation. 
% \KZ{If they have already published to ArXiv before the release of
% our paper, we can't say we are concurrent to them: Concurrent to our work,} 

Controllable generation techniques are especially important in dialogue systems and the applications of several controlling aspects have been studied. For example, we may condition the generation with dialogue acts for the genuine reflection of the desired behavior \citep{wen2015semantically}, add emotions in the response to enhance the expressiveness of the bot \citep{zhou2018emotional}, and also impose personal profiles like gender \citep{su2020stylistic} and persona \citep{zhang2018personalizing} to establish a human-like companion. Most works separately add control on a single aspect, and some pioneering works have started to explore the composition of these attribute controls \citep{chen2022cped}. 
% \KZ{What's the difference between Chen'22 and Gu'22, and ours?} 
% \ZL{Chen'22 is mainly a dataset paper, which tried some basic methods.}
