% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{cite}
\usepackage{multirow}
\usepackage{newfloat}
\usepackage{listings}
\usepackage{subcaption}
\usepackage{color}
\usepackage{amsmath}
\newcommand{\KZ}[1]{\textcolor{blue}{Kenny: #1}}
\usepackage{verbatim}
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%
\begin{document}
%
\title{Predicting Click Popularity on Wikipedia Hyperlinks by Visual Features}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
As an omnipresent feature on Wikipedia, hypertext links are crucial means for users to retrieve information. However, the sub-optimal organization of website structure may degrade the flow of information. Having a better understanding of the effect of various factors on click popularity can be instructive for the amelioration of website structure. In this paper, we study click popularity prediction on hypertext links. We formulate the problem as the ranking of links according to Click Through Rate (CTR) and utilize Learning to Rank (L2R) algorithms to solve it. We observe the significant impact of visual factors on the CTR of hyperlinks and introduce new visual features to the L2R model. To validate the effectiveness of the proposed visual features, we conduct experiments on the Wikipedia clickstream dataset. Results have shown that adding visual features can significantly improve the ranking performance across ten different categories. We further conduct ablation tests to quantitively evaluate the impact of each visual feature.
\keywords{World Wide Web \and Click models \and Human-Computer Interaction}
\end{abstract}

\input{intro}
\input{formulation}
\input{approach}
\input{experiments}
\input{related}
\input{conclude}

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{mybibliography}
\end{document}
