%!TEX program = xelatex
\documentclass[letterpaper]{article}

\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}

\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}

\usepackage{rotating}
\usepackage{color}
\usepackage{epsfig,subcaption, multicol,multirow}
\usepackage{epstopdf}
\usepackage{amsmath,algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{url}
\usepackage{lingmacros,framed}

\graphicspath{{figures/}}
\newcommand{\KZ}[1]{\textcolor{blue}{Kenny: #1}}
\newcommand{\ZY}[1]{\textcolor{red}{J: #1}}
\newcommand{\tabref}[1]{Table \ref{#1}}
\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\secref}[1]{Section \ref{#1}}
\newcommand{\eqnref}[1]{Equation (\ref{#1})}
\newcommand{\cut}[1]{}
\newtheorem{example}{Example}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

\pdfinfo{
/Title (Commonsense Causal Reasoning between Short Texts)
/Author (Zhiyi Luo,YuChen Sha,Kenny Q. Zhu,Seung-won Hwang,Zhongyuan Wang)}

\setcounter{secnumdepth}{2}

\begin{document}
\title{Commonsense Causal Reasoning between Short Texts}

\author{
\AND
Zhiyi Luo{\small $~^{1}$}~~~Yuchen Sha{\small $~^{1}$}~~~Kenny Q. Zhu{\small $~^{1}$}~~~Seung-won Hwang{\small $~^{2}$}~~~Zhongyuan Wang{\small $~^{3}$}\\
{\small $^{1}$}Shanghai Jiao Tong University, Shanghai, China\\
\{jessherlock,sycbelief\}@sjtu.edu.cn,kzhu@cs.sjtu.edu.cn\\
{\small $^{2}$}Yonsei University, Seoul, Republic of Korea\\
seungwonh@yonsei.ac.kr\\
{\small $^{3}$}Microsoft Research Asia, Beijing, China\\
zhy.wang@microsoft.com
}

\maketitle
\begin{abstract}
Commonsense causal reasoning is the process of capturing and understanding
the causal dependencies amongst events and actions.
Such events and actions can be expressed in terms, phrases or
sentences in natural language text.
Therefore, one possible way of obtaining causal knowledge is by extracting
causal relations between terms or phrases from a large text corpus.
However, causal relations in text are sparse, ambiguous, and sometimes implicit,
and thus difficult to obtain.
This paper attacks the problem of commonsense causality reasoning between short
texts (phrases and sentences) using a data driven approach.
We propose a framework that automatically harvests a network of
causal-effect terms from a large web corpus.
Backed by this network, we propose a novel and effective metric to properly
model the causality strength between terms. We show these signals
can be aggregated for causality reasonings between
short texts, including sentences and phrases.
In particular, our approach outperforms all previously
reported results in the standard SEMEVAL COPA task by substantial margins.

\end{abstract}

\input{intro}
\input{approach}
\input{eval}
\input{related}
\input{conclusion}

\bibliographystyle{aaai}
\bibliography{causal}

\end{document}
