\documentclass[conference]{IEEEtran}

\usepackage{url,color}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amsmath}
\interdisplaylinepenalty=2500
\usepackage{array}
\usepackage{threeparttable}
\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\tabref}[1]{Table \ref{#1}}

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
\usepackage{stfloats}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
\newcommand{\KZ}[1]{\textcolor{blue}{Kenny: #1}}
\newcommand{\XY}[1]{\textcolor{red}{Xinyu: #1}}
\newcommand{\YF}[1]{\textcolor{blue}{Yifan: #1}}

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Action Conceptualization: Mining isA Relation between Actions and Nouns}

\author{\IEEEauthorblockN{Xinyu Hua\IEEEauthorrefmark{1},
Yifan Wang\IEEEauthorrefmark{1},
Yu Gong\IEEEauthorrefmark{1} and
Kenny Zhu\IEEEauthorrefmark{1}}

\IEEEauthorblockA{\IEEEauthorrefmark{1}Department of Computer Science and Engineering\\
Shanghai Jiao Tong University\\
Email: \{huaxinyu, racheter, kenzhu\}@sjtu.edu.cn}}


% make the title area
\maketitle

\begin{abstract}
This paper presents a retrieval based method to achieve action conceptualization,
 which is the process of abstracting action concepts into noun concepts. Action
 concepts are predicate together with argument concepts such as for subject and
 object. For example the noun concept ``acquisition'' would be a good abstraction
 of the action concept ``company buy company''.
 Our work is based on the assumption that the word used in news title are
 usually generalization or abstraction of the event discussed in the news content.
 We use online textual news as our corpus, and build a tripartite graph to model
 the relation between noun, news and action. We subsequently build an action-noun map
 by mining relatedness between noun and action. This work can be useful in various
 domains. As a showcase we build a news search engine with semantic search enabled
 by our conceptualization result. On a human labeled evaluation dataset our method
 outperforms a topic model baseline and a TF-IDF baseline.
\end{abstract}




% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle



\input{tex/intro}
\input{tex/related}
\input{tex/problem}
\input{tex/approach}
\input{tex/system}
\input{tex/eval}



\section{Conclusion}
The conclusion goes here.


\section*{Acknowledgment}
The authors would like to thank...

\bibliographystyle{IEEEtran}
\bibliography{icdm}

\end{document}
