\def\year{2017}\relax
%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{aaai17}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{color}
\usepackage{amsmath,amsfonts,amssymb,amsthm,amsopn}
\usepackage{times}
\usepackage{url}
\usepackage{color}
\usepackage{latexsym}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{diagbox}
\usepackage{array}
\usepackage{multicol}
\usepackage{threeparttable}
\usepackage{epstopdf}
\usepackage{listings}
\usepackage{multirow}

%code environment
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=Java,
  aboveskip=1.5mm,
  belowskip=1.5mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\tiny\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\tiny\color{blue},
  commentstyle=\tiny\color{dkgreen},
  stringstyle=\tiny\color{mauve},
  breaklines=true,
  breakatwhitespace=true
  tabsize=3
}

\newcommand{\KZ}[1]{\textcolor{blue}{Kenny: #1}}

\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Automatic Inference of Semantic Tag Phrases for 
Source Code Repositories)
/Author (Put All Your Authors Here, Separated by Commas)}
\setcounter{secnumdepth}{2}
 \begin{document}
% The file aaai.sty is the style file for AAAI Press
% proceedings, working notes, and technical reports.
%
\title{Automatic Inference of Semantic Tag Phrases for Source Code Repositories}
%\author{Yuding Liang $^{1}$ and Hongfei Hu $^{2}$ and Kenny Q. Zhu $^{3}$\\
%Shanghai Jiao Tong University, Shanghai, China\\
%$^{1}$liangyuding@sjtu.edu.cn, $^{2}$eich2ef@gmail.com, $^{3}$kzhu@cs.sjtu.edu.cn \\
%}
\maketitle
\begin{abstract}
We present a framework to automatically tag methods in a large code repository 
with natural language keywords. This helps people better understand large-scale,
real-world code and practically enables both keyword search and code search in
these large repositories.
The framework is based on a previous supervised learning model which predicts
a natural language description from a small code snippet and vice versa. 
However, it is enhanced with identifier semantics and function call 
information. Our experiments on ten Github repositories show that 
the new framework performs significantly better than the previous one 
in tag accuracy without penalty in time complexity.
\end{abstract}

\input{tex/intro}
\input{tex/preliminary}
\input{tex/model}
\input{tex/eval}
\input{tex/related}

\section{Conclusion}
We present an improved model to automatically infer meaningful tags for
potentially complex methods in large code repositories. This model 
combines the structural information of the code such as inter-method 
invocation information, as well as semantic information such as the English
content words in the identifiers and user comments. The model achieves better
prediction accuracies than known methods and baselines, with very reasonble
execution time cost.

\section*{Acknowledgment}
We thank Miltiadis Allamanis for his generous help in reproducing his
results on our dataset.


\bibliographystyle{aaai}
\bibliography{reference}
\end{document}
