\def\year{2017}\relax
\documentclass[letterpaper]{article}
\usepackage{aaai17}
\usepackage{times}
\usepackage{graphicx}
\usepackage{helvet}
\usepackage{subcaption}
\usepackage{courier}
\usepackage{url,color}
\usepackage{amsmath,amsfonts}
\usepackage{threeparttable}
\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\tabref}[1]{Table \ref{#1}}
\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}


\newcommand{\KZ}[1]{\textcolor{blue}{Kenny: #1}}
\newcommand{\XY}[1]{\textcolor{red}{Xinyu: #1}}
\newcommand{\YF}[1]{\textcolor{blue}{Yifan: #1}}

\pdfinfo{
/Title (Insert Your Title Here)
/Author (Put All Your Authors Here, Separated by Commas)}
\setcounter{secnumdepth}{0}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Enhanced web search by action conceptualization}
%\author{
%Xinyu Hua, Yifan Wang, Kenny Zhu\\
%}

\maketitle
\begin{abstract}
  This paper presents a retrieval based method to achieve action conceptualization,
  which is the process of abstracting action concepts into noun concepts. Action
  concepts are predicate together with argument concepts such as for subject and
  object. For example the noun concept ``acquisition'' would be a good abstraction
  of the action concept ``company buy company''.
  Our work is based on the assumption that the word used in news title are
  usually generalization or abstraction of the event discussed in the news content.
  We use online textual news as our corpus, and build a tripartite graph to model
  the relation between noun, news and action. We subsequently build an action-noun map
  by mining relatedness between noun and action. This work can be useful in various
  domains. As a showcase we build a news search engine with semantic search enabled
  by our conceptualization result. On a human labeled evaluation dataset our method
  outperforms a topic model baseline and a TF-IDF baseline.
\end{abstract}

\input{tex/intro}
\input{tex/data}
\input{tex/approach}
\input{tex/system}
\input{tex/eval}
\input{tex/related}
\input{tex/conclusion}

\nocite{*}
\bibliographystyle{aaai}
\bibliography{actionplus}

\end{document}
