\setlength\parindent{2em}
\begin{abstract}
	Apache Spark分布式数据处理系统及其衍生的生态系统让大规模数据的处理变得更加高效。
	尽管现在已经有了许多统计模型和推断算法库，但是专业用户需要理解Spark系统的
	底层细节，从而很难开发自己的模型。概率编程语言的出现让专业用户可以用很简洁的
	程序语言来描述复杂的概率统计模型，概率编程框架可以自动地生成统计推断算法实现，
	回答用户对模型的各种概率查询。我们提出了一个基于Spark的分布式概率编程框架，把
	高效的分布式系统和概率编程相结合，使得用户可以很容易地定义新的贝叶斯模型，并
	由InferSpark生成出能利用Spark大数据处理能力的贝叶斯推断代码。尽管InferSpark的
	初步实现已经能在大规模数据上进行贝叶斯推断，而以往最先进的概率编程框架不能在这样
	大规模的数据上进行贝叶斯推断，但是InferSpark由于使用了Spark内置的图处理框架GraphX，
	性能不理想。我们找到了导致性能问题的原因，并以此设计了一个新的图处理框架
	InferSpark-Graph来解决性能问题。实验显示了InferSpark-Graph极大地提高了InferSpark
	的性能。

	\keywords{分布式系统，贝叶斯推断，概率编程}
\end{abstract}
\setlength\parindent{0pt}

\begin{englishabstract}
	
	The Apache Spark software stack has enabled fast large-scale data processing.
	Despite a rich library of statistical models and inference algorithms, it
	does not give domain users the ability to develop their own models. The
	emergence of probabilistic programming languages has shown the promise of
	developing sophisticated probabilistic models through succinct and
	declarative modeling. These frameworks have the potential of automatically
	generating inference algorithm implementations for the customized models and
	answering various statistical queries about the models.  We propose
	InferSpark, a probabilistic programming framework on top of Apache Spark,
	which unites the two directions to produce a declarative big data Bayesian
	inference framework. Efficient Bayesian inference can be easily implemented
	in this framework and the inference process can leverage the distributed main
	memory processing power of Spark.  The preliminary implementation of
	InferSpark enables Bayesian inference on large-scale data that was impossible
	using the state-of-the-art probabilistic programming frameworks, but it
	suffers from poor performance. We identify the cause of the
	poor performance as the limitations of GraphX, the built-in graph processing
	framework of Spark. We design a new graph processing framework,
	InferSpark-Graph, to overcome the problem. Empirical evaluation shows it
	greatly improves the performance of InferSpark.

	\englishkeywords{Distributed system, Bayesian inference, Probabilistic programming}
\end{englishabstract}
