\documentclass{sig-alternate}
\usepackage{url,color}
\usepackage{subfigure}
\usepackage{alltt}
\usepackage{epsfig}
\usepackage{epstopdf}
\usepackage{enumerate}
\usepackage{multirow}
\usepackage{fancyvrb}
%\usepackage{slashbox}
%\renewcommand{\rmdefault}{ptm}
%\usepackage{mathptmx}
\newcommand\Hlight[1]{\textcolor[rgb]{0,0,1}{\textbf{#1}}}
\newcommand\Vlight[1]{\textcolor[rgb]{1,0,1}{\textbf{#1}}}
%\newcommand{\KZ}[1]{\textcolor{blue}{[KZ:#1]}}
\begin{document}
\numberwithin{equation}{section}
% first the title is needed
\title{A Verilog Precompiler for Interactive Optimization of IP Core Design}
%%%%
\maketitle
\begin{abstract}
SV+ is an interactive compiler that makes circuit designer do trade-offs 
between resource consuming and time cost easily, without rewriting the 
source code. A set of succinct SV+ syntaxes are proposed in this work. 
They can be used to embed with Verilog to describe the 
re-configurable parts of a circuit. Users have opportunity to select 
optimization options during the compiling process. The compiler 
generates Verilog RTL codes, depends on these choices. And for different
 optimization choices, the circuits vary in architectures besides 
in time and resource. SV+ syntaxes can describe reconfigurable circuit
 structures in mathematical or functional level, so designers are 
liberated from putting much effort on concerning about module scheduling
 and wire connection. Unlike other circuit compilers, for example DFT 
compiler\cite{GNordin:FFT}, which work on single kind of algorithm,
 SV+ syntaxes can be used in a range of Verilog programs as long as 
there are any reconfigurable components available in the design.
\end{abstract}

\input{intro}
\input{syntax}
\input{compiler}
\input{examples}
\input{experiments}
\input{relatedwork}
\input{conclusion}
\bibliographystyle{abbrv}
\bibliography{richip}
\newpage
\appendix
\input{appendix}
\end{document}
