\section{Related Work}\label{sec:relatedwork}
SV+ is targeted as a Verilog Precompiler to generate readable code with state machines for sequential circuit.
There has been recent work related to SV+.

A lot of pople are working on high level systhsis (HLS)\cite{HLS:intro}\cite{ChipDesign:HLS}\cite{SPARK} to make circuit design easier and more efficient. Paper\cite{Survey:HLS} has talked much on development in HLS whose main idea is translating descriptions in high level languages into HDLs.  
Many C-like digital hardware description languages have been proposed. The authors in\cite{HLSofDigitalSystems} analyzed two challenges of synthesising hardware from C-like language, concurrency and timing control. For example, C2Verilog\cite{C2Verilog}, a full-featured ANSI C to synthesizable RTL Verilog compiler, relys on the complier completely to identify parallelism, uses complex rules to insert cycles and imposes outside timing constraints. Likewise, SV+ generates sequential circuit, however, applys state machine to circuit. Furthermore, we can configure the state machine with not only the ALU units and memory ports but also the concurrency (except the basic configuration such as word size).

SPIRAL\cite{CodeG:Spiral}\cite{SpiralProject} is a code generating system for DSP transforms. It autonomously implements algorithm, optimizes at alogrithmic level, and creates the best implementation in combinational circuit for platform-specific features. Furthermore, SPIRAL generates customized codes to user-specified cost/performance tradeoffs. Even though SPIRAL provides some tradeoff choices to user, its code is relatively fixed, which sometimes dose not meet user's design requirement and at the same time the code is sometimes lacking of readability. SV+ provides a precompiler to generate configurable and reusable circuit macros to meet user's demands and readable code for user to modify if necessary.

Differing from those mentioned above, Bluespec itself is a hardware description language (HDL). It is translated into intermediate TRS and then into Verilog RTL or a cycle-accurate C-simulation. Like Verilog, Bluespec consists of circuit modules of statements, rules and interfaces. Nevertheless, Bluespec presents a high-level description for how to apply the rules of a design. It is translated rules descriptions into hardware descriptions in a fixed way without configurability.


