\def\year{2019}\relax
%File: formatting-instruction.tex
\documentclass[letterpaper]{article} %DO NOT CHANGE THIS
\usepackage{aaai19}  %Required
\usepackage{times}  %Required
\usepackage{helvet}  %Required
\usepackage{courier}  %Required
\usepackage{url}  %Required
\usepackage{graphicx}  %Required
\frenchspacing  %Required
\setlength{\pdfpagewidth}{8.5in}  %Required
\setlength{\pdfpageheight}{11in}  %Required


\usepackage{latexsym}
\usepackage{makecell}
\usepackage{CJKutf8}
\usepackage{epsfig}
\usepackage{algorithm, algpseudocode}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{color}
\usepackage{subfigure}
\usepackage{url}
\usepackage{mathrsfs}
\usepackage{amsmath}
\usepackage[small]{caption}
\usepackage{amssymb}



\newcommand\BibTeX{B{\sc ib}\TeX}
\newcommand{\secref}[1]{Section \ref{#1}}
\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\eqnref}[1]{Eq. (\ref{#1})}
\newcommand{\exref}[1]{Example \ref{#1}}
\newcommand{\algoref}[1]{Algorithm \ref{#1}}
\newcommand{\tabref}[1]{Table \ref{#1}}
\newcommand{\bi}[1]{\textbf{\textit{#1}}}

\newcommand{\yu}[1]{{\bf \color{red} [[Yu says ``#1'']]}}
\newcommand{\lu}[1]{{\bf \color{blue} [[Lu says ``#1'']]}}
\newcommand{\KZ}[1]{{\bf \color{red} [[Kenny says ``#1'']]}}

\newcommand{\lstm}{\operatornamewithlimits{LSTM}}
\newcommand{\bilstm}{\operatornamewithlimits{BiLSTM}}
\newcommand{\argmax}{\operatornamewithlimits{argmax}}
\newcommand{\seg}{\operatornamewithlimits{seg\_tag}}
\newcommand{\ner}{\operatornamewithlimits{ne\_tag}}
\newcommand{\slot}{\operatornamewithlimits{slot\_fill}}
\newcommand{\batch}{\operatornamewithlimits{Batch}}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proof}{Proof}

%PDF Info Is Required:
%\pdfinfo{
%	/Title (2019 Formatting Instructions for Authors Using LaTeX)
%	/Author (AAAI Press Staff)}
\setcounter{secnumdepth}{2}

\begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{A Multi-task Selected Learning Approach for Solving \\ 3D Flexible Bin Packing Problem}
%\author{AAAI Press\\
%Association for the Advancement of Artificial Intelligence\\
%2275 East Bayshore Road, Suite 160\\
%Palo Alto, California 94303\\
%}

\maketitle
\begin{abstract}
	A 3D flexible bin packing problem (FBPP) arises from the process of warehouse packing in cross-border e-commerce. The objective is to find a way to 
place a set of cuboid-shaped items into a flexible bin orthogonally,\KZ{Not sure
what you mean by orthogonally..} 
such that the surface area of the stack is minimized. In particular, $5\%$ of the tens of millions of packages are prepared using plastic wrapping as outer packaging every day, which bring pressure on the plastic stack surface minimization. 
It is a grave challenge to find the optimal solution within very limited 
computational budget because the problem is proven to be NP-hard. However, existing heuristic methods for classic 3D bin packing could not find a good enough solution and the development of efficient heuristic algorithms for the practical problems is costly. %This problem is based on the fact that there is no fixed-sized bin in 
%many real business scenarios and the cost of a bin is proportional to 
%its surface area. Based on previous research on 3D BPP, 
%the surface area is determined by the sequence, spatial locations and 
%orientations of items. It is a new NP-hard combinatorial optimization problem on unfixed-sized bin packing,
In this paper, we propose a multi-task 
framework based on Selected Learning to learn a heuristic-like policy that generates the sequence and orientations of items to be packed simultaneously. A large scale real-world order dataset from e-commerce and logistic platform is used to validate the effectiveness of the proposed method in reducing packing materials by comparisons to other baseline methods. Numerical results also demonstrate that the proposed method significantly outperforms the well-designed greedy algorithm by 
a substantial gain of $7.52\%$. 
%Through comprehensive experiments on a large scale real-world order dataset from e-commerce and logistic platform , the  method significantly outperforms the well-designed greedy algorithm by a substantial gain of $7.52\%$  in reducing packing materials.
\KZ{Please proofread the paper very very carefully again. I find many typos
and grammatical errors.}
\end{abstract}


\begin{CJK}{UTF8}{gbsn}
	
	\input{intro}
	
	\input{problem}
	
	%\input{data}
	
	\input{approach}
	
	\input{experiment}
	
	\input{related}
	
	\input{conclusion}
	
\end{CJK}

\bibliographystyle{aaai}

\bibliography{ref}
\end{document}
