%
% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf]{acmart}

%
% defining the \BibTeX command - from Oren Patashnik's original BibTeX documentation.
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

% Rights management information. 
% This information is sent to you when you complete the rights form.
% These commands have SAMPLE values in them; it is your responsibility as an author to replace
% the commands and values with those provided to you when you complete the rights form.
%
% These commands are for a PROCEEDINGS abstract or paper.
\copyrightyear{2018}
\acmYear{2018}
\setcopyright{acmlicensed}
\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
\acmPrice{15.00}
\acmDOI{10.1145/1122445.1122456}
\acmISBN{978-1-4503-9999-9/18/06}

\usepackage{times}
\usepackage{url}
\usepackage{latexsym}

\usepackage{soul}
\usepackage{algorithm}
\usepackage{algorithmic}
\urlstyle{same}

\usepackage{helvet}
\usepackage{courier}
\usepackage{color}
\usepackage{amsmath,amsfonts,amssymb,amsthm,amsopn}
\usepackage{color}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{diagbox}
\usepackage{array}
\usepackage{multicol}
\usepackage{threeparttable}
\usepackage{epstopdf}
\usepackage{listings}
\usepackage{multirow}
\usepackage{subfigure}
\theoremstyle{definition}
\newtheorem{example}{Example}

\newcommand{\secref}[1]{Section \ref{#1}}
\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\eqnref}[1]{Eq. (\ref{#1})}
\newcommand{\tabref}[1]{Table \ref{#1}}
\newcommand{\exref}[1]{Example \ref{#1}}
\newcommand{\cut}[1]{}
\newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}

\newcommand{\KZ}[1]{\textcolor{blue}{Kenny: #1}}
\newcommand{\ZY}[1]{\textcolor{red}{Zhiyi: #1}}
\newcommand{\YZ}[1]{\textcolor{red}{Yizhu: #1}}
\newcommand{\SN}[1]{\textcolor{magenta}{Sandy: #1}}

\begin{document}

\title{Causal Attention Fusion for Commonsense Causalities Generation}

\author{Ben Trovato}
\authornote{Both authors contributed equally to this research.}
\email{trovato@corporation.com}
\orcid{1234-5678-9012}
\author{G.K.M. Tobin}
\authornotemark[1]
\email{webmaster@marysville-ohio.com}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \streetaddress{P.O. Box 1212}
  \city{Dublin}
  \state{Ohio}
  \postcode{43017-6221}
}

\author{Lars Th{\o}rv{\"a}ld}
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
  \city{Hekla}
  \country{Iceland}}
\email{larst@affiliation.org}

\author{Valerie B\'eranger}
\affiliation{%
  \institution{Inria Paris-Rocquencourt}
  \city{Rocquencourt}
  \country{France}
}

\author{Aparna Patel}
\affiliation{%
 \institution{Rajiv Gandhi University}
 \streetaddress{Rono-Hills}
 \city{Doimukh}
 \state{Arunachal Pradesh}
 \country{India}}
 
\author{Huifen Chan}
\affiliation{%
  \institution{Tsinghua University}
  \streetaddress{30 Shuangqing Rd}
  \city{Haidian Qu}
  \state{Beijing Shi}
  \country{China}}

\author{Charles Palmer}
\affiliation{%
  \institution{Palmer Research Laboratories}
  \streetaddress{8600 Datapoint Drive}
  \city{San Antonio}
  \state{Texas}
  \postcode{78229}}
\email{cpalmer@prl.com}

\author{John Smith}
\affiliation{\institution{The Th{\o}rv{\"a}ld Group}}
\email{jsmith@affiliation.org}

\author{Julius P. Kumquat}
\affiliation{\institution{The Kumquat Consortium}}
\email{jpkumquat@consortium.net}

\begin{abstract}
Commonsense causal reasoning is the process of understanding
the causal dependency between 
common events or actions. 
Previously, the commonsense causal reasoning
was considered as a selection problem.
However, we cannot get enough candidates
and need more flexible causes (or effects) in many scenarios,
such as causal-based QA problem.
Thus, the ability to generate causes (or effects) is an important problem. 
In this paper, we propose an approach 
to solve the commonsense causalities generation problem 
by fusing causality strength from CausalNet and attention in convolutional sequence to sequence model.
The results show that this approach generate proper causes (or effects), 
and outperforms the baselines in terms of BLEU score, causality strength and Accuracy.
\end{abstract}

% Keywords. The author(s) should pick words that accurately describe the work being
% presented. Separate the keywords with commas.
\keywords{commonsense causal reasoning, causality extraction, causality generation, convolutional sequence to sequence learning, neural networks}

%
% This command processes the author and affiliation and title information and builds
% the first part of the formatted document.
\maketitle

\input{intro}
\input{approach}
\input{eval}
\input{related}
\input{conclusion}

% The acknowledgments section is defined using the "acks" environment (and NOT an unnumbered section). This ensures
% the proper identification of the section in the article metadata, and the consistent spelling of the heading.
\begin{acks}
To Robert, for the bagels and explaining CMYK and color spaces.
\end{acks}

%
% The next two lines define the bibliography style to be used, and the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{emnlp-ijcnlp-2019}

% 
% If your work has an appendix, this is the place to put it.
%\appendix

\end{document}
