\documentclass[preprint]{sigplanconf}
\input{packages}
\input{settings}
\renewcommand{\shrink}{\vspace*{-2ex}}

\title{Speculative Nondeterminism}
\authorinfo{}{}{} % enable double-blind reviewing

\begin{document}

\maketitle

\begin{abstract}
We propose a new programmable concurrency control framework called
speculative nondeterminism for real time,
``open'' and distributed agents. 
%By open, we mean the agent programs
%are independent and are not necessarily constrained to operate
%in a particular fashion, and they may join the system at arbitrary times.
In this framework, dynamic and concurrent agent programs 
affect each other through a centralized store which represents shared resources.
%There is no direct communication among the agents.
%Because a sequential agent maybe blocked due to resource constraints
%in the store,
Our framework has novel programming constructs which
allows an agent to speculate against the future by multiple
exclusive choices that encode different strategies to achieve its goals.
The agent can make multiple choices which execute together but in isolation,
thus, there is a combinatorial effect through the joint interaction.
% The choices from the same agent execute in isolation but the choices from
% different agents interact through the store in a combinatorial fashion.
Unlike other concurrency frameworks, speculation models many potential
outcomes and thus improves the chances of an agent reaching a desired outcome.
% The benefit of speculation is that unlike other concurrency frameworks,
% the combinatorial-choice models more possibilities and
% improves the chances of successful outcomes for any participating agent.
Each possibility is represented by a ``virtual world.''
Agents operate in the virtual worlds created by the system,
the framework provides mechanisms for agents which have reached their
objective but yet are represented by multiple possible worlds to cleanly
exit. We also provide mechanisms to reduce the possibilities where an
agent can commit to certainly possibilities and give up on others, but
this is rather different from conventional committed choice.
% further allows the agents who have achieved their objectives
% in all existing worlds to exit and return to reality without delay.
% The choices from the same agent are meant to be executed in
% isolation from each other because they may update the store in different ways.
% Only one successful choice becomes the eventual reality. When multiple
% agents each specifies some choices, the system creates
% many stores and thus runtime environments to represent the
% different combinations of choices. We argue that combinatorial choices
% improve the likelihood of successful program completion and
% thus improve the overall system throughput.
% This is achieved with the programmable ``exit'' and ``commit'' operators
% where ``exit'' indicates that the agent program terminates and
% ``commit'' specifies when and where in the program agent wants to commit 
% to a particular choice and remove all other worlds (possibilities) associated
% with the other choice. This mechanism also controls the space of choices 
% and reclaims valuable computation resources to make the system practical. 
This paper presents the design, operational semantics of 
speculative nondeterminism, small but practical examples illustrating
the use of the language and experimental results of a prototype.
% demonstrates a prototype implementation of 
% the framework along with extensive evaluation results.
\end{abstract}

\keywords
speculation, concurrency, nondeterminism, agents

\input{intro}
\input{language}
\input{system}
\input{experiment}
\input{related}
\input{conclusion}

\bibliographystyle{abbrvnat}
{\renewcommand{\baselinestretch}{0.90}
\normalsize
\bibliography{ocp,gcc}
}
\end{document}
