\subsection{Cell and Context Feature}
\label{sec:cell}

As shown in \figref{fig:overview}, the output of our model is a score, which represents the linking confidence between a mention table and a candidate entity table. This score comes from two categories. One is to measure how similar or compatible two tables are. We employ two features called cell feature and context feature to capture the compatibility between mention table and candidate entity table.

After translation layer, each mention embedding $v_{\textbf{m}_{ij}}$ is converted into the same vector space as entity embedding. We concatenate translated mention embedding $\widetilde{v_{\textbf{m}_{ij}}}$ with entity embedding $v_{\textbf{e}_{ij}}$ and then go through a fully connected layer to get a hidden feature for a pair of cells $\langle \textbf{m}_{ij}, \textbf{e}_{ij}\rangle$. After averaging among all cells which need to be linked, we get the cell feature, which now represents a pair of tables $\langle T_M, T_E \rangle$.

\begin{equation}
f_{cell}(T_M, T_E) = \frac{1}{|P|}\sum_{\langle i,j\rangle \in P}FC([\widetilde{v_{\textbf{m}_{ij}}}, v_{\textbf{e}_{ij}}])
\end{equation}

Where $FC$ represents fully connected layer, and $[v_1, v_2]$ means vector concatenation.

Context feature follows similar idea. Instead of using mention embedding, we choose context embedding to concatenate with entity embedding. Context embedding for a particular cell $\textbf{m}_{ij}$ is an average of all mention embeddings of cells which are in the same row or the same column as $\textbf{m}_{ij}$ (exclude $\textbf{m}_{ij}$ itself). Detailed equation is as follows.

\begin{equation}
	f_{cxt}(T_M, T_E) = \frac{1}{|P|}\sum_{\langle i,j\rangle \in P}FC([\widetilde{vcxt_{\textbf{m}_{ij}}}, v_{\textbf{e}_{ij}}])
\end{equation}

\begin{equation}
vcxt_{\textbf{m}_{ij}} = \frac{1}{|\pi_{ij}|}(\sum_{\langle i,k\rangle \in P, k \neq j} v_{\textbf{m}_{ik}} + \sum_{\langle k,j\rangle \in P, k \neq i} v_{\textbf{m}_{kj}})
\end{equation}

Where $\pi_{ij}$ is number of cells which are in the same row or column as cell $\textbf{m}_{ij}$. 
Regardless table offers rare context information for entity disambiguation, mentions in the same row or column contain strong relatedness and can be regarded as surrounding context. 

By learning cell feature and context feature from mention table and candidate entity table, we can capture a general sense of semantic relatedness of all mention-entity pairs from two tables.






