%%%% ijcai15.tex

%\typeout{IJCAI-15 Instructions for Authors}

% These are the instructions for authors for IJCAI-15.
% They are the same as the ones for IJCAI-11 with superficical wording
%   changes only.

\documentclass{sig-alternate}
% The file ijcai15.sty is the style file for IJCAI-15 (same as ijcai07.sty).

%\usepackage{ijcai15}

% Use the postscript times font!
\usepackage{times}
\usepackage{rotating}
\usepackage{color}
\usepackage{epsfig,caption,subcaption, multicol,multirow}
\usepackage{amsmath,algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{url}
%\usepackage{subfigure}
\newcommand{\KZ}[1]{\textcolor{blue}{Kenny: #1}}
\newcommand{\ZY}[1]{\textcolor{red}{J: #1}}
\newcommand{\ZYBEGIN}{\textcolor{red}{\{BEGIN}}
\newcommand{\ZYEND}{\textcolor{red}{END\}}}
\newcommand{\tabref}[1]{Table \ref{#1}}
\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\secref}[1]{Section \ref{#1}}
\newcommand{\eqnref}[1]{Equation (\ref{#1})}
\newtheorem{example}{Example}
%\usepackage{mathrsfs}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

% the following package is optional:
%\usepackage{latexsym}

% Following comment is from ijcai97-submit.tex:
% The preparation of these files was supported by Schlumberger Palo Alto
% Research, AT\&T Bell Laboratories, and Morgan Kaufmann Publishers.
% Shirley Jowell, of Morgan Kaufmann Publishers, and Peter F.
% Patel-Schneider, of AT\&T Bell Laboratories collaborated on their
% preparation.

% These instructions can be modified and used in other conferences as long
% as credit to the authors and supporting agencies is retained, this notice
% is not changed, and further modification or reuse is not restricted.
% Neither Shirley Jowell nor Peter F. Patel-Schneider can be listed as
% contacts for providing assistance without their prior permission.

% To use for other conferences, change references to files and the
% conference appropriate and use other authors, contacts, publishers, and
% organizations.
% Also change the deadline and address for returning papers and the length and
% page charge instructions.
% Put where the files are available in the appropriate places.

\title{Commonsense Causal Reasoning by Causal Relation Extraction
from the Web
%\thanks{This work has been supported by NSFC-NRF Joint Research Scheme.}
}
%\author{Zhiyi Luo \and Yuchen Sha \and Kenny Q. Zhu\\
%Shanghai Jiao Tong University\\
%Shanghai, China
%\And
%Seung-won Hwang\\
%POSTECH\\
%Pohang, Korea
%}

\begin{document}

\maketitle

\begin{abstract}
Commonsense causal reasoning is the process of capturing and understanding
the causal dependencies amongst events and actions using commonsense knowledge. 
Such events and actions can be expressed in terms, phrases or 
sentences in natural language text.
Therefore, one possible way of obtaining causal knowledge is by extracting
causal relations between terms or phrases from a large text corpus. 
However, causal relations in text are sparse, ambiguous, and sometimes implicit,
and thus difficult to obtain.
This paper attacks the problem of commonsense causal reasoning between two
pieces of text using a data driven approach.
We propose a framework that automatically harvests a network of
causal-effect terms from a large web corpus.
We encode causal directions and strengths on the
network based on lexico-syntactic analysis of the sentences from which
the terms are extracted.
Backed by this network, we propose an algorithm to detect explicit events 
from input texts and formulate these events as light-weight causal structure 
patterns to refine the computation of causal strength between the texts.
%To showcase the power of our network, we also demonstrate its 
%pretty good causal directional property. The reasonable
%results from our framework also make this work flexible to 
%incorporate with other existing causality detection systems.
We evaluate this framework on the tasks of causal reasonings between sentences
as well as phrases. In particular, our approach outperforms all previously 
reported results in the standard SEMEVAL COPA task by substantial margins.
\end{abstract}

% A category with the (minimum) three required fields
%\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures,
% performance measures]

\terms{Framework; Algorithms; Experimentation}

\keywords{Commonsense causal reasoning; causal strength metric; causality
detection}

\input{intro}

\input{approach}

\input{eval}

\input{related}

\input{conclusion}

%\section*{Acknowledgments}
%% The file named.bst is a bibliography style file for BibTeX 0.99c
\bibliographystyle{abbrv}%named
\bibliography{causal}

\end{document}
