%
% File emnlp2016.tex
%

\documentclass[11pt,letterpaper]{article}
\usepackage{emnlp2016}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath,amsfonts}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{url,color}
\usepackage{threeparttable}
\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\tabref}[1]{Table \ref{#1}}
% Uncomment this line for the final submission:
\emnlpfinalcopy

%  Enter the EMNLP Paper ID here:
\def\emnlppaperid{12345}

% To expand the titlebox for more authors, uncomment
% below and set accordingly.
% \addtolength\titlebox{.5in}

\newcommand\BibTeX{B{\sc ib}\TeX}

\newcommand{\KZ}[1]{\textcolor{blue}{Kenny: #1}}
\newcommand{\XY}[1]{\textcolor{red}{Xinyu: #1}}
\newcommand{\YF}[1]{\textcolor{blue}{Yifan: #1}}


\title{Action Conceptualization: Mining isA Relation between Actions and Nouns}

% Author information can be set in various styles:
% For several authors from the same institution:
% \author{a \and ... \and Author n \\
%         Address line \\ ... \\ Address line}
% if the names do not fit well on one line use
%         Author 1 \\ {\bf Author 2} \\ ... \\ {\bf Author n} \\
% For authors from different institutions:
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \And  ... \And
%         Author n \\ Address line \\ ... \\ Address line}
% To start a seperate ``row'' of authors use \AND, as in
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \AND
%         Author 2 \\ Address line \\ ... \\ Address line \And
%         Author 3 \\ Address line \\ ... \\ Address line}
% If the title and author information does not fit in the area allocated,
% place \setlength\titlebox{<new height>} right after
% at the top, where <new height> can be something larger than 2.25in
\author{%Xinyu Hua \and Yifan Wang \and Yu Gong \and Kenny Q. Zhu\\
%Shanghai Jiao Tong University\\
%  {\tt huaxinyu, racheter, gy910210, kenzhu @sjtu.edu.cn}\\
  }

\date{}

\begin{document}

\maketitle

\begin{abstract}
  This paper presents a retrieval based method to achieve action conceptualization,
  which is the process of abstracting action concepts into noun concepts. Action
  concepts are predicate together with argument concepts such as for subject and
  object. For example the noun concept ``acquisition'' would be a good abstraction
  of the action concept ``company buy company''.
  Our work is based on the assumption that the word used in news title are
  usually generalization or abstraction of the event discussed in the news content.
  We use online textual news as our corpus, and build a tripartite graph to model
  the relation between noun, news and action. We subsequently build an action-noun map
  by mining relatedness between noun and action. This work can be useful in various
  domains. As a showcase we build a news search engine with semantic search enabled
  by our conceptualization result. On a human labeled evaluation dataset our method
  outperforms a topic model baseline and a TF-IDF baseline.
\end{abstract}

\input{tex/intro}

\input{tex/data}

\input{tex/approach}

\input{tex/system}

\input{tex/eval}

\input{tex/related}

\input{tex/conclusion}


\section*{Acknowledgments}

Do not number the acknowledgment section.

\bibliography{emnlp2016}
\bibliographystyle{emnlp2016}

\end{document}
